### 2019-03-11 paper/main.tex
dev

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\documentclass[%
 reprint,
%superscriptaddress,
%groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose,
%preprint,
%preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
 amsmath,amssymb,
 aps,
%pra,
%prb,
%rmp,
%prstab,
%prstper,
%floatfix,
]{revtex4-2}

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
%%%%%%%%%%%%%%%%%% Commands %%%%%%%%%%%%%%%%%

% include bbl file (arXiv)
\newif\ifbbl
% \bblfalse
\bbltrue

\newcommand{\ie}{i.\,e.~}
\newcommand{\Ie}{I.\,e.~}
\newcommand{\eg}{e.\,g.~}
\newcommand{\Eg}{E.\,g.~}
% \newcommand{\e}{\mathrm{e}}
\newcommand{\ic}{i}

\newcommand*\conj[1]{
  \vbox{
  \hrule height 0.3ptword
  \kern0.5ex
  \hbox{
  \kern-0.4em
  \ifmmode#1\else\ensuremath{#1}\fi
   \kern-0.em
  }
 }
}
\newcommand{\B}{\boldsymbol}
% \newcommand{\tens}[1]{\B{#1}}
% \newcommand{\tens}[1]{\underline{\underline{#1}}}
\newcommand{\tens}[1]{\B{#1}}
\newcommand{\re}{\mathrm{Re}}
\newcommand{\im}{\mathrm{Im}}
\newcommand{\grad}{\B{\mathrm{\nabla}}}
\renewcommand{\div}{\B{\mathrm{\nabla\cdotp}}}
\newcommand{\ddroit}{\mathrm{d}}
\newcommand{\epsf}{\varepsilon^{\rm f}}
\newcommand{\epsftens}{\tens{\varepsilon}^{\rm f}}
\newcommand{\epstens}{\tens{\varepsilon}}
\newcommand{\epsd}{\varepsilon^{\rm d}}
\newcommand{\epsvac}{\varepsilon_{0}}
\newcommand{\epshom}{\tilde{\epstens}}
\newcommand{\fig}[1]{Fig.~(\ref{#1})}
\newcommand{\equ}[1]{Eq.~(\ref{#1})}

\newcommand{\xitens}{\tens{\xi}}
\newcommand{\xihom}{\tilde{\xitens}}

\begin{document}

\title{Homogenization of periodic and random ferroelectric-dielectric composites}

% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
\author{Benjamin Vial and Yang Hao}
\affiliation{School of Engineering and Computer Science, Queen Mary, University of London, London, E1 4NS, United Kingdom}
% \eads{\mailto{b.vial@qmul.ac.uk}, \mailto{y.hao@qmul.ac.uk}}

\begin{abstract}
We investigate the homogenized permittivity of ferroelectric-dielectric mixtures under
a static electric field. A refined model is used to take into account the coupling
between the electrostatic problem and the electric field dependent permittivity of the
ferroelectric material. Periodic and random structures in two dimensions are investigated and
we study the effective permittivity, losses, electrically induced anisotropy and tunability
 of the homogenized materials.
\end{abstract}

\keywords{Homogenization, Ferroelectrics, Metamaterials , Tunability}

\maketitle

\section{Introduction}

Ferroelectric materials play a crucial role in tunable
microwave devices, with typical applications including antenna beam steering,
phase shifters, tunable power splitters, filters, voltage controlled oscillators and
matching networks \cite{Tagantsev2018}. Both bulk ceramics and thin films have
been employed to design frequency agile components \cite{vendik1999ferroelectric, lancaster1998thin,
xi2000oxide} and metamaterials \cite{Hand2008, Zhao2008}. The main reason of using
ferroelectric materials is their strong dependence of their permittivity $\varepsilon$
on an applied electric field $E$, which is measured by their tunability defined as $n = \varepsilon(0)/\varepsilon(E)$.
The key requirements for antenna and microwave applications are large tunability and low losses.
These two characteristics are correlated and one has to find a trade-off for optimal device
performance, which can be quantified by the so called commutation quality factor
$K = (n -1)^2/(n\, \tan\delta(0)\,\tan\delta(E))$, where $\tan\delta$ is the loss tangent.\\
These materials have usually high permittivity values,
often leading to slow response time and impedance mismatch, which can be an issue in some practical
applications. Thus it has been considered to mix ferroelectric ceramics to low-index and
low-loss non-tunable dielectrics in order to reduce both permittivity value and losses.
The effective parameters of those composites have been investigated \cite{Sherman2006,
jylha2008tunability, Sherman2004, ASTAFIEV20032381} and it has been found that the
permittivity can be greatly reduced while losses and tunability are much less sensitive to the
dielectric phase addition.\\
This study investigates the effective permittivity of dielectric/ferroelectric composites
by using a two-scale convergence method \cite{Allaire92, Guenneau2000}.
The originality lies in the fact that a fully coupling model is employed to
calculate the electrostatic field distribution when a uniform biasing field is
applied on the structures, which will result in a local modification of the permittivity
in the ferroelectric phase due to the microstructure. As compared to a simple uncoupled model where the
ferroelectric phase is only modified through the biasing field,
the resulting effective permittivity, dielectric losses, tunability and
anisotropy significantly differ. \\
We first a two-dimensional model of metamaterials made of parallel rods with circular cross section,
considering both periodic and random distributions.

%#########################################################################################

\section*{Theory and numerical model}

We consider a composite made of a ferroelectric material with anisotropic
permittivity $\epsftens(\B E)$
that is dependent on an applied electric field $\B E$,
and a non tunable dielectric of permittivity $\epsd$, which are both non-magnetic.
The structures under study are invariant along the $z$ direction, which leads to the standard decomposition
of the wave equation in the transverse electric case (TE, electric field parallel
 to the direction of invariance) and the
transverse magnetic case (TM, magnetic field parallel to the direction
of invariance).
A uniform biasing field is applied to the sample in order to be able to tune the
permittivity of the dielectric phase.
Modelling homogenized properties of this type of mixtures can be done by assuming
that the electric field distribution is uniform throughout the sample,
so that the study of the tunability is
essentially achieved by changing the value of the properties in the ferroelectric phase and computing
 the effective permittivity
of the composite. We refer this approach as to the uncoupled model in the following.
However, a more accurate description is to take into account the change of the
electric field by the microstructure, if any. We therefore need to solve an
electrostatic equation to find the field distribution within the material, but its solution
depends on the permittivities of both materials, and the permittivity in the
ferroelectric phase depends on this induced electric field: this leads to a strongly coupled problem.\\

% -------------------------------------------------------------------------------
\subsection*{Permittivity model\label{permmodel}}

We use barium strontium titanate (BST) as our ferroelectric material. Microwave measurements
at 10 GHz where performed and the normalized permittivity value
as a function of biasing field are reported on \fig{fig1}.\\
To describe the permittivity, we make use of the Landau potential
given by $F(P,E) = F_0 +  a P^2/2 + b P^4/4 + cP^6/6 - EP$, where $E$ is
the applied electric field and $P$ is the polarization \cite{Zhou2008}. Variations of the
permittivity with the temperature can be taken into account through the
 coefficients $a$, $b$ and $c$, but we assume we are working at a constant
room temperature. We further assume that the material is not subject to any stress, so that the variation
of permittivity due to mechanical constraints is irrelevant.
The equation of state $$\frac{\partial F (P, E)}{\partial P}   = a P_0 + b P_0^3 + c P_0^5 - E = 0$$ gives the
dependence of the polarization on the applied electric field,
with $P_0$ being the equilibrium polarization.
Along the direction of a uniformly applied electric field, the permittivity is given by:

\begin{equation}
  \epsf(E) = \left[\epsvac \frac{\partial^2 F (P, E)}{\partial P^2} \right]^{-1} = \frac{\epsf(0)}{1 + \beta P_0^2 + \gamma P_0^4},
  \label{eq_epsf}
\end{equation}
where $\beta = 3 b \epsvac \epsf(0) /a$ and  $\gamma = 5 c \epsvac \epsf(0) /a$.
The permittivity without bias $\epsf(0)$ was measured to be 120 and the fitting parameters
are $a = 0.992/\epsvac$, $b=0.086/(\epsvac^3\,E_{\rm ref}^2)$, $c=0.014/(\epsvac^5\,E_{\rm ref}^4)$, $E_{\rm ref}=1$ kV/mm.
As the norm of the field increases, the permittivity decreases with a characteristic
bell curve typical for a ferroelectric material in its paraelectric state.
\begin{figure}[!t]
\centering
\includegraphics[width=1\columnwidth]{epsilon_fit}
\caption{Variation of the ferroelectric permittivity as a function of the
 applied electric field (green dots: measurements, grey dashed line: fit to
 formula~(\ref{eq_epsf})).}
\label{fig1}
\end{figure}
Furthermore, assuming the crystalline principal axes of the ferroelectric material
are oriented in the coordinate directions, and that the diagonal components of the permittivity
tensor are only function of the corresponding bias electric field components \cite{Krowne2002}, we have:
\begin{equation}
  \epsftens (\B E) =
\left(
\begin{matrix}
\epsf_{xx}(E_x) & 0 & 0 \cr
0 & \epsf_{yy}(E_y) & 0 \cr
0 & 0 & \epsf_{zz}(E_z) \cr

  \end{matrix}
  \right)
\label{eq_epsftens}
\end{equation}
where each of the diagonal components have the functional form
given by \equ{eq_epsf}.

% -------------------------------------------------------------------------------
\subsection*{Electrostatic model}
The composites under study are made of two materials, thus their permittivity
is represented by a piecewise defined tensor $\epstens(\B r, \B E)$ which is
equal to $\epsftens(\B E(\B r))$ in the ferroelectric phase and ${\rm diag}(\epsd)$
in the dielectric phase.
In the following, we consider two different cases for the biasing field.
Because of the form~(\ref{eq_epsftens}) assumed for the ferroelectric permittivity
tensor, $\varepsilon_{zz}$ will not be changing for a field in the plane orthogonal
to the $z$ axis. This is the only component
being relevant for TE polarization, so we consider in this case a uniform biasing
electric field applied along the direction of invariance $\B E_0 = E_{0} \B e_z$.
On the other hand,
the in-plane components of $\epsftens$ are tuned by $E_x$ and $E_y$, therefore,
without loss of generality,
we consider a uniform applied electric field directed along the $x$ axis
$\B E_0 = E_{0} \B e_x$ for the TM polarization case.
To calculate the total electric field in the material, one
has to solve the electrostatic equation for the potential $V$:
\begin{equation}
\div (\epsvac \epstens \grad V) = 0
\label{eq_elstat}
\end{equation}
Note that for the TE case, the solution is straightforward since the structures
are invariant along $z$, so that the electric field is equal to the uniform biasing field.
However in the TM case, the situation is much more complex: this is a coupled problem since the
electric field $E=-\grad V$ derived from the
solution of \equ{eq_elstat} depends on the permittivity distribution, which
itself depends on the electric field.
The coupled system formed
of Eqs.~(\ref{eq_epsftens}) and (\ref{eq_elstat}) is solved iteratively until there
is convergence on the norm of the electric field.
Here we would like to emphasise that the permittivity in the ferroelectric material, although
uniform initially, will be spatially varying due to the non-uniform distribution
of the total electric field.\\

% -------------------------------------------------------------------------------
\subsection*{Homogenization}
The effective permittivity for TM polarization is calculated
using two scale homogenization technique \cite{Allaire92, Guenneau2000}.
For this purpose, one has to find the solutions
$\psi_j$ of two annex problems $\mathcal P_j$, $j=\{1, 2\}$:
\begin{equation}
\div \left[ \xitens \grad(\psi_j + r_j) \right] = 0,
\label{eq_hom_annex}
\end{equation}
where $\B r = (x, y)^T$ is the position vector in the $xy$ plane and
$\xitens=\epstens^{\rm T}/ {\rm det }(\epstens)$.
The homogenized coefficient $\xihom$ is obtained with:
\begin{equation}
\xihom = \langle \xitens \rangle + \B \phi,
\label{eq_hom}
\end{equation}
where $\langle . \rangle$ denotes the mean value over the unit cell.
The elements of the matrix $\B \phi$ represent correction terms and
are given by $\B \phi_{ij} = \langle \xitens \grad \psi_i \rangle_j$.
Finally the homogenized permittivity  can be calculated using $\epshom_{\rm TM}=\xihom^{\rm T}/ {\rm det }(\xihom)$.\\
On the other hand, the TE case is fairly easy to handle since the homogenized permittivity
is simply the average of the permittivity in the unit cell:
\begin{equation}
\epshom_{\rm TE} = \langle \epstens \rangle .
\label{eq_hom_TE}
\end{equation}

% -------------------------------------------------------------------------------
\subsection*{Numerical setup}
In the TM case, equations~(\ref{eq_elstat}) and (\ref{eq_hom_annex}) are solved with a Finite Element
Method using the open source packages Gmsh \cite{gmsh} and GetDP \cite{getdp}.
In both cases we use a square unit cell $\Omega$ of length $d$ with periodic boundary
conditions along $x$ and $y$. Second order Lagrange elements are used and the
solution is computed with a direct solver (MUMPS \cite{MUMPS}).
% The source code and
% data necessary to reproduce the results reported in this paper are freely available
% online.

%#########################################################################################

\section*{Numerical results}
In the following numerical results, the dielectric phase is supposed to be
lossless with $\epsd = 3$ while the ferroelectric material follows the
permittivity described in section~\ref{permmodel} and has a constant loss
tangent $\tan \delta^{\rm f} = 10^{-2}$.

% -------------------------------------------------------------------------------
\subsection*{Two dimensional periodic metamaterial}
Lets us now consider infinitely long dielectric rods of circular cross section
of radius $r$ embedded in a ferroelectric matrix.\\
We first study the convergence of the coupled problem on the particular case with dielectric
filling fraction $f=\pi r^2/d^2=0.5$ and $E_0=2$kV/mm. Figures \ref{conv2D}(a) and \ref{conv2D}(b) show the
convergence of the real part and loss tangent of the components of the homogenized
 permittivity tensor, respectively. The $yy$ components converge very quickly
 and are almost unaffected by the coupling process whereas the
 $xx$ components change drastically from the initial conditions.
 This is due to the effect of the distribution
 of the electrostatic field within the unit cell (see Figs.~(\ref{conv2D})(c) and \ref{conv2D}(d)),
 where the $x$ component of the electric field is still much stronger
 than the $y$ component, even if it is spatially varying in the ferroelectric medium.
 At equilibrium, the electric field is concentrated close to the $y$ axis in between two neighbouring
 rods. This in turn affects the permittivity distribution (see Figs.~(\ref{conv2D})(e) and \ref{conv2D}(f)),
 and the homogenized properties of the composite.\\
 We computed the effective parameters of these metamaterial structures for different
 radii of the rods and studied their behaviour when subjected to an external
 electrostatic field (see \fig{eff_par_2D_TM}). The results of our coupled
 model differ significantly from the uncoupled one. Increasing the dielectric fraction
 lowers the effective permittivity while the losses are slightly reduced but much less sensitive.
 Due to the inhomogeneous redistribution of the permittivity over the ferroelectric domain, the
 overall tunability changes. In the case studied here, effective tunability is reduced with
 increasing dielectric concentration. There are two concurrent effect at stake here: on the one hand
 the dilution of ferroelectric makes the composite less tunable, but on the other hand,
 the rearrangement of the electrostatic field surrounding the inclusion and its
 concentration in some region will cause a higher permittivity change locally.
 The relative strength of those phenomena is governed by the shape of the inclusion and its permittivity
 and so it is envisioned that the performance of the composites might be enhanced by engineering
 their microstructure.
 The geometry of the unit cell is symmetric so the homogenized material is
  isotropic when no field is applied.
 But when the sample is biased, the permittivity distribution becomes asymmetric due
 to the inhomogeneity of the electric field, thus making the effective material properties anisotropic.
This geometric effect is added to the anisotropy arising from the material properties of the ferroelectric
phase, and depending on the topology and permittivity of the rods, one effect would be predominant.
Those subtle phenomena can only be rigorously taken into account by employing a coupling formalism
and are responsible for the difference observed when compared to a simple uncoupled model.\\

\begin{figure}[!t]
\centering
\includegraphics[width=0.95\columnwidth]{conv}
\caption{Convergence of the coupled problem in the TM polarization case.
Real part (a) and loss tangent (b) of the components of the homogenized
 permittivity tensor as a function of iteration step $i$. The distribution of
 the electric field (colormap: magnitude, arrows: direction) and of the
 $xx$ component of the permittivity tensor are shown for $i=1$
  (c and d) and $i=29$ (e and f).
 }
\label{conv2D}
\end{figure}

\begin{figure*}[!t]
\centering
\includegraphics[width=0.8\textwidth]{effpar_per}
\caption{Effective parameters of the 2D metamaterials as a function of the
 applied electric field for various filling fraction of dielectric, TM polarization.
 (a): normalized permittivity, (b): normalized loss tangent, (c): normalized tunability and
 (d): anisotropy factor. The solid lines correspond to the coupled model and
 the dashed lines to the uncoupled model.}
\label{eff_par_2D_TM}
\end{figure*}

% -------------------------------------------------------------------------------
\subsection*{Random case}
We finally study the effect of random particle distribution on the effective parameters of the
composites. This is an important point as fabrication of randomly dispersed
inclusions is much more easy from a technological perspective. For each filling fraction of the dielectric,
we generated 21 numerical samples with inclusions of circular cross section of average radius
$r=d/20$ that can vary by $\pm 30\%$. Their centre is chosen randomly and the
rods are allowed to overlap. An example of distribution for $f=0.5$ is given on \fig{randmatepsi}.
The effective material properties are plotted on \fig{eff_par_2Drand_TM}.
Similarly to the periodic case, the permittivity decreases with increasing dilution of
ferroelectric, but for identical filling fraction,
the permittivity is lower as compared to the periodic array, and the smaller the dielectric concentration the larger
is the difference. Losses decrease as well and the reduction is substantially larger
than the periodic case, with higher variation from sample to sample as $f$ increases.
The tunability is reduced as one adds more dielectric, but is slightly greater than that in the periodic case.
The redistribution of electric field, permittivity and convergence of
the effective parameters are displayed in \fig{conv_random}. The effect of
disorder plays an important role here: the electrostatic field gets concentrated
in between neighbouring inclusions and the smaller the gap the higher the field, hence
a greater local permittivity change. In addition, even if the distribution of particle is
random, one expects that the anisotropy due to geometry would cancel for a sufficiently large number
of particles (which is the case as the mean anisotropy factor is close to $1$ when no
bias field is applied). However, the anisotropy due to ferroelectric properties is
important in this case as well, as both the $x$ and $y$ components of the electrostatic field
are playing a role. This result in an anisotropy factor that might be greater than $1$,
but with high variability from sample to sample. However, on average, the anisotropy factor
increases with increasing dielectric concentration, and the smaller the concentration the more tunable
it will be.

\begin{figure}
\centering
\includegraphics[width=1\columnwidth]{randmatepsi}
\caption{Permittivity distribution of the numerical samples used for $f=0.5$. Dark
colour indicates the ferroelectric material while light colour represents the
dielectric inclusions.}
\label{randmatepsi}
\end{figure}

\begin{figure}[!t]
\centering
\includegraphics[width=0.95\columnwidth]{effpar_rand}
\caption{Effective parameters of the random 2D mixtures as a function of the
 applied electric field for various filling fraction of dielectric, TM polarization.
 (a): normalized permittivity, (b): normalized loss tangent, (c): normalized tunability and
 (d): anisotropy factor. The solid lines represent the average values
  over the 21 samples and the lighter error bands show a confidence interval corresponding to
  the standard deviation.}
\label{eff_par_2Drand_TM}
\end{figure}

\begin{figure}[!t]
\centering
\includegraphics[width=0.95\columnwidth]{cvrand}
\caption{Convergence of the coupled problem for TM polarization in the random case
for one sample.
Real part (a) and loss tangent (b) of the components of the homogenized
 permittivity tensor as a function of iteration step $i$. The distribution of
 the electric field (colour map: magnitude in logarithmic scale, arrows: direction) and of the
 $xx$ component of the permittivity tensor are shown for $i=1$
  (c and d) and $i=7$ (e and f).
 }
\label{conv_random}
\end{figure}

%#########################################################################################

\section*{Conclusion}

We have studied the homogenized properties of dielectric/ferroelectric mixtures
using a rigorous model that take into account the coupling between the electrostatic
field distribution and the field dependant ferroelectric permittivity tensor. After
convergence of the coupled problem, the effective permittivity tensor is calculated using
two scale convergence homogenization theory.
The results obtained by this model differ significantly from a simple assumption that
the permittivity of the ferroelectric respond just to the uniform biasing field.
We have considered both periodic and random arrays
of dielectric rods in a ferroelectric matrix in 2D, and studied their effective properties
for TE and TM polarization as a function of dielectric concentration and bias field.
Importantly, adding more low index and low loss dielectric allows to decrease
the overall permittivity significantly and slightly lower the losses. On the other hand,
the higher the dielectric concentration the smaller the tunability would be while
anisotropy gets higher as the concentration decreases.
The properties of the composites are affected by multiple factors:
 geometry and the spatially dependent electric field that will induce locally a tunable, anisotropic
 response in the ferroelectric phase depending on its amplitude and direction.
 This suggest that the performances of the composites
 may be enhanced by distributing the two phases in an optimal way to get high
  tunability and low losses. Further work in that direction is needed as well as
  extending this study to 3D media.
 Finally, because the permittivity of the dielectric is much smaller than the ferroelectric one,
 it would be of great interest to use high contrast homogenization theory
 \cite{BOUCHITTE2004377, cherednichenko_cooper_2015} to
 study this kind of mixtures.
 This would reveal the frequency dependant artificial magnetism due to "micro-resonances"
 in the high index phase and potentially lead to composites with tunable effective permeability.

%
%
% \ack
% This work was funded by the Engineering and Physical Sciences Research Council
% (EPSRC), UK, under a grant (EP/P005578/1) 'Adaptive Tools for
% Electromagnetics and Materials Modelling to Bridge the Gap between Design and Manufacturing (AOTOMAT)'.
% The authors would like to thanks Henry Giddens for performing the measurements of
% ferroelectric permittivity used in this paper.

\section*{References}
% \bibliographystyle{iopart-num}
\bibliography{biblio}

\end{document}

### 2019-03-11 ferromtm/models/bidon.py

@@ -1,0 +1,67 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+# Author: Benjamin Vial
+# License: MIT
+# import logging
+# from gridmap import grid_map
+
+
+# logging.captureWarnings(True)
+# logging.basicConfig(
+#     format=("%(asctime)s - %(name)s - %(levelname)s - " + "%(message)s"),
+#     level=logging.DEBUG,
+# )
+
+import numpy as np
+import time
+
+
+def main_rand(params, save=False, coupling=True):
+    print("fuck")
+    return params
+
+
+def main_rand_coupled(params):
+    test = main_rand(params, save=True, coupling=True)
+    return test
+
+
+# function_parallel = main_rand_coupled
+
+nE = 11
+Ebias = np.linspace(0, 2, nE)
+nF = 5
+Fincl = np.linspace(0.1, 0.5, nF)
+E1, F1 = np.meshgrid(Ebias, Fincl)
+params = np.vstack((E1.ravel(), F1.ravel())).T
+from aotomat.tools.parallelize import *
+
+# def run_parallel(params):
+#     result = grid_map(
+#         main_rand_coupled,
+#         params,
+#         quiet=False,
+#         num_slots=1,
+#         temp_dir=u"./tmp",
+#         max_processes=len(params),
+#         queue="all.q",
+#         require_cluster=True,
+#         local=True,
+#         cleanup=True,
+#     )
+#     return result
+
+
+if __name__ == "__main__":
+    run_parallel = parallel(main_rand_coupled, partype="gridmap")
+
+    # f_parallel(params)
+    tstart = time.time()
+    print("TSART: {}".format(tstart))
+    out = run_parallel(params)
+    print(out)
+    # f_parallel(params, save=True, coupling=False)
+    tend = time.time()
+    et = tend - tstart
+    print("TEND: {}".format(tend))
+    print("ELAPSED: {}s".format(et))

### 2019-03-11 ferromtm/models/bst.py

@@ -112,11 +112,11 @@ if __name__ == "__main__":
         E_exp, eps_norm_exp[1], "o", label="measured, $f=3.8$ GHz", color="#b05151"
     )
     plt.plot(E_fit, eps_norm_fit[1], "--", color="#b05151", label="fit, $f=3.8$ GHz")
-    plt.ylabel(
-        r"normalized permittivity $\varepsilon^{\rm f}/\varepsilon^{\rm f}(E=0)$"
-    )
+    plt.ylabel(r"normalized permittivity")
+    # $\varepsilon^{\rm f}/\varepsilon^{\rm f}(E=0)$
     plt.xlabel("electric field (MV/m)")
     plt.legend()
 
     plt.tight_layout()
-    fig.savefig("epsilon_fit.eps")
+    plt.ylim((0.1, 1.04))
+    # fig.savefig("epsilon_fit.eps")

### 2019-03-11 ferromtm/models/coupled2D.py

@@ -3,11 +3,12 @@
 # Author: Benjamin Vial
 # License: MIT
 
-from ferromtm import __file__
-
+import ferromtm
 import numpy as np
 
-# from aotomat.tools.plottools import *
+import time
+
+## from aotomat.tools.plottools import *
 from pytheas.homogenization import *
 from aotomat.electrostatics.per2D import femmodel as model_es
 from pytheas.homogenization.twoscale2D import femmodel as model_hom
@@ -17,36 +18,24 @@ from pytheas.material import genmat
 import os
 import tempfile
 from ferromtm.models.bst import epsilonr_ferroelectric
-from aotomat.tools.parallelize import *
+from pytheas.tools.utils import refine_mesh
 
-rootdir = os.path.dirname(os.path.dirname(__file__))
+# import logging
 #
+# logging.captureWarnings(True)
+# logging.basicConfig(
+#     format=("%(asctime)s - %(name)s - %(levelname)s - " + "%(message)s"),
+#     level=logging.DEBUG,
+# )
 #
 
-from aotomat.material.bst import epsi_bst_norma
+rootdir = os.path.dirname(os.path.dirname(ferromtm.__file__))
 
-
-def epsilonr_ferroelectric_(E_applied, tandelta=1e-2, eps00=120, sample=4):
-    return epsi_bst_norma(E_applied, sample) * eps00 * (1 - tandelta * 1j)
-
-
-E_applied_i = np.linspace(-10, 10, 1001)
-epsilonr_ferroelectric_i = epsilonr_ferroelectric_(E_applied_i)
-
-
-def epsilonr_ferroelectric_old(E_applied, tandelta=1e-2, eps00=120, sample=4, dc=False):
-    return np.interp(E_applied, E_applied_i, epsilonr_ferroelectric_i)
-
-
-# epsilonr_ferroelectric = epsilonr_ferroelectric_old
-
-# importlib.reload(model_es)
-# importlib.reload(model_hom)
 
 pi = np.pi
 eps_incl = 3
 data_folder = os.path.join(rootdir, "data", "results")
-mat_folder = "../data/mat/random/"
+mat_folder = os.path.join(rootdir, "data", "mat")
 
 
 def ellipse(Rinclx, Rincly, rot_incl, x0, y0):
@@ -117,6 +106,20 @@ def make_pattern(f, choice="rand", isample=0):
     return mat
 
 
+def ref_mesh(fem):
[…]

### 2019-03-11 ferromtm/models/run_circ.py

@@ -1,0 +1,24 @@
+from coupled2D import *
+from aotomat.tools.parallelize import *
+
+
+def main_per_uncoupled(params):
+    return main_circle(params, coupling=False, save=True)
+
+
+def main_per_coupled(params):
+    return main_circle(params, save=True, coupling=True)
+
+
+if __name__ == "__main__":
+
+    run_parallel_coupled = parallel(main_per_coupled, partype="gridmap")
+    run_parallel_uncoupled = parallel(main_per_uncoupled, partype="gridmap")
+    tstart = time.time()
+    print("TSART: {}".format(tstart))
+    out_coupled = run_parallel_coupled(params)
+    out_uncoupled = run_parallel_uncoupled(params)
+    tend = time.time()
+    et = tend - tstart
+    print("TEND: {}".format(tend))
+    print("ELAPSED: {}s".format(et))

### 2019-03-11 ferromtm/models/run_convergence.py

@@ -1,0 +1,12 @@
+from coupled2D import *
+from aotomat.tools.parallelize import *
+
+
+if __name__ == "__main__":
+    tstart = time.time()
+    print("TSART: {}".format(tstart))
+    out_cv = main_circle_conv(params[104])
+    tend = time.time()
+    et = tend - tstart
+    print("TEND: {}".format(tend))
+    print("ELAPSED: {}s".format(et))

### 2019-03-11 ferromtm/models/run_rand.py

@@ -1,0 +1,23 @@
+from coupled2D import *
+from aotomat.tools.parallelize import *
+
+
+def main_rand_uncoupled(params):
+    return main_rand(params, coupling=False, save=True)
+
+
+def main_rand_coupled(params):
+    return main_rand(params, save=True, coupling=True)
+
+
+if __name__ == "__main__":
+    run_parallel_coupled = parallel(main_rand_coupled, partype="gridmap")
+    run_parallel_uncoupled = parallel(main_rand_uncoupled, partype="gridmap")
+    tstart = time.time()
+    print("TSART: {}".format(tstart))
+    out_coupled = run_parallel_coupled(params)
+    out_uncoupled = run_parallel_uncoupled(params)
+    tend = time.time()
+    et = tend - tstart
+    print("TEND: {}".format(tend))
+    print("ELAPSED: {}s".format(et))

### 2019-03-11 ferromtm/visualization/plots.py

@@ -1,5 +1,7 @@
 import matplotlib as mpl
 
+# mpl.use("Qt4Agg")
+
 mpl.rcParams["legend.fancybox"] = False
 mpl.rcParams["legend.fontsize"] = "small"
 mpl.rcParams["legend.frameon"] = False

### 2019-03-11 ferromtm/visualization/postpro2D.py

@@ -1,5 +1,5 @@
-from ferromtm.visualization.plots import *
 from ferromtm.models.coupled2D import *
+from ferromtm.visualization.plots import *
 
 
 n_bulk = tunability(epsilonr_ferroelectric(Ebias), epsilonr_ferroelectric(0))
@@ -13,7 +13,7 @@ def load_arch(E_bias, f, coupling=True):
     if not coupling:
         name += "_uncoupled"
     saveddir = os.path.join(data_folder, "circ_rods")
-    saveddir = os.path.join(data_folder, "circ_rods_pattern")
+    # saveddir = os.path.join(data_folder, "circ_rods_pattern")
     filename = os.path.join(saveddir, name + ".npz")
     arch = np.load(filename)
     eps_hom = arch["eps_hom"]
@@ -135,7 +135,7 @@ def plot_eff_par(fig, ax):
     subplot_id(ax=ax[0][0], id="a")
     ax[1][0].set_ylim((0.75, 1.01))
     subplot_id(ax=ax[1][0], id="b")
-    ax[0][1].set_ylim((0.9, 1.21))
+    ax[0][1].set_ylim((0.9, 1.41))
     subplot_id(ax=ax[0][1], id="c")
     ax[1][1].set_ylim((0.37, 1.03))
     subplot_id(ax=ax[1][1], id="d")

### 2019-03-11 ferromtm/visualization/postpro2D_conv.py

@@ -1,0 +1,158 @@
+from ferromtm.models.coupled2D import *
+from ferromtm.visualization.plots import *
+
+
+n_bulk = tunability(epsilonr_ferroelectric(Ebias), epsilonr_ferroelectric(0))
+K_bulk = cqf(epsilonr_ferroelectric(Ebias), epsilonr_ferroelectric(0))
+eps_00 = epsilonr_ferroelectric(0).real
+tandelta_00 = -epsilonr_ferroelectric(0).imag / epsilonr_ferroelectric(0).real
+
+
+def load_arch(iter):
+    cv_dir = os.path.join(data_folder, "circ_rods", "convergence")
+    fname = "cv_iter_{}.npz".format(iter)
+    filename = os.path.join(cv_dir, fname)
+    arch = np.load(filename)
+    eps_hom = arch["eps_hom"]
+    epsi = arch["epsi_map"]
+    E = arch["E_map"]
+    return epsi, E, eps_hom
+
+
+iplot = [0, 1, 2, 3, 4]
+
+ncv = 13
+
+
+def load_results():
+    Eps_eff_xx = np.zeros(ncv, dtype=complex)
+    Eps_eff_yy = np.zeros(ncv, dtype=complex)
+    Aniso_factor = np.zeros(ncv, dtype=float)
+    E_cv = []
+    epsi_cv = []
+    for icv in range(ncv):
+        epsi, E, eps_hom = load_arch(icv)
+        Eps_eff_xx[icv] = eps_hom[0, 0]
+        Eps_eff_yy[icv] = eps_hom[1, 1]
+        Aniso_factor[icv] = aniso_factor(eps_hom)
+        E_cv.append(E)
+        epsi_cv.append(epsi)
+
+    norm_eps_xx = Eps_eff_xx.real / eps_00
+    norm_loss_xx = -Eps_eff_xx.imag / Eps_eff_xx.real / tandelta_00
+    norm_eps_yy = Eps_eff_yy.real / eps_00
+    norm_loss_yy = -Eps_eff_yy.imag / Eps_eff_yy.real / tandelta_00
+    return (norm_eps_xx, norm_loss_xx, norm_eps_yy, norm_loss_yy, E_cv, epsi_cv)
+
+
+E0x, E0y = 2, 0
+normE0 = 2
+
+
+def plotEarrows(ax, Enewx, Enewy):
[…]

### 2019-03-11 ferromtm/visualization/postpro2D_random.py

@@ -24,7 +24,7 @@ iplot = [0, 1, 2, 3, 4]
 Nbsamples = 21
 
 
-def load_results():
+def load_results_():
     Eps_eff_lin = np.zeros((Nbsamples, nE, nF), dtype=complex)
     Eps_eff_nl = np.zeros((Nbsamples, nE, nF), dtype=complex)
     Aniso_factor_lin = np.zeros((Nbsamples, nE, nF), dtype=float)
@@ -38,6 +38,7 @@ def load_results():
             # print(iE)
             for isample in sample_list:
                 # print(isample)
+                print("E={:.2f}MV/m, f={:.2f}, sample {}".format(E_bias, f, isample))
                 _, _, eps_hom = load_arch(E_bias, f, isample, coupling=True)
                 # eigval, eigvec = np.linalg.eig(eps_hom)
                 # eps_hom = np.diag(eigval)
@@ -77,6 +78,21 @@ def load_results():
             n_norm_nl[isample, :, iF] = n_nl[isample, :, iF] / n_bulk
     # Knorm_lin[isample, :, iF] = K_lin[isample, :, iF] / K_bulk
     # Knorm_nl[isample, :, iF] = K_nl[isample, :, iF] / K_bulk
+    name = "random_case"
+    saveddir = os.path.join(data_folder, "rand_circ_rods")
+    filename = os.path.join(saveddir, name + ".npz")
+    np.savez(
+        filename,
+        norm_eps=norm_eps,
+        norm_eps_nl=norm_eps_nl,
+        norm_loss=norm_loss,
+        norm_loss_nl=norm_loss_nl,
+        n_norm_lin=n_norm_lin,
+        n_norm_nl=n_norm_nl,
+        Aniso_factor_lin=Aniso_factor_lin,
+        Aniso_factor_nl=Aniso_factor_nl,
+    )
+
     return (
         norm_eps,
         norm_eps_nl,
@@ -87,6 +103,36 @@ def load_results():
         Aniso_factor_lin,
         Aniso_factor_nl,
     )
+
+
+def load_results(retrieve=False):
+    print("Loading results...")
+    if retrieve:
+        return load_results_()
+    else:
+        name = "random_case"
+        saveddir = os.path.join(data_folder, "rand_circ_rods")
+        filename = os.path.join(saveddir, name + ".npz")
+        arch = np.load(filename)
[…]

### 2019-03-11 notebooks/config/latex_config.py

@@ -1,12 +1,0 @@
-c = get_config()
-
-c.Exporter.template_file = '/templates/latex.tplx'
-c.TagRemovePreprocessor.remove_input_tags.add("rm_in")
-c.TagRemovePreprocessor.remove_all_outputs_tags.add("rm_out")
-
-# the following does the equivalent of --no-prompt, see here: https://github.com/jupyter/nbconvert/blob/master/nbconvert/nbconvertapp.py#L109-L114
-# exporter_settings = {
-#     'exclude_input_prompt' : True,
-#     'exclude_output_prompt' : True,
-# }
-# c.TemplateExporter.update(exporter_settings)

### 2019-03-11 notebooks/config/nb_config.py

@@ -1,5 +1,0 @@
-c = get_config()
-
-c.Exporter.template_file = "./templates/nb.tpl"
-c.TagRemovePreprocessor.remove_input_tags.add("rm_in")
-c.TagRemovePreprocessor.remove_all_outputs_tags.add("rm_out")

### 2019-03-11 notebooks/config/slides_config.py

@@ -1,8 +1,0 @@
-c = get_config()
-
-c.Exporter.template_file = "./templates/slides.tpl"
-c.TagRemovePreprocessor.remove_input_tags.add("rm_in")
-c.TagRemovePreprocessor.remove_all_outputs_tags.add("rm_out")
-c.SlidesExporter.reveal_theme = "simple"
-exporter_settings = {"exclude_input_prompt": True, "exclude_output_prompt": True}
-c.TemplateExporter.update(exporter_settings)

### 2019-03-11 notebooks/js/code_toggle.js

@@ -1,16 +1,0 @@
-
-  function code_toggle() {
-    if (code_shown){
-      $('div.input').hide('500');
-      $('#toggleButton').val('Show Code')
-    } else {
-      $('div.input').show('500');
-      $('#toggleButton').val('Hide Code')
-    }
-    code_shown = !code_shown
-  } 
-  
-  $( document ).ready(function(){
-    code_shown=false; 
-    $('div.input').hide()
-  });

### 2019-03-11 notebooks/js/foot.js

@@ -1,8 +1,0 @@
-
-  $(document).ready(function(){
-    $('div.prompt').hide();
-    $('div.back-to-top').hide();
-    $('nav#menubar').hide();
-    $('.breadcrumb').hide();
-    $('.hidden-print').hide();
-  });

### 2019-03-11 notebooks/js/preload.js

@@ -1,8 +1,0 @@
-
-  jQuery(document).ready(function($) {  
-  
-  $(window).on('load', function(){
-    $('#preloader').fadeOut('slow',function(){$(this).remove();});
-  });
-  
-  });

### 2019-03-11 notebooks/test.py

@@ -1,22 +1,0 @@
-from flask import Flask
-
-app = Flask(__name__)
-
-
-@app.route("/")
-def index():
-    return "Index!"
-
-
-@app.route("/hello")
-def hello():
-    return "Hello World!"
-
-
-@app.route("/members")
-def members():
-    return "Members"
-
-
-if __name__ == "__main__":
-    app.run(debug=True)

### 2019-03-14 paper/main.tex
paper

@@
 
-We use barium strontium titanate (BST) as our ferroelectric material. Microwave measurements
-at 10 GHz where performed and the normalized permittivity value
+We use barium strontium titanate (BST) as our ferroelectric material. Measurements
+have been carried out at electrostatics and at microwave frequencies, and the normalized permittivity value
 as a function of biasing field are reported on \fig{fig1}.\\
@@
 with $P_0$ being the equilibrium polarization.
-Along the direction of a uniformly applied electric field, the permittivity is given by:
-
+Along the direction of a uniform applied electric field, the relative permittivity is given by:
 \begin{equation}
-  \epsf(E) = \left[\epsvac \frac{\partial^2 F (P, E)}{\partial P^2} \right]^{-1} = \frac{\epsf(0)}{1 + \beta P_0^2 + \gamma P_0^4},
+  \epsf(E) = \left[\frac{\partial^2 F (P, E)}{\partial P^2} \right]^{-1} = \frac{\epsf(0)}{1 + \alpha P_0^2 + \beta P_0^4},
   \label{eq_epsf}
 \end{equation}
-where $\beta = 3 b \epsvac \epsf(0) /a$ and  $\gamma = 5 c \epsvac \epsf(0) /a$.
-The permittivity without bias $\epsf(0)$ was measured to be 120 and the fitting parameters
-are $a = 0.992/\epsvac$, $b=0.086/(\epsvac^3\,E_{\rm ref}^2)$, $c=0.014/(\epsvac^5\,E_{\rm ref}^4)$, $E_{\rm ref}=1$ kV/mm.
+where $\epsf(0)=1/a$, $\alpha=3b/a$ and $\beta=5c/a$. The fitting parameters are given in Table \ref{table_params_fit}.
 As the norm of the field increases, the permittivity decreases with a characteristic
@@
 \caption{Variation of the ferroelectric permittivity as a function of the
- applied electric field (green dots: measurements, grey dashed line: fit to
- formula~(\ref{eq_epsf})).}
+ applied electric field (dots: measurements, dashed lines: fit to
+ formula~(\ref{eq_epsf})), for the static case (green) and at microwave frequencies
+  (orange, $f=3.8$ GHz). The fitting parameters are given in Table \ref{table_params_fit}.}
 \label{fig1}
@@
 given by \equ{eq_epsf}.
+\begin{table}
+  \begin{tabular}{c | ccc}
+   & $\epsf(0)$  & $\alpha$ ($\rm \mu m^2/V^2$) & $\beta$ ($\rm \mu m^4/V^4$)\\ \hline
+  % \\[-1.2em]
+  static & 3050 & 0.120 & 0.024\\ \hline
+  % \\[-1.2em]
+  $f=3.8$ GHz & 165 & 0.240 & 0.079
+  \end{tabular}
+  \caption{Fitting parameters}
+  \label{table_params_fit}
+\end{table}
 
@@
 \end{equation}
-Note that for the TE case, the solution is straightforward since the structures
-are invariant along $z$, so that the electric field is equal to the uniform biasing field.
+Note that for the TE case, the solution is trivial since the structures
+are invariant along $z$, so that the electric field is equal to the uniform biasing field, and
+we will therefore not study it in the following.
 However in the TM case, the situation is much more complex: this is a coupled problem since the
@@
 are given by $\B \phi_{ij} = \langle \xitens \grad \psi_i \rangle_j$.
-Finally the homogenized permittivity  can be calculated using $\epshom_{\rm TM}=\xihom^{\rm T}/ {\rm det }(\xihom)$.\\
-On the other hand, the TE case is fairly easy to handle since the homogenized permittivity
-is simply the average of the permittivity in the unit cell:
-\begin{equation}
-\epshom_{\rm TE} = \langle \epstens \rangle .
-\label{eq_hom_TE}
-\end{equation}
+Finally the homogenized permittivity  can be calculated using $\epshom=\xihom^{\rm T}/ {\rm det }(\xihom)$.\\
+Note that the TE case, which we shall not study here as no coupling happens, is trivial since
+the homogenized permittivity is simply the average of the permittivity in the unit cell:
+$\epshom = \langle \epstens \rangle$.
 
@@
 \subsection*{Numerical setup}
-In the TM case, equations~(\ref{eq_elstat}) and (\ref{eq_hom_annex}) are solved with a Finite Element
+Equations~(\ref{eq_elstat}) and (\ref{eq_hom_annex}) are solved with a Finite Element
 Method using the open source packages Gmsh \cite{gmsh} and GetDP \cite{getdp}.
@@
  and are almost unaffected by the coupling process whereas the
- $xx$ components change drastically from the initial conditions.
+ $xx$ components change substantially from the initial conditions.
  This is due to the effect of the distribution
@@
  Due to the inhomogeneous redistribution of the permittivity over the ferroelectric domain, the
- overall tunability changes. In the case studied here, effective tunability is reduced with
- increasing dielectric concentration. There are two concurrent effect at stake here: on the one hand
+ overall tunability changes. In the case studied here, taking into account the coupling leads to an effective tunability increases with
+ increasing dielectric concentration, and is higher than the tunability of bulk ferroelectric.  There are two concurrent effect at stake here: on the one hand
  the dilution of ferroelectric makes the composite less tunable, but on the other hand,
@@
 
-\begin{figure}[!t]
+\begin{figure*}[!t]
 \centering
-\includegraphics[width=0.95\columnwidth]{conv}
-\caption{Convergence of the coupled problem in the TM polarization case.
+\includegraphics[width=0.9\textwidth]{conv_per}
+\caption{Convergence of the coupled problem.
 Real part (a) and loss tangent (b) of the components of the homogenized
  permittivity tensor as a function of iteration step $i$. The distribution of
- the electric field (colormap: magnitude, arrows: direction) and of the
+ the normalized electric field (colormap: magnitude, arrows: direction) and of the
  $xx$ component of the permittivity tensor are shown for $i=1$
-  (c and d) and $i=29$ (e and f).
+  (c and d) and $i=12$ (e and f).
  }
 \label{conv2D}
-\end{figure}
+\end{figure*}
 
@@
 \caption{Effective parameters of the 2D metamaterials as a function of the
- applied electric field for various filling fraction of dielectric, TM polarization.
+ applied electric field for various filling fraction of dielectric.
  (a): normalized permittivity, (b): normalized loss tangent, (c): normalized tunability and
@@
 
-\begin{figure}[!t]
+\begin{figure*}[!t]
 \centering
-\includegraphics[width=0.95\columnwidth]{effpar_rand}
+\includegraphics[width=0.95\textwidth]{effpar_rand_cpl}
 \caption{Effective parameters of the random 2D mixtures as a function of the
@@
 \label{eff_par_2Drand_TM}
-\end{figure}
-
-\begin{figure}[!t]
+\end{figure*}
+%
+%
+%
+\begin{figure*}[!t]
 \centering
-\includegraphics[width=0.95\columnwidth]{cvrand}
-\caption{Convergence of the coupled problem for TM polarization in the random case
+\includegraphics[width=0.95\textwidth]{conv_rand}
+\caption{Convergence of the coupled problem in the random case
 for one sample.
@@
  permittivity tensor as a function of iteration step $i$. The distribution of
- the electric field (colour map: magnitude in logarithmic scale, arrows: direction) and of the
+ the normalized electric field (colour map: magnitude in logarithmic scale, arrows: direction) and of the
  $xx$ component of the permittivity tensor are shown for $i=1$
-  (c and d) and $i=7$ (e and f).
+  (c and d) and $i=14$ (e and f).
  }
 \label{conv_random}
-\end{figure}
+\end{figure*}
 
@@
 of dielectric rods in a ferroelectric matrix in 2D, and studied their effective properties
-for TE and TM polarization as a function of dielectric concentration and bias field.
+for TM polarization as a function of dielectric concentration and bias field.
 Importantly, adding more low index and low loss dielectric allows to decrease

### 2019-03-14 ferromtm/models/bidon.py

@@ -1,67 +1,0 @@
-#!/usr/bin/env python
-# -*- coding: utf-8 -*-
-# Author: Benjamin Vial
-# License: MIT
-# import logging
-# from gridmap import grid_map
-
-
-# logging.captureWarnings(True)
-# logging.basicConfig(
-#     format=("%(asctime)s - %(name)s - %(levelname)s - " + "%(message)s"),
-#     level=logging.DEBUG,
-# )
-
-import numpy as np
-import time
-
-
-def main_rand(params, save=False, coupling=True):
-    print("fuck")
-    return params
-
-
-def main_rand_coupled(params):
-    test = main_rand(params, save=True, coupling=True)
-    return test
-
-
-# function_parallel = main_rand_coupled
-
-nE = 11
-Ebias = np.linspace(0, 2, nE)
-nF = 5
-Fincl = np.linspace(0.1, 0.5, nF)
-E1, F1 = np.meshgrid(Ebias, Fincl)
-params = np.vstack((E1.ravel(), F1.ravel())).T
-from aotomat.tools.parallelize import *
-
-# def run_parallel(params):
-#     result = grid_map(
-#         main_rand_coupled,
-#         params,
-#         quiet=False,
-#         num_slots=1,
-#         temp_dir=u"./tmp",
-#         max_processes=len(params),
-#         queue="all.q",
-#         require_cluster=True,
-#         local=True,
-#         cleanup=True,
-#     )
-#     return result
-
-
-if __name__ == "__main__":
-    run_parallel = parallel(main_rand_coupled, partype="gridmap")
-
-    # f_parallel(params)
-    tstart = time.time()
-    print("TSART: {}".format(tstart))
-    out = run_parallel(params)
-    print(out)
-    # f_parallel(params, save=True, coupling=False)
-    tend = time.time()
-    et = tend - tstart
-    print("TEND: {}".format(tend))
-    print("ELAPSED: {}s".format(et))

### 2019-03-14 ferromtm/models/bst.py

@@ -106,12 +106,12 @@ if __name__ == "__main__":
 
     plt.close("all")
     fig = plt.figure(figsize=(5, 3))
-    plt.plot(E_exp, eps_norm_exp[0], "o", label="measured, $f=0$", color="#3e8b58")
-    plt.plot(E_fit, eps_norm_fit[0], "--", color="#3e8b58", label="fit, $f=0$")
+    plt.plot(E_exp, eps_norm_exp[0], "o", label="measured, static", color="#3e8b58")
+    plt.plot(E_fit, eps_norm_fit[0], "--", color="#3e8b58", label="fit, static")
     plt.plot(
-        E_exp, eps_norm_exp[1], "o", label="measured, $f=3.8$ GHz", color="#b05151"
+        E_exp, eps_norm_exp[1], "o", label="measured, $f=3.8$ GHz", color="#eb931e"
     )
-    plt.plot(E_fit, eps_norm_fit[1], "--", color="#b05151", label="fit, $f=3.8$ GHz")
+    plt.plot(E_fit, eps_norm_fit[1], "--", color="#eb931e", label="fit, $f=3.8$ GHz")
     plt.ylabel(r"normalized permittivity")
     # $\varepsilon^{\rm f}/\varepsilon^{\rm f}(E=0)$
     plt.xlabel("electric field (MV/m)")

### 2019-03-14 ferromtm/models/coupled2D.py

@@ -32,10 +32,18 @@ from pytheas.tools.utils import refine_mesh
 rootdir = os.path.dirname(os.path.dirname(ferromtm.__file__))
 
 
+#
+# def epsilonr_ferroelectric(E, dc=True):
+#     eps = 20
+#     return np.ones_like(E)*eps
+
 pi = np.pi
 eps_incl = 3
 data_folder = os.path.join(rootdir, "data", "results")
 mat_folder = os.path.join(rootdir, "data", "mat")
+cv_dir_ = "circ_rods"
+# cv_dir_ = "rand_circ_rods"
+cv_dir = os.path.join(data_folder, cv_dir_, "convergence")
 
 
 def ellipse(Rinclx, Rincly, rot_incl, x0, y0):
@@ -140,6 +148,8 @@ def init_es(f, E_bias, incl=True, mat=None):
     fem_es.dx = 1
     fem_es.dy = 1
     fem_es.dz = 1
+    fem_es.Nix = 501
+    fem_es.Niy = 501
     fem_es.r = r
     fem_es.f = f
     fem_es.eps_incl = eps_incl
@@ -182,6 +192,8 @@ def init_hom(fem_es):
     fem_hom.dx = fem_es.dx
     fem_hom.dy = fem_es.dy
     fem_hom.dz = fem_es.dz
+    fem_hom.Nix = fem_es.Nix
+    fem_hom.Niy = fem_es.Niy
     fem_hom.eps_incl = fem_es.eps_incl
     fem_hom.eps_host = fem_es.eps_host
     fem_hom.tmp_dir = tempfile.mkdtemp(prefix="/tmp/benjaminv.")
@@ -259,8 +271,8 @@ def ppEmap(fem):
 
 def ppEpsimap(fem):
     fem.postpro_fields()
-    eps_xx = fem.get_field_map("epsilonr_xx.txt").real
-    eps_yy = fem.get_field_map("epsilonr_yy.txt").real
+    eps_xx = fem.get_field_map("epsilonr_xx.txt")
+    eps_yy = fem.get_field_map("epsilonr_yy.txt")
     return eps_xx, eps_yy
 
 
@@ -275,12 +287,14 @@ def coupling_loop(fem_es, epsi, tol=1e-2, max_iter=100, verbose=False, record_cv
         # E, fem_es = compute_elstat_pb(fem_es, epsi)
         fem_hom = init_hom(fem_es)
         epsi_rf = epsilonr_ferroelectric(E0)
+
[…]

### 2019-03-14 ferromtm/models/slab.py

@@ -1,0 +1,203 @@
+import numpy as np
+from pytheas.material import genmat
+from pytheas import periodic2D, utils
+from pytheas.periodic2D import Periodic2D
+from ferromtm.models.coupled2D import *
+from ferromtm.visualization.plots import *
+import tempfile
+
+plt.close("all")
+
+
+cv_dir_ = "circ_rods"
+# cv_dir_ = "rand_circ_rods"
+cv_dir = os.path.join(data_folder, cv_dir_, "convergence")
+
+
+def load_arch(iter):
+    fname = "cv_iter_{}.npz".format(iter)
+    filename = os.path.join(cv_dir, fname)
+    arch = np.load(filename)
+    eps_hom = arch["eps_hom"]
+    epsi = arch["epsi_map"]
+    E = arch["E_map"]
+    return epsi, E, eps_hom
+
+
+pi = np.pi
+f = 0.5
+E0 = 2
+rincl = (f / pi) ** 0.5
+nincly = 5
+dx = 1
+
+ef = epsilonr_ferroelectric(E0)
+epsi = [ef, 3]
+matprop = [np.sqrt(e) for e in epsi]
+fem = Periodic2D()
+
+fem.lambda0 = 150  #: flt: incident wavelength
+
+# opto-geometric parameters  -------------------------------------------
+fem.d = 1  #: flt: period
+fem.h_sup = fem.lambda0 * 2  #: flt: "thickness" superstrate
+fem.h_sub = fem.lambda0 * 2  #: flt: "thickness" substrate
+fem.h_layer1 = 1  #: flt: thickness layer 1
+fem.h_layer2 = 1  #: flt: thickness layer 2
+fem.h_des = nincly * dx  #: flt: thickness layer design
+fem.h_pmltop = fem.lambda0  #: flt: thickness pml top
+fem.h_pmlbot = fem.lambda0  #: flt: thickness pml bot
+fem.a_pml = 1  #: flt: PMLs parameter, real part
+fem.b_pml = 1  #: flt: PMLs parameter, imaginary part
+fem.eps_sup = 1  #: flt: permittivity superstrate
+fem.eps_sub = 1  #: flt: permittivity substrate
+fem.eps_layer1 = 1  #: flt: permittivity layer 1
+fem.eps_layer2 = 1  #: flt: permittivity layer 2
+fem.eps_des = 1  #: flt: permittivity layer design
+
+fem.theta_deg = 0.0  #: flt: incident angle
[…]

### 2019-03-14 ferromtm/visualization/plots.py

@@ -1,6 +1,6 @@
 import matplotlib as mpl
 
-# mpl.use("Qt4Agg")
+# mpl.use("Qt5Agg")
 
 mpl.rcParams["legend.fancybox"] = False
 mpl.rcParams["legend.fontsize"] = "small"

### 2019-03-14 ferromtm/visualization/postpro2D_conv.py

@@ -1,5 +1,6 @@
 from ferromtm.models.coupled2D import *
 from ferromtm.visualization.plots import *
+from matplotlib.ticker import MaxNLocator
 
 
 n_bulk = tunability(epsilonr_ferroelectric(Ebias), epsilonr_ferroelectric(0))
@@ -7,9 +8,12 @@ K_bulk = cqf(epsilonr_ferroelectric(Ebias), epsilonr_ferroelectric(0))
 eps_00 = epsilonr_ferroelectric(0).real
 tandelta_00 = -epsilonr_ferroelectric(0).imag / epsilonr_ferroelectric(0).real
 
+cv_dir_ = "circ_rods"
+cv_dir_ = "rand_circ_rods"
+cv_dir = os.path.join(data_folder, cv_dir_, "convergence")
+
 
 def load_arch(iter):
-    cv_dir = os.path.join(data_folder, "circ_rods", "convergence")
     fname = "cv_iter_{}.npz".format(iter)
     filename = os.path.join(cv_dir, fname)
     arch = np.load(filename)
@@ -19,9 +23,8 @@ def load_arch(iter):
     return epsi, E, eps_hom
 
 
-iplot = [0, 1, 2, 3, 4]
-
-ncv = 13
+ncv = 13  # periodic
+ncv = 15  # random
 
 
 def load_results():
@@ -57,13 +60,14 @@ def plotEarrows(ax, Enewx, Enewy):
     dd = np.linspace(0, nx - 1, nx)
     X0, Y0 = np.meshgrid(dd, dd)
     X, Y = X0[::dspl, ::dspl], Y0[::dspl, ::dspl]
+    X, Y = X0, Y0
 
     U0 = Enewx[::dspl, ::dspl].T
     V0 = Enewy[::dspl, ::dspl].T
     normarrow = np.sqrt(U0 ** 2 + V0 ** 2)
-    U = U0 / 1
-    V = V0 / 1
-    ax.streamplot(X, Y, U, V, density=1, linewidth=0.25 * (normarrow), color="k")
+    U = U0
+    V = V0
+    ax.streamplot(X, Y, U, V, density=1, linewidth=1, color="#ababab")
 
 
 def plot_E_map_conv(axtmp, i, label=None):
@@ -77,7 +81,7 @@ def plot_E_map_conv(axtmp, i, label=None):
     Enp = Enp.T / normE0
     Enp[epsp <= 3] = np.NaN
[…]

### 2019-03-18 paper/main.tex
writting up paper

@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-\documentclass[%
- reprint,
-%superscriptaddress,
-%groupedaddress,
-%unsortedaddress,
-%runinaddress,
-%frontmatterverbose,
-%preprint,
-%preprintnumbers,
-%nofootinbib,
-%nobibnotes,
-%bibnotes,
- amsmath,amssymb,
- aps,
-%pra,
-%prb,
-%rmp,
-%prstab,
-%prstper,
-%floatfix,
-]{revtex4-2}
+%% Author_tex.tex
+%% V1.0
+%% 2012/13/12
+%% developed by Techset
+%%
+%% This file describes the coding for rsproca.cls
+
+\documentclass[openacc]{rsproca_new}%%%%where rsproca is the template name
 
@@
 \usepackage{bm}
-%%%%%%%%%%%%%%%%%% Commands %%%%%%%%%%%%%%%%%
-
-% include bbl file (arXiv)
-\newif\ifbbl
-% \bblfalse
-\bbltrue
 
@@
 
+%%%% *** Do not adjust lengths that control margins, column widths, etc. ***
+
+%%%%%%%%%%% Defining Enunciations  %%%%%%%%%%%
+\newtheorem{theorem}{\bf Theorem}[section]
+\newtheorem{condition}{\bf Condition}[section]
+\newtheorem{corollary}{\bf Corollary}[section]
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{document}
 
+%%%% Article title to be placed here
 \title{Homogenization of periodic and random ferroelectric-dielectric composites}
+\author{Benjamin Vial and Yang Hao}
 
-% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
-\author{Benjamin Vial and Yang Hao}
-\affiliation{School of Engineering and Computer Science, Queen Mary, University of London, London, E1 4NS, United Kingdom}
-% \eads{\mailto{b.vial@qmul.ac.uk}, \mailto{y.hao@qmul.ac.uk}}
+%%%%%%%%% Insert author address here
+\address{School of Engineering and Computer Science, Queen Mary, University of London, London, E1 4NS, United Kingdom}
 
+%%%% Subject entries to be placed here %%%%
+\subject{xxxxx, xxxxx, xxxx}
+
+%%%% Keyword entries to be placed here %%%%
+\keywords{Homogenization, Ferroelectrics, Metamaterials , Tunability}
+
+%%%% Insert corresponding author and its email address}
+\corres{Benjamin Vial\\
+\email{b.vial@qmul.ac.uk}}
+
+%%%% Abstract text to be placed here %%%%%%%%%%%%
 \begin{abstract}
@@
 \end{abstract}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\keywords{Homogenization, Ferroelectrics, Metamaterials , Tunability}
+%%%%%%%%%% Insert the texts which can accomdate on firstpage in the tag "fmtext" %%%%%
 
-\maketitle
-
+\begin{fmtext}
   \section{Introduction}
@@
   applications. Thus it has been considered to mix ferroelectric ceramics to low-index and
-low-loss non-tunable dielectrics in order to reduce both permittivity value and losses.
+  low-loss non-tunable dielectrics in order to reduce both permittivity
+\end{fmtext}
+
+%%%%%%%%%%%%%%% End of first page %%%%%%%%%%%%%%%%%%%%%
+
+\maketitle
+\noindent values and losses.
 The effective parameters of those composites have been investigated \cite{Sherman2006,
@@
 anisotropy significantly differ. \\
-We first a two-dimensional model of metamaterials made of parallel rods with circular cross section,
-considering both periodic and random distributions.
+We study first a two-dimensional model of metamaterials made of parallel rods with circular cross section,
+considering both square periodic arrays and random distributions within the unit cell of
+a periodic array.
 
@@
 
-\section*{Theory and numerical model}
+\section{Theory and numerical model}
 
@@
 % -------------------------------------------------------------------------------
-\subsection*{Permittivity model\label{permmodel}}
+\subsection{Permittivity model\label{permmodel}}
 
@@
 given by $F(P,E) = F_0 +  a P^2/2 + b P^4/4 + cP^6/6 - EP$, where $E$ is
-the applied electric field and $P$ is the polarization \cite{Zhou2008}. Variations of the
+the applied electric field and $P$ is the polarization \cite{landau_electrodynamics_2013, Zhou2008}. Variations of the
 permittivity with the temperature can be taken into account through the
@@
 \centering
-\includegraphics[width=1\columnwidth]{epsilon_fit}
+\includegraphics[width=0.8\columnwidth]{epsilon_fit}
 \caption{Variation of the ferroelectric permittivity as a function of the
@@
 where each of the diagonal components have the functional form
-given by \equ{eq_epsf}.
+given by \equ{eq_epsf}. Note that we will use the static values of permittivity
+for the electrostatic modelling, while we are interrested in the homogenized values
+of permittivity at microwaves.\\
 \begin{table}
-  \begin{tabular}{c | ccc}
-   & $\epsf(0)$  & $\alpha$ ($\rm \mu m^2/V^2$) & $\beta$ ($\rm \mu m^4/V^4$)\\ \hline
-  % \\[-1.2em]
-  static & 3050 & 0.120 & 0.024\\ \hline
-  % \\[-1.2em]
-  $f=3.8$ GHz & 165 & 0.240 & 0.079
+  \caption{Fitting parameters to model (\ref{eq_epsf}) for the measured permittivity values as a function
+  of applied electrc field shown on \fig{fig1}. }
+  \label{table_params_fit}
+  \begin{tabular}{llll}
+    \hline
+   case & $\epsf(0)$  & $\alpha$ ($\rm \mu m^2/V^2$) & $\beta$ ($\rm \mu m^4/V^4$)\\ \hline
+  static & 3050 & 0.120 & 0.024\\
+  $f=3.8$ GHz & 165 & 0.240 & 0.079 \\\hline
   \end{tabular}
-  \caption{Fitting parameters}
-  \label{table_params_fit}
 \end{table}
@@
 % -------------------------------------------------------------------------------
-\subsection*{Electrostatic model}
+\subsection{Electrostatic model}
 The composites under study are made of two materials, thus their permittivity
@@
 % -------------------------------------------------------------------------------
-\subsection*{Homogenization}
+\subsection{Homogenization}
 The effective permittivity for TM polarization is calculated
@@
 % -------------------------------------------------------------------------------
-\subsection*{Numerical setup}
+\subsection{Numerical setup}
 Equations~(\ref{eq_elstat}) and (\ref{eq_hom_annex}) are solved with a Finite Element
@@
 
-\section*{Numerical results}
+\section{Numerical results}
 In the following numerical results, the dielectric phase is supposed to be
-lossless with $\epsd = 3$ while the ferroelectric material follows the
+lossless and non dispersive with $\epsd = 3$ while the ferroelectric material follows the
 permittivity described in section~\ref{permmodel} and has a constant loss
@@
 % -------------------------------------------------------------------------------
-\subsection*{Two dimensional periodic metamaterial}
+\subsection{Two dimensional periodic metamaterial}
+\begin{figure}[!t]
+\centering
+\includegraphics[width=1\textwidth]{conv_per}
+\caption{Convergence of the coupled problem.
+Real part (a) and loss tangent (b) of the components of the homogenized
+ permittivity tensor as a function of iteration step $i$. The distribution of
+ the normalized electric field (colormap: magnitude, arrows: direction) and of the
+ $xx$ component of the permittivity tensor are shown for $i=1$
+  (c and d) and $i=12$ (e and f).
+ }
+\label{conv2D}
+\end{figure}
 Lets us now consider infinitely long dielectric rods of circular cross section
@@
  This is due to the effect of the distribution
- of the electrostatic field within the unit cell (see Figs.~(\ref{conv2D})(c) and \ref{conv2D}(d)),
+ of the electrostatic field within the unit cell (see Figs.~(\ref{conv2D}.c) and (\ref{conv2D}.d)),
  where the $x$ component of the electric field is still much stronger
@@
  At equilibrium, the electric field is concentrated close to the $y$ axis in between two neighbouring
- rods. This in turn affects the permittivity distribution (see Figs.~(\ref{conv2D})(e) and \ref{conv2D}(f)),
+ rods. This in turn affects the permittivity distribution (see Figs.~(\ref{conv2D}.e) and (\ref{conv2D}.f)),
  and the homogenized properties of the composite.\\
@@
  Due to the inhomogeneous redistribution of the permittivity over the ferroelectric domain, the
- overall tunability changes. In the case studied here, taking into account the coupling leads to an effective tunability increases with
- increasing dielectric concentration, and is higher than the tunability of bulk ferroelectric.  There are two concurrent effect at stake here: on the one hand
+ overall tunability changes. In the case studied here, taking into account the coupling leads to an effective tunability increase with
+ higher dielectric concentration, and that is larger than the tunability of bulk ferroelectric.  There are two concurrent effect at stake here: on the one hand
  the dilution of ferroelectric makes the composite less tunable, but on the other hand,
@@
 This geometric effect is added to the anisotropy arising from the material properties of the ferroelectric
-phase, and depending on the topology and permittivity of the rods, one effect would be predominant.
+phase itself, and depending on the topology and permittivity of the rods, one effect would be predominant.
 Those subtle phenomena can only be rigorously taken into account by employing a coupling formalism
@@
 
-\begin{figure*}[!t]
+\begin{figure}[!t]
 \centering
-\includegraphics[width=0.9\textwidth]{conv_per}
-\caption{Convergence of the coupled problem.
-Real part (a) and loss tangent (b) of the components of the homogenized
- permittivity tensor as a function of iteration step $i$. The distribution of
- the normalized electric field (colormap: magnitude, arrows: direction) and of the
- $xx$ component of the permittivity tensor are shown for $i=1$
-  (c and d) and $i=12$ (e and f).
- }
-\label{conv2D}
-\end{figure*}
-
-\begin{figure*}[!t]
-\centering
-\includegraphics[width=0.8\textwidth]{effpar_per}
+\includegraphics[width=1\textwidth]{effpar_per}
 \caption{Effective parameters of the 2D metamaterials as a function of the
@@
 \label{eff_par_2D_TM}
-\end{figure*}
+\end{figure}
 
 % -------------------------------------------------------------------------------
-\subsection*{Random case}
+\subsection{Random case}
+\begin{figure}
+\centering
+\includegraphics[width=0.8\columnwidth]{randmatepsi}
+\caption{Permittivity distribution of the numerical samples used for $f=0.5$. Dark
+colour indicates the ferroelectric material while light colour represents the
+dielectric inclusions.}
+\label{randmatepsi}
+\end{figure}
+
 We finally study the effect of random particle distribution on the effective parameters of the
@@
 
-\begin{figure}
+\begin{figure}[!t]
 \centering
-\includegraphics[width=1\columnwidth]{randmatepsi}
-\caption{Permittivity distribution of the numerical samples used for $f=0.5$. Dark
-colour indicates the ferroelectric material while light colour represents the
-dielectric inclusions.}
-\label{randmatepsi}
-\end{figure}
-
-\begin{figure*}[!t]
-\centering
-\includegraphics[width=0.95\textwidth]{effpar_rand_cpl}
+\includegraphics[width=1\textwidth]{effpar_rand_cpl}
 \caption{Effective parameters of the random 2D mixtures as a function of the
- applied electric field for various filling fraction of dielectric, TM polarization.
+ applied electric field for various filling fraction of dielectric, when the
+ coupling is taken into account.
  (a): normalized permittivity, (b): normalized loss tangent, (c): normalized tunability and
@@
 \label{eff_par_2Drand_TM}
-\end{figure*}
+\end{figure}
 %
@@
 %
-\begin{figure*}[!t]
+\begin{figure}[!t]
 \centering
-\includegraphics[width=0.95\textwidth]{conv_rand}
+\includegraphics[width=1\textwidth]{conv_rand}
 \caption{Convergence of the coupled problem in the random case
@@
 \label{conv_random}
-\end{figure*}
+\end{figure}
 
@@
 
-\section*{Conclusion}
+\section{Conclusion}
 
@@
 
+\vskip6pt
+
+\enlargethispage{20pt}
+
+\ethics{Insert ethics text here.}
+
+\dataccess{Insert data accessibility text here. '(If no information, then please include the text ``This article has no additional data'').}
+
+\aucontribute{Insert author contributions text here (to be included if more than one author).}
+
+\competing{The authors declare no competing interrests.}
+
+\funding{his work was funded by the Engineering and Physical Sciences Research Council (EPSRC), UK, under a grant (EP/P005578/1) 'Adaptive Tools for Electromagnetics and Materials Modelling to Bridge the Gap between Design and Manufacturing (AOTOMAT)'.}
+
+\ack{The authors would like to thanks Henry Giddens for performing the measurements of ferroelectric permittivity used in this paper.}
+
+\disclaimer{Insert disclaimer text here.}
+
+%%%%%%%%%% Insert bibliography here %%%%%%%%%%%%%%
+
+\vskip2pc
+
+% \begin{thebibliography}{9}
 %
-%
-% \ack
-% This work was funded by the Engineering and Physical Sciences Research Council
-% (EPSRC), UK, under a grant (EP/P005578/1) 'Adaptive Tools for
-% Electromagnetics and Materials Modelling to Bridge the Gap between Design and Manufacturing (AOTOMAT)'.
-% The authors would like to thanks Henry Giddens for performing the measurements of
-% ferroelectric permittivity used in this paper.
+% \end{thebibliography}
 
-\section*{References}
-% \bibliographystyle{iopart-num}
+\bibliographystyle{RS}
 \bibliography{biblio}
@@
 \end{document}
+%
+%
+%
+% \begin{fmtext}
+% \section{Insert A head here}
+% %%%% Insert A head here
+%
+% This demo file is intended to serve as a ``starter file''
+% for rsproca journal papers produced under \LaTeX\ using
+% rsproca\_new.cls v1.0.
+%
+% \subsection{Insert B head here}
+% %%%% Insert B head here
+% Subsection text here.
+%
+% \subsubsection{Insert C head here}
+% %%%% Insert C head here
+% Subsubsection text here.
+%
+% \section{Equations}
+%
+% Sample equations.
+%
+% %%% Numbered equation
+% \begin{align}\label{1.1}
+% \begin{split}
+% \frac{\partial u(t,x)}{\partial t} &= Au(t,x) \left(1-\frac{u(t,x)}{K}\right)-B\frac{u(t-\tau,x) w(t,x)}{1+Eu(t-\tau,x)},\\
+% \frac{\partial w(t,x)}{\partial t} &=\delta \frac{\partial^2w(t,x)}{\partial x^2}-Cw(t,x)+D\frac{u(t-\tau,x)w(t,x)}{1+Eu(t-\tau,x)},
+% \end{split}
+% \end{align}
+%
+% \begin{align}\label{1.2}
+% \begin{split}
+% \frac{dU}{dt} &=\alpha U(t)(\gamma -U(t))-\frac{U(t-\tau)W(t)}{1+U(t-\tau)},\\
+% \frac{dW}{dt} &=-W(t)+\beta\frac{U(t-\tau)W(t)}{1+U(t-\tau)}.
+% \end{split}
+% \end{align}
+%
+% %%%% Unnumbered equation
+% \begin{eqnarray}
+% \frac{\partial(F_1,F_2)}{\partial(c,\omega)}_{(c_0,\omega_0)} = \left|
+% \begin{array}{ll}
+% \frac{\partial F_1}{\partial c} &\frac{\partial F_1}{\partial \omega} \\\noalign{\vskip3pt}
+% \frac{\partial F_2}{\partial c}&\frac{\partial F_2}{\partial \omega}
+% \end{array}\right|_{(c_0,\omega_0)}\notag\\
+% =-4c_0q\omega_0 -4c_0\omega_0p^2 =-4c_0\omega_0(q+p^2)>0.
+% \end{eqnarray}
+% \end{fmtext}
+%
+% %%%%%%%%%%%%%%% End of first page %%%%%%%%%%%%%%%%%%%%%
+%
+% \maketitle
+%
+% \section{Enunciations}
+%
+% \begin{theorem}\label{T0.1}
+% Assume that $\alpha>0, \gamma>1, \beta>\frac{\gamma+1}{\gamma-1}$.
+% Then there exists a small $\tau_1>0$, such that for $\tau\in
+% [0,\tau_1)$, if $c$ crosses $c(\tau)$ from the direction of
+% to  a small amplitude periodic traveling wave solution of
+% (2.1), and the period of $(\check{u}^p(s),\check{w}^p(s))$ is
+% \[
+% \check{T}(c)=c\cdot \left[\frac{2\pi}{\omega(\tau)}+O(c-c(\tau))\right].
+% \]
+% \end{theorem}
+%
+%
+% \begin{condition}\label{C2.2}
+% From (0.8) and (2.10), it holds
+% $\frac{d\omega}{d\tau}<0,\frac{dc}{d\tau}<0$ for $\tau\in
+% [0,\tau_1)$. This fact yields that the system (2.1) with delay
+% $\tau>0$ has the periodic traveling waves for smaller wave speed $c$
+% than that the system (2.1) with $\tau=0$ does. That is, the
+% delay perturbation stimulates an early occurrence of the traveling waves.
+% \end{condition}
+%
+%
+% \section{Figures \& Tables}
+%
+% The output for figure is:\vspace*{-7pt}
+%
+% \begin{figure}[!h]
+% %\centering\includegraphics[width=2.5in]{xxxxxx.eps}
+% %%% where xxxxxx name represents "figurename.eps"
+% \caption{Insert figure caption here}
+% \label{fig_sim}
+% \end{figure}
+%
+% \vspace*{-5pt}
+%
+% \noindent The output for table is:\vspace*{-7pt}
+%
+% \begin{table}[!h]
+% \caption{An Example of a Table}%%%Table caption goes here
+% \label{table_example}
+% \begin{tabular}{llll}%%%The number of columns has to be defined here
+% \hline
+% date &Dutch policy &date &European policy \\
+% \hline
+% 1988 &Memorandum Prevention &1985 &European Directive (85/339) \\
+% 1991--1997 &{\bf Packaging Covenant I} & & \\
+% 1994 &Law Environmental Management &1994 &European Directive (94/62) \\
+% 1997 &Agreement Packaging and Packaging Waste & & \\\hline
+% \end{tabular}
+% \vspace*{-4pt}
+% \end{table}%%%End of the table
+%
+% \section{Conclusion}
+% The conclusion text goes here.
+%
+% \vskip6pt
+%
+% \enlargethispage{20pt}
+%
+% \ethics{Insert ethics text here.}
+%
+% \dataccess{Insert data accessibility text here. '(If no information, then please include the text ``This article has no additional data'').}
+%
+% \aucontribute{Insert author contributions text here (to be included if more than one author).}
+%
+% \competing{Insert competing interests text here.}
+%
+% \funding{Insert funding text here.}
+%
+% \ack{Insert acknowledgment text here.}
+%
+% \disclaimer{Insert disclaimer text here.}
+%
+% %%%%%%%%%% Insert bibliography here %%%%%%%%%%%%%%
+%
+% \vskip2pc
+%
+% % \begin{thebibliography}{9}
+% %
+% % \end{thebibliography}
+%
+% \bibliographystyle{RS}
+% \bibliography{biblio}

### 2019-03-20 paper/main.tex
dev

@@
   we study the effective permittivity, losses, electrically induced anisotropy and tunability
-   of the homogenized materials.
+   of those metamaterials.
 \end{abstract}
@@
   \section{Introduction}
-
-  Ferroelectric materials play a crucial role in tunable
+  Ferroelectric materials play a crucial role in reconfigurable 
   microwave devices, with typical applications including antenna beam steering,
   phase shifters, tunable power splitters, filters, voltage controlled oscillators and
-  matching networks \cite{Tagantsev2018}. Both bulk ceramics and thin films have
-  been employed to design frequency agile components \cite{vendik1999ferroelectric, lancaster1998thin,
-  xi2000oxide} and metamaterials \cite{Hand2008, Zhao2008}. The main reason of using
+  matching networks \cite{tagantsev_ferroelectric_2018}. Both bulk ceramics and thin films have
+  been employed to design frequency agile components \cite{vendik_ferroelectric_1999, lancaster_thin-film_1998,xi_oxide_2000} and metamaterials \cite{hand_frequency_2008, zhao_experimental_2008}.
+The main reason of using
   ferroelectric materials is their strong dependence of their permittivity $\varepsilon$
@@
 \noindent values and losses.
-The effective parameters of those composites have been investigated \cite{Sherman2006,
-jylha2008tunability, Sherman2004, ASTAFIEV20032381} and it has been found that the
+The effective parameters of those composites have been investigated \cite{sherman_ferroelectric-dielectric_2006, jylha_tunability_2008, sherman_tunability_2004, astafiev_can_2003} and it has been found that the
 permittivity can be greatly reduced while losses and tunability are much less sensitive to the
@@
 This study investigates the effective permittivity of dielectric/ferroelectric composites
-by using a two-scale convergence method \cite{Allaire92, Guenneau2000}.
+by using a two-scale convergence method \cite{allaire_homogenization_1992, guenneau_homogenization_2000}.
 The originality lies in the fact that a fully coupling model is employed to
@@
 given by $F(P,E) = F_0 +  a P^2/2 + b P^4/4 + cP^6/6 - EP$, where $E$ is
-the applied electric field and $P$ is the polarization \cite{landau_electrodynamics_2013, Zhou2008}. Variations of the
+the applied electric field and $P$ is the polarization \cite{landau_electrodynamics_2013, zhou_dielectric_2008}. Variations of the
 permittivity with the temperature can be taken into account through the
@@
 are oriented in the coordinate directions, and that the diagonal components of the permittivity
-tensor are only function of the corresponding bias electric field components \cite{Krowne2002}, we have:
+tensor are only function of the corresponding bias electric field components \cite{krowne_anisotropic_2002}, we have:
 \begin{equation}
@@
 The effective permittivity for TM polarization is calculated
-using two scale homogenization technique \cite{Allaire92, Guenneau2000}.
+using two scale homogenization technique \cite{allaire_homogenization_1992, guenneau_homogenization_2000}.
 For this purpose, one has to find the solutions
@@
 \end{equation}
-where $\B r = (x, y)^T$ is the position vector in the $xy$ plane and
+where $\B r = (x, y)^{\rm T}$ is the position vector in the $xy$ plane and
 $\xitens=\epstens^{\rm T}/ {\rm det }(\epstens)$.
@@
 Equations~(\ref{eq_elstat}) and (\ref{eq_hom_annex}) are solved with a Finite Element
-Method using the open source packages Gmsh \cite{gmsh} and GetDP \cite{getdp}.
+Method using the open source packages Gmsh \cite{geuzaine_gmsh:_2009} and GetDP \cite{dular_general_1998}.
 In both cases we use a square unit cell $\Omega$ of length $d$ with periodic boundary
 conditions along $x$ and $y$. Second order Lagrange elements are used and the
-solution is computed with a direct solver (MUMPS \cite{MUMPS}).
+solution is computed with a direct solver (MUMPS \cite{amestoy_fully_2001}).
 % The source code and
@@
  it would be of great interest to use high contrast homogenization theory
- \cite{BOUCHITTE2004377, cherednichenko_cooper_2015} to
+ \cite{bouchitte_homogenization_2004, cherednichenko_homogenization_2015} to
  study this kind of mixtures.

### 2019-03-21 paper/main.tex
analytical R coeffs aniso slab

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% Coupled model and homogenization of dielectric-ferroelectric mixtures.
+%
+% We will present the study of the effective permittivity tensor of ferroelectric-dielectric composites under a static electric field.
+A refined model is used to take into account the coupling between the electrostatic problem and the electric field dependent permittivity of the ferroelectric medium.
+Periodic and random arrays of dielectric rods in a ferroelectric matrix are investigated and we study the effective permittivity, losses, electrically induced anisotropy and tunability of those metamaterials using a two-scale homogenization method.
 
@@
 permittivity can be greatly reduced while losses and tunability are much less sensitive to the
-dielectric phase addition.\\
+dielectric phase addition.
+\\
 This study investigates the effective permittivity of dielectric/ferroelectric composites
@@
 \begin{equation}
-\div (\epsvac \epstens \grad V) = 0
+\div (\epstens \grad V) = 0
 \label{eq_elstat}
@@
 $\xitens=\epstens^{\rm T}/ {\rm det }(\epstens)$.
-The homogenized coefficient $\xihom$ is obtained with:
+The homogenized tensor $\xihom$ is obtained with:
 \begin{equation}
@@
 are given by $\B \phi_{ij} = \langle \xitens \grad \psi_i \rangle_j$.
-Finally the homogenized permittivity  can be calculated using $\epshom=\xihom^{\rm T}/ {\rm det }(\xihom)$.\\
+Finally the effective permittivity tensor can be calculated using $\epshom=\xihom^{\rm T}/ {\rm det }(\xihom)$.\\
 Note that the TE case, which we shall not study here as no coupling happens, is trivial since

### 2019-03-21 ferromtm/models/slab.py

@@ -79,14 +79,19 @@ fem.aniso = True
 
 
 def main(t, coupled=True, homogenized=False):
-    fem.tmp_dir = tempfile.mkdtemp(prefix="/tmp/benjaminv.")
-    fem.initialize()
-    mesh = fem.make_mesh()
     if coupled:
         iter = 12  # periodic
     else:
         iter = 0
     epsi_map, E_map, eps_hom = load_arch(iter)
+    fem.tmp_dir = tempfile.mkdtemp(prefix="/tmp/benjaminv.")
+    fem.theta_deg = t
+    ct = np.cos(t * pi / 180)
+    fem.h_pmltop = fem.lambda0 / ct  #: flt: thickness pml top
+    fem.h_pmlbot = fem.lambda0 / ct  #: flt: thickness pml bot
+    fem.initialize()
+    mesh = fem.make_mesh()
+
     epsi_xx = epsi_map[0]
     epsi_yy = epsi_map[1]
     n_x, n_y = epsi_xx.shape
@@ -106,7 +111,7 @@ def main(t, coupled=True, homogenized=False):
     make_pos_tensor_eps(fem, epsi, interp=True)
 
     effs = []
-    fem.theta_deg = t
+
     fem.compute_solution()
     effs = fem.diffraction_efficiencies()
     print("efficiencies", effs)
@@ -188,16 +193,16 @@ if __name__ == "__main__":
     plt.legend()
     plt.xlabel("incident angle (degree)")
     plt.ylabel("Reflection")
-    plt.xlim((0, 80))
+    plt.xlim((0, 90))
     plt.ylim((0, 1))
 
     plt.figure()
-    plt.plot(angle, Q_meta, "-r", alpha=0.5, lw=4, label="MTM coupled")
-    plt.plot(angle, Q_hom, "--r", label="hom. coupled")
-    plt.plot(angle, Q_meta_uncpl, "-b", alpha=0.5, lw=4, label="MTM uncoupled")
-    plt.plot(angle, Q_hom_uncpl, "--b", label="hom. uncoupled")
+    plt.plot(angle, T_meta, "-r", alpha=0.5, lw=4, label="MTM coupled")
+    plt.plot(angle, T_hom, "--r", label="hom. coupled")
+    plt.plot(angle, T_meta_uncpl, "-b", alpha=0.5, lw=4, label="MTM uncoupled")
[…]

### 2019-03-21 ferromtm/models/slab_analytical.py

@@ -1,0 +1,86 @@
+import numpy as np
+from pytheas.material import genmat
+from pytheas import periodic2D, utils
+from pytheas.periodic2D import Periodic2D
+from ferromtm.models.coupled2D import *
+from ferromtm.visualization.plots import *
+import tempfile
+
+plt.close("all")
+
+
+def rslab(h, lambda0, theta, epsxx, epsyy):
+    """reflection coefficient for TM polarization of a
+    slab with diagonal permittivity in vacuum"""
+
+    t = pi * theta / 180
+    ct = np.cos(t)
+    st = np.sin(t)
+    k0 = 2 * pi / lambda0
+    k0x = k0 * st
+    k0y = k0 * ct
+    ky = k0 * (np.sqrt(epsxx * (1 - st ** 2 / epsyy)))
+
+    r1 = (k0y - ky / epsxx) / (k0y + ky / epsxx)
+    expo = np.exp(-2 * 1j * ky * h)
+    r = r1 * (1 - expo) / (1 - r1 ** 2 * expo)
+    return r
+
+
+#
+#
+#
+# def rslab_iso(h, lambda0, theta, eps):
+#     """reflection coefficient for TM polarization of a
+#     slab with diagonal permittivity in vacuum"""
+#
+#     t = pi * theta / 180
+#     ct = np.cos(t)
+#     st = np.sin(t)
+#     k0 = 2 * pi / lambda0
+#
+#     k1 = k0
+#     k2 = k0 * np.sqrt(eps)
+#     a1 = -k1 * st
+#
+#     b1 = k1 * ct
+#     b2 = np.sqrt(k2 ** 2 - a1 ** 2)
+#
+#     r12 = (b1 - b2 / eps) / (b1 + b2 / eps)
+#
+#     cti = np.conj(np.sqrt(1 - st ** 2 / eps + 0j))
+#     deltai = cti * k0 * np.sqrt(eps) * h
+#     expo = np.exp(-2 * 1j * deltai)
+#
+#     r = r12 * (1 - expo) / (1 - r12 ** 2 * expo)
+#     t = 1 + r
+#     return r, t
+
+
+h = 5
+
+lambda0 = 150
+
+epsxx = 2.19112589e01 - 1.77562977e-01j
+epsyy = 5.60140547e01 - 5.32664927e-01j
+
+theta = np.linspace(0, 89, 111)
[…]

### 2019-03-21 ferromtm/models/slab_test.py

@@ -1,0 +1,164 @@
+import numpy as np
+from pytheas.material import genmat
+from pytheas import periodic2D, utils
+from pytheas.periodic2D import Periodic2D
+from ferromtm.models.coupled2D import *
+from ferromtm.visualization.plots import *
+import tempfile
+
+plt.close("all")
+
+
+cv_dir_ = "circ_rods"
+# cv_dir_ = "rand_circ_rods"
+cv_dir = os.path.join(data_folder, cv_dir_, "convergence")
+
+
+def load_arch(iter):
+    fname = "cv_iter_{}.npz".format(iter)
+    filename = os.path.join(cv_dir, fname)
+    arch = np.load(filename)
+    eps_hom = arch["eps_hom"]
+    epsi = arch["epsi_map"]
+    E = arch["E_map"]
+    return epsi, E, eps_hom
+
+
+pi = np.pi
+f = 0.5
+E0 = 2
+rincl = (f / pi) ** 0.5
+nincly = 5
+dx = 1
+
+ef = epsilonr_ferroelectric(E0)
+epsi = [ef, 3]
+matprop = [np.sqrt(e) for e in epsi]
+fem = Periodic2D()
+
+fem.lambda0 = 2  #: flt: incident wavelength
+
+# opto-geometric parameters  -------------------------------------------
+fem.d = 1  #: flt: period
+fem.h_sup = fem.lambda0 * 2  #: flt: "thickness" superstrate
+fem.h_sub = fem.lambda0 * 2  #: flt: "thickness" substrate
+fem.h_layer1 = 1 * fem.d  #: flt: thickness layer 1
+fem.h_layer2 = 1 * fem.d  #: flt: thickness layer 2
+fem.h_des = nincly * dx  #: flt: thickness layer design
+fem.h_pmltop = fem.lambda0  #: flt: thickness pml top
+fem.h_pmlbot = fem.lambda0  #: flt: thickness pml bot
+fem.a_pml = 1  #: flt: PMLs parameter, real part
+fem.b_pml = 1  #: flt: PMLs parameter, imaginary part
+fem.eps_sup = 1  #: flt: permittivity superstrate
+fem.eps_sub = 1  #: flt: permittivity substrate
+fem.eps_layer1 = 1  #: flt: permittivity layer 1
+fem.eps_layer2 = 1  #: flt: permittivity layer 2
+fem.eps_des = 1  #: flt: permittivity layer design
+
[…]

### 2019-03-25 paper/main.tex
paper

@@
   \hline
-   case & $\epsf(0)$  & $\alpha$ ($\rm \mu m^2/V^2$) & $\beta$ ($\rm \mu m^4/V^4$)\\ \hline
-  static & 3050 & 0.120 & 0.024\\
+  case        & $\epsf(0)$ & $\alpha$ ($\rm \mu m^2/V^2$) & $\beta$ ($\rm \mu m^4/V^4$) \\ \hline
+  static      & 3050       & 0.120                        & 0.024                       \\
   $f=3.8$ GHz & 165        & 0.240                        & 0.079                       \\\hline
@@
 are invariant along $z$, so that the electric field is equal to the uniform biasing field, and
-we will therefore not study it in the following.
+we will thus not study it in the following.
 However in the TM case, the situation is much more complex: this is a coupled problem since the
@@
 Here we would like to emphasise that the permittivity in the ferroelectric material, although
-uniform initially, will be spatially varying due to the non-uniform distribution
+uniform initially, is spatially varying due to the non-uniform distribution
 of the total electric field.\\
@@
 We first study the convergence of the coupled problem on the particular case with dielectric
-filling fraction $f=\pi r^2/d^2=0.5$ and $E_0=2$kV/mm. Figures \ref{conv2D}(a) and \ref{conv2D}(b) show the
+filling fraction $f=\pi r^2/d^2=0.5$ and $E_0=2$MV/m. Figures \ref{conv2D}(a) and \ref{conv2D}(b) show the
 convergence of the real part and loss tangent of the components of the homogenized
- permittivity tensor, respectively. The $yy$ components converge very quickly
+permittivity tensor, respectively. The $yy$ components converge quickly
 and are almost unaffected by the coupling process whereas the
@@
 where the $x$ component of the electric field is still much stronger
- than the $y$ component, even if it is spatially varying in the ferroelectric medium.
+than the $y$ component, even if spatially varying in the ferroelectric medium.
 At equilibrium, the electric field is concentrated close to the $y$ axis in between two neighbouring
@@
 Due to the inhomogeneous redistribution of the permittivity over the ferroelectric domain, the
- overall tunability changes. In the case studied here, taking into account the coupling leads to an effective tunability increase with
- higher dielectric concentration, and that is larger than the tunability of bulk ferroelectric.  There are two concurrent effect at stake here: on the one hand
+overall tunability changes. In the case studied here, taking into account
+the coupling leads to an effective tunability increase with
+higher dielectric concentration, and that is larger than the tunability
+ of bulk ferroelectric. Two concurrent effects are at stake here: on the one hand
 the dilution of ferroelectric makes the composite less tunable, but on the other hand,
@@
 than the periodic case, with higher variation from sample to sample as $f$ increases.
-The tunability is reduced as one adds more dielectric, but is slightly greater than that in the periodic case.
+The effective tunability is on average smaller than that in the periodic case, and
+for low biasing fields and for some particular samples can be greater than the bulk tunability. However,
+at higher applied eelectric fields, normalized tunability becomes smaller than unity and
+is reduced as one adds more dielectric. \\
 The redistribution of electric field, permittivity and convergence of
@@
 
-\aucontribute{Insert author contributions text here (to be included if more than one author).}
+\aucontribute{Benjamin Vial wrote devised the research, implemented
+the codes and wrote the paper. Yang Hao supervised the research and
+co-authored the manuscript.}
 
@@
 
-\funding{his work was funded by the Engineering and Physical Sciences Research Council (EPSRC), UK, under a grant (EP/P005578/1) 'Adaptive Tools for Electromagnetics and Materials Modelling to Bridge the Gap between Design and Manufacturing (AOTOMAT)'.}
+\funding{This work was funded by the Engineering and Physical Sciences Research
+ Council (EPSRC), UK, under a grant (EP/P005578/1) 'Adaptive Tools for
+  Electromagnetics and Materials Modelling to Bridge the Gap between
+  Design and Manufacturing (AOTOMAT)'.}
 
-\ack{The authors would like to thanks Henry Giddens for performing the measurements of ferroelectric permittivity used in this paper.}
+\ack{The authors would like to thanks Henry Giddens for performing the
+measurements of ferroelectric permittivity used in this paper.}
 

### 2019-03-26 paper/main.tex
test docker

@@
  The key requirements for antenna and microwave applications are large tunability and low losses.
- These two characteristics are correlated and one has to find a trade-off for optimal device
- performance, which can be quantified by the so called commutation quality factor
+ These two characteristics are correlated and one has to find a trade-off for optimal device performance, which can be quantified by the so called commutation quality factor
  $K = (n -1)^2/(n\, \tan\delta(0)\,\tan\delta(E))$, where $\tan\delta$ is the loss tangent.\\
@@
 \maketitle
-\noindent values and losses.
+\noindent values and losses.\\
 The effective parameters of those composites have been investigated \cite{sherman_ferroelectric-dielectric_2006, jylha_tunability_2008, sherman_tunability_2004, astafiev_can_2003} and it has been found that the
-permittivity can be greatly reduced while losses and tunability are much less sensitive to the
-dielectric phase addition.
+permittivity can be greatly reduced while losses are much less sensitive to the dielectric phase addition, and in some can lead to a small increase of the tunability of the mixture.
+In the context of porous ferroelectrics, the homogenized properties strongly depends on the size and morphology of the pores \cite{okazaki_effects_1973,stanculescu_study_2015}.
+In addition, the influence
+of local field enhancement in the tunability has been shown to be of particular importance \cite{padurariu_tailoring_2012,padurariu_field-dependent_2012,cazacu_tunable_2013}.
 \\
-This study investigates the effective permittivity of dielectric/ferroelectric composites
+This study investigates the effective permittivity of composites made of dielectric inclusions in a ferroelectric matrix
 by using a two-scale convergence method \cite{allaire_homogenization_1992, guenneau_homogenization_2000}.
@@
 the resulting effective permittivity, dielectric losses, tunability and
-anisotropy significantly differ. \\
+anisotropy significantly differ.
+The difference between earlier sudies in the litterature \cite{padurariu_tailoring_2012,padurariu_field-dependent_2012} is that the non-linear coupling is taken into account beyond the first iteration and that we use two-scale
+convergence homogenization theory to compute the effective parameters at higher frequencies, instead of a capacitance based model.
 We study first a two-dimensional model of metamaterials made of parallel rods with circular cross section,
@@
  \centering
- \includegraphics[width=1\textwidth]{effpar_rand_cpl}
+ \includegraphics[width=0.9\textwidth]{effpar_rand_cpl}
  \caption{Effective parameters of the random 2D mixtures as a function of the
@@
 %#########################################################################################
+%
 

### 2019-03-26 ferromtm/models/circle_maps.py

@@ -1,5 +1,5 @@
 from coupled2D import *
-from aotomat.tools.parallelize import *
+from ferromtm.tools.parallelize import *
 
 
 def main_circle(params, save=False, coupling=True):

### 2019-03-26 ferromtm/models/coupled2D.py

@@ -8,9 +8,9 @@ import numpy as np
 
 import time
 
-## from aotomat.tools.plottools import *
+
 from pytheas.homogenization import *
-from aotomat.electrostatics.per2D import femmodel as model_es
+from ferromtm.models.electrostatics.per2D import femmodel as model_es
 from pytheas.homogenization.twoscale2D import femmodel as model_hom
 import importlib
 from ferromtm.tools.utils import *

### 2019-03-26 ferromtm/models/coupled3D.py

@@ -7,9 +7,8 @@
 # import matplotlib.pyplot as plt
 # plt.ion()
 import numpy as np
-from aotomat.tools.plottools import *
 from pytheas.homogenization import *
-from aotomat.electrostatics.per3D import femmodel as model_es
+from ferromtm.models.electrostatics.per3D import femmodel as model_es
 from pytheas.homogenization.twoscale3D import femmodel as model_hom
 import importlib
 
@@ -176,6 +175,8 @@ def coupling_loop_analytical(E, f, eps_incl, eps_f, verbose=False):
 
 
 if __name__ == "__main__":
+    from ferromtm.visualization.plots import *
+
     fmax = 4 / 3 * pi * 0.5 ** 3
     f = 0.4
     nbias = 10

### 2019-03-26 ferromtm/models/electrostatics/per2D/femmodel.py

@@ -1,0 +1,105 @@
+import os
+import subprocess
+import numpy as np
+import scipy as sc
+from pytheas.tools import femio
+from pytheas.basefem import BaseFEM, get_file_path
+
+pi = np.pi
+
+
+class FemModel(BaseFEM):
+    """A class for computing electrostatic fields of
+    a periodic 2D medium using a finite element model.
+    See the base class :class:`BaseFEM` documentation for more info.
+    """
+
+    def __init__(self):
+        super().__init__()
+        self.dir_path = get_file_path(__file__)
+
+        #: flt: incident plane wave wavelength in free space
+        self.lambda0 = 1.0
+        #: flt: static applied electric field
+        self.E_static = 1.0
+        self.theta = 0
+
+        #: flt: global mesh parameter
+        #: `MeshElementSize = lambda0/(parmesh*n)`, `n`: refractive index
+        self.parmesh = 10.0
+        self.quad_mesh_flag = False
+        self.coupling_flag = True
+        self.type_des = "elements"
+        #: int: number of x points for postprocessing field maps
+        self.Nix = 100
+        self.Niy = 100
+
+        self.eps_host = 1 - 0j
+        self.eps_incl = 1 - 0j
+
+        # opto-geometric parameters  -------------------------------------------
+        self.dx = 1  #: flt: period x
+        self.dy = 1  #: flt: period y
+        self.dom_des = 1000  #: design domain number (check .geo/.pro files)
+
+    @property
+    def corners_des(self):
+        return -self.dx / 2, +self.dx / 2, -self.dy / 2, +self.dy / 2
+
+    @property
+    def domX_L(self):
+        return -self.dx / 2
+
+    @property
+    def domX_R(self):
+        return self.dx / 2
+
+    @property
+    def domY_B(self):
+        return -self.dy / 2
+
+    @property
+    def domY_T(self):
+        # + self.h_pmltop
+        return self.dy / 2
+
+    def make_param_dict(self):
+        param_dict = super().make_param_dict()
+        # param_dict["save_solution"] = int(self.save_solution)
+        param_dict["coupling_flag"] = int(self.coupling_flag)
+        return param_dict
+
+    def compute_solution(self, **kwargs):
+        if self.pattern:
+            self.update_epsilon_value()
+        self.update_params()
+        self.print_progress("Computing solution: homogenization problem")
+        argstr = "-petsc_prealloc 1500 -ksp_type preonly \
[…]

### 2019-03-26 ferromtm/models/electrostatics/per3D/femmodel.py

@@ -1,0 +1,131 @@
+import os
+import subprocess
+import numpy as np
+import scipy as sc
+from pytheas.tools import femio
+from pytheas.basefem import BaseFEM, get_file_path
+
+pi = np.pi
+
+
+class FemModel(BaseFEM):
+    """A class for computing electrostatic fields of
+    a periodic 3D medium using a finite element model.
+    See the base class :class:`BaseFEM` documentation for more info.
+    """
+
+    def __init__(
+        self,
+        #: flt: caracteristic length of the problem (typically the period)
+        l_carac=1.0,
+        #: flt: global mesh parameter
+        #: `MeshElementSize = l_carac/(parmesh*n)`, `n`: refractive index
+        parmesh=10.0,
+        # opto-geometric parameters  -------------------------------------------
+        dx=1,  #: flt: period x
+        dy=1,  #: flt: period y
+        dz=1,  #: flt: period z
+        ax=0.25,  #: flt: ellipsoid principal axis length x
+        ay=0.25,  #: flt: ellipsoid principal axis length y
+        az=0.25,  #: flt: ellipsoid principal axis length z
+        eps_host=1 - 0j,
+        eps_incl=1 - 0j,
+        dom_des=1002,  #: design domain number (check .geo/.pro files)
+        dim=3,  #: dimension of the problem
+        save_solution=False,
+        type_des="nodes",
+        inclusion_flag=False,
+        coupling_flag=False,
+        E_static=1,
+    ):
+
+        super().__init__()
+        self.dir_path = get_file_path(__file__)
+
+        #: flt: caracteristic length of the problem (typically the period)
+        self.l_carac = l_carac
+
+        #: flt: global mesh parameter
+        #: `MeshElementSize = l_carac/(parmesh*n)`, `n`: refractive index
+        self.parmesh = parmesh
+        # opto-geometric parameters  -------------------------------------------
+        self.dx = dx
+        self.dy = dy
+        self.dz = dz
+        self.ax = ax
+        self.ay = ay
+        self.az = az
+        self.eps_host = eps_host
+        self.eps_incl = eps_incl
+        self.dom_des = dom_des  #: design domain number (check .geo/.pro files)
+        self.dim = dim  #: dimension of the problem
+
+        self.save_solution = save_solution
+
+        self.type_des = type_des
+        self.lambda_mesh = l_carac
+        self.eps_des = eps_host
+
+        self.inclusion_flag = inclusion_flag
[…]

### 2019-03-26 ferromtm/models/run_circ.py

@@ -1,5 +1,5 @@
 from coupled2D import *
-from aotomat.tools.parallelize import *
+from ferromtm.tools.parallelize import *
 
 
 def main_per_uncoupled(params):

### 2019-03-26 ferromtm/models/run_convergence.py

@@ -1,5 +1,5 @@
 from coupled2D import *
-from aotomat.tools.parallelize import *
+from ferromtm.tools.parallelize import *
 
 
 if __name__ == "__main__":

### 2019-03-26 ferromtm/models/run_rand.py

@@ -1,5 +1,5 @@
 from coupled2D import *
-from aotomat.tools.parallelize import *
+from ferromtm.tools.parallelize import *
 
 
 def main_rand_uncoupled(params):

### 2019-03-26 ferromtm/models/slab.py

@@ -164,57 +164,3 @@ def extract_effs(out):
     for k in ["R", "T", "Q", "B"]:
         e.append(get_key(out, k))
     return e
-
-
-if __name__ == "__main__":
-
-    run = False
-
-    angle = list(np.linspace(0, 89, 100))
-    save_dir_ = "meta"
-    save_arch = os.path.join(data_folder, save_dir_, "efficiencies_angle.npz")
-
-    if run:
-        from aotomat.tools.parallelize import *
-
-        main_meta_par = parallel(main_meta, partype="gridmap")
-        main_meta_uncpl_par = parallel(main_meta_uncpl, partype="gridmap")
-
-        out_meta = main_meta_par(angle)
-        out_meta_uncpl = main_meta_uncpl_par(angle)
-
-        np.savez(save_arch, out_meta=out_meta, out_meta_uncpl=out_meta_uncpl)
-    else:
-        arch = np.load(save_arch)
-        out_meta = arch["out_meta"]
-        out_meta_uncpl = arch["out_meta_uncpl"]
-
-    R_hom = main_hom(np.array(angle), coupled=True)
-    R_hom_uncpl = main_hom(np.array(angle), coupled=False)
-
-    R_meta, T_meta, Q_meta, B_meta = extract_effs(out_meta)
-    R_meta_uncpl, T_meta_uncpl, Q_meta_uncpl, B_meta_uncpl = extract_effs(
-        out_meta_uncpl
-    )
-
-    plt.figure()
-    plt.plot(angle, R_meta, "-r", alpha=0.5, lw=4, label="MTM coupled")
-    plt.plot(angle, R_hom, "--r", label="hom. coupled")
-    plt.plot(angle, R_meta_uncpl, "-b", alpha=0.5, lw=4, label="MTM uncoupled")
-    plt.plot(angle, R_hom_uncpl, "--b", label="hom. uncoupled")
-    plt.legend()
-    plt.xlabel("incident angle (degree)")
-    plt.ylabel("Reflection")
-    plt.xlim((0, 90))
-    plt.ylim((0, 1))
-
-    # plt.figure()
-    # plt.plot(angle, T_meta, "-r", alpha=0.5, lw=4, label="MTM coupled")
-    # plt.plot(angle, T_hom, "--r", label="hom. coupled")
-    # plt.plot(angle, T_meta_uncpl, "-b", alpha=0.5, lw=4, label="MTM uncoupled")
[…]

### 2019-03-26 ferromtm/models/slab_analytical.py

@@ -1,86 +1,0 @@
-import numpy as np
-from pytheas.material import genmat
-from pytheas import periodic2D, utils
-from pytheas.periodic2D import Periodic2D
-from ferromtm.models.coupled2D import *
-from ferromtm.visualization.plots import *
-import tempfile
-
-plt.close("all")
-
-
-def rslab(h, lambda0, theta, epsxx, epsyy):
-    """reflection coefficient for TM polarization of a
-    slab with diagonal permittivity in vacuum"""
-
-    t = pi * theta / 180
-    ct = np.cos(t)
-    st = np.sin(t)
-    k0 = 2 * pi / lambda0
-    k0x = k0 * st
-    k0y = k0 * ct
-    ky = k0 * (np.sqrt(epsxx * (1 - st ** 2 / epsyy)))
-
-    r1 = (k0y - ky / epsxx) / (k0y + ky / epsxx)
-    expo = np.exp(-2 * 1j * ky * h)
-    r = r1 * (1 - expo) / (1 - r1 ** 2 * expo)
-    return r
-
-
-#
-#
-#
-# def rslab_iso(h, lambda0, theta, eps):
-#     """reflection coefficient for TM polarization of a
-#     slab with diagonal permittivity in vacuum"""
-#
-#     t = pi * theta / 180
-#     ct = np.cos(t)
-#     st = np.sin(t)
-#     k0 = 2 * pi / lambda0
-#
-#     k1 = k0
-#     k2 = k0 * np.sqrt(eps)
-#     a1 = -k1 * st
-#
-#     b1 = k1 * ct
-#     b2 = np.sqrt(k2 ** 2 - a1 ** 2)
-#
-#     r12 = (b1 - b2 / eps) / (b1 + b2 / eps)
-#
-#     cti = np.conj(np.sqrt(1 - st ** 2 / eps + 0j))
-#     deltai = cti * k0 * np.sqrt(eps) * h
-#     expo = np.exp(-2 * 1j * deltai)
-#
-#     r = r12 * (1 - expo) / (1 - r12 ** 2 * expo)
-#     t = 1 + r
-#     return r, t
-
-
-h = 5
-
-lambda0 = 150
-
-epsxx = 2.19112589e01 - 1.77562977e-01j
-epsyy = 5.60140547e01 - 5.32664927e-01j
-
-theta = np.linspace(0, 89, 111)
[…]

### 2019-03-26 ferromtm/models/slab_angle.py

@@ -1,0 +1,15 @@
+from ferromtm.models.slab import *
+
+angle = list(np.linspace(0, 89, 100))
+save_dir_ = "meta"
+save_arch = os.path.join(data_folder, save_dir_, "efficiencies_angle.npz")
+
+
+if __name__ == "__main__":
+    from ferromtm.tools.parallelize import *
+
+    main_meta_par = parallel(main_meta, partype="gridmap")
+    main_meta_uncpl_par = parallel(main_meta_uncpl, partype="gridmap")
+    out_meta = main_meta_par(angle)
+    out_meta_uncpl = main_meta_uncpl_par(angle)
+    np.savez(save_arch, out_meta=out_meta, out_meta_uncpl=out_meta_uncpl)

### 2019-03-26 ferromtm/models/slab_freq.py

@@ -1,5 +1,4 @@
-from slab import *
-
+from ferromtm.models.slab import *
 
 fem.theta_deg = 20
 
@@ -46,44 +45,19 @@ def main_hom(fnorm, coupled=True):
     return np.abs(r) ** 2
 
 
+fnorm = list(np.linspace(1 / 150, 1 / 10, 150))
+save_dir_ = "meta"
+save_arch = os.path.join(data_folder, save_dir_, "efficiencies_freq.npz")
+
+
 if __name__ == "__main__":
 
-    run = False
+    from ferromtm.tools.parallelize import *
 
-    fnorm = list(np.linspace(1 / 150, 1 / 10, 150))
-    save_dir_ = "meta"
-    save_arch = os.path.join(data_folder, save_dir_, "efficiencies_freq.npz")
+    main_meta_par = parallel(main_meta, partype="gridmap")
+    main_meta_uncpl_par = parallel(main_meta_uncpl, partype="gridmap")
 
-    if run:
-        from aotomat.tools.parallelize import *
+    out_meta = main_meta_par(fnorm)
+    out_meta_uncpl = main_meta_uncpl_par(fnorm)
 
-        main_meta_par = parallel(main_meta, partype="gridmap")
-        main_meta_uncpl_par = parallel(main_meta_uncpl, partype="gridmap")
-
-        out_meta = main_meta_par(fnorm)
-        out_meta_uncpl = main_meta_uncpl_par(fnorm)
-
-        np.savez(save_arch, out_meta=out_meta, out_meta_uncpl=out_meta_uncpl)
-    else:
-        arch = np.load(save_arch)
-        out_meta = arch["out_meta"]
-        out_meta_uncpl = arch["out_meta_uncpl"]
-
-    R_hom = main_hom(np.array(fnorm), coupled=True)
-    R_hom_uncpl = main_hom(np.array(fnorm), coupled=False)
-
-    R_meta, T_meta, Q_meta, B_meta = extract_effs(out_meta)
-    R_meta_uncpl, T_meta_uncpl, Q_meta_uncpl, B_meta_uncpl = extract_effs(
-        out_meta_uncpl
-    )
-
-    plt.figure()
-    plt.plot(fnorm, R_meta, "-r", alpha=0.5, lw=4, label="MTM coupled")
-    plt.plot(fnorm, R_hom, "--r", label="hom. coupled")
[…]

### 2019-03-26 ferromtm/models/slab_modes.py

@@ -1,4 +1,5 @@
-from slab import *
+from ferromtm.models.slab import *
+
 
 maps_dir_ = "circ_rods"
 maps_dir = os.path.join(data_folder, maps_dir_)
@@ -53,68 +54,29 @@ def main_meta_uncpl(E_bias):
     return main_modes(E_bias, coupled=False)
 
 
-# def main_hom(fnorm, coupled=True):
-#     if coupled:
-#         iter = 12  # periodic
-#     else:
-#         iter = 0
-#     _, _, eps_hom = load_arch(iter)
-#     lambda0 = fem.d/fnorm
-#     r = rslab(fem.h_des, lambda0, fem.theta_deg, eps_hom[0,0], eps_hom[1,1])
-#     return np.abs(r)**2
+def main_modes_analytical(E_bias, coupled=True):
+    _, eps_hom = load_arch(E_bias, coupled)
+    h, epsxx, epsyy = fem.h_des, np.conj(eps_hom[0, 0]), np.conj(eps_hom[1, 1])
+    n = 7
+    n_ = np.array(range(7))
+    alpha = (np.sqrt(epsxx) + 1) / (np.sqrt(epsxx) - 1)
+    ev = (n_ * pi - 1j * np.log(alpha)) / (h * np.sqrt(epsxx))
+    return ev
 
+
+save_dir_ = "meta"
+save_arch = os.path.join(data_folder, save_dir_, "modes.npz")
+
+nE = 21
+Ebias = list(np.linspace(0, 2, nE))
 
 if __name__ == "__main__":
+    from ferromtm.tools.parallelize import *
 
-    run = False
+    main_meta_par = parallel(main_meta, partype="gridmap")
+    main_meta_uncpl_par = parallel(main_meta_uncpl, partype="gridmap")
 
-    save_dir_ = "meta"
-    save_arch = os.path.join(data_folder, save_dir_, "modes.npz")
+    ev_meta = main_meta_par(Ebias)
+    ev_meta_uncpl = main_meta_uncpl_par(Ebias)
 
-    nE = 21
-    Ebias = list(np.linspace(0, 2, nE))
-
-    if run:
-        from aotomat.tools.parallelize import *
-
-        main_meta_par = parallel(main_meta, partype="gridmap")
-        main_meta_uncpl_par = parallel(main_meta_uncpl, partype="gridmap")
-
[…]

### 2019-03-26 ferromtm/models/slab_test.py

@@ -1,164 +1,0 @@
-import numpy as np
-from pytheas.material import genmat
-from pytheas import periodic2D, utils
-from pytheas.periodic2D import Periodic2D
-from ferromtm.models.coupled2D import *
-from ferromtm.visualization.plots import *
-import tempfile
-
-plt.close("all")
-
-
-cv_dir_ = "circ_rods"
-# cv_dir_ = "rand_circ_rods"
-cv_dir = os.path.join(data_folder, cv_dir_, "convergence")
-
-
-def load_arch(iter):
-    fname = "cv_iter_{}.npz".format(iter)
-    filename = os.path.join(cv_dir, fname)
-    arch = np.load(filename)
-    eps_hom = arch["eps_hom"]
-    epsi = arch["epsi_map"]
-    E = arch["E_map"]
-    return epsi, E, eps_hom
-
-
-pi = np.pi
-f = 0.5
-E0 = 2
-rincl = (f / pi) ** 0.5
-nincly = 5
-dx = 1
-
-ef = epsilonr_ferroelectric(E0)
-epsi = [ef, 3]
-matprop = [np.sqrt(e) for e in epsi]
-fem = Periodic2D()
-
-fem.lambda0 = 2  #: flt: incident wavelength
-
-# opto-geometric parameters  -------------------------------------------
-fem.d = 1  #: flt: period
-fem.h_sup = fem.lambda0 * 2  #: flt: "thickness" superstrate
-fem.h_sub = fem.lambda0 * 2  #: flt: "thickness" substrate
-fem.h_layer1 = 1 * fem.d  #: flt: thickness layer 1
-fem.h_layer2 = 1 * fem.d  #: flt: thickness layer 2
-fem.h_des = nincly * dx  #: flt: thickness layer design
-fem.h_pmltop = fem.lambda0  #: flt: thickness pml top
-fem.h_pmlbot = fem.lambda0  #: flt: thickness pml bot
-fem.a_pml = 1  #: flt: PMLs parameter, real part
-fem.b_pml = 1  #: flt: PMLs parameter, imaginary part
-fem.eps_sup = 1  #: flt: permittivity superstrate
-fem.eps_sub = 1  #: flt: permittivity substrate
-fem.eps_layer1 = 1  #: flt: permittivity layer 1
-fem.eps_layer2 = 1  #: flt: permittivity layer 2
-fem.eps_des = 1  #: flt: permittivity layer design
-
[…]

### 2019-03-26 ferromtm/models/slab_tetra.py

@@ -1,96 +1,0 @@
-import tetrachotomy
-from slab_modes import *
-
-# import importlib
-# importlib.reload(tetrachotomy)
-tetrachotomy.plot_rect = True
-tetrachotomy.plot_circ = True
-tetrachotomy.plot_poles = True
-
-plt.close("all")
-pi = np.pi
-tols = (1e-8 * (1 + 1j), 1e-8 * (1 + 1j), 1e-8 * (1 + 1j))
-par_integ = (1e-8, 1e-8, 13)
-tol_pol = 1e-8 * (1 + 1j)
-tol_res = 1e-8 * (1 + 1j)
-inv_golden_number = 2 / (1 + np.sqrt(5))
-ratio = inv_golden_number
-ratio_circ = 1 - inv_golden_number
-nref_max = 100
-ratio_re, ratio_im = ratio, ratio
-
-
-z0 = 0.02 - 0.001 * 1j
-z1 = 0.1 + 0.005 * 1j
-
-z0 = -1 - 1 * 1j
-z1 = 1 + 1 * 1j
-
-x0, x1, y0, y1 = z0.real, z1.real, z0.imag, z1.imag
-#####################################
-
-E_bias = 2
-epsi_map, eps_hom = load_arch(E_bias, coupling=True)
-
-
-def main_hom(fnorm, coupled=True):
-    fnorm_ = fnorm.real / 10 + 1j * fnorm.imag / 100
-    lambda0 = fem.d / fnorm_
-    r = rslab(fem.h_des, lambda0, fem.theta_deg, eps_hom[0, 0], eps_hom[1, 1])
-    return np.abs(r) ** 2
-
-
-def func(z):
-    return 1 / main_hom(z, coupled=True)
-
-
-# #
-x_ = np.linspace(z0.real, z1.real, 201)
-y_ = np.linspace(z0.imag, z1.imag, 200)
-x, y = np.meshgrid(x_, y_)
-
-z = x + 1j * y
-u = func(z)
-
-plt.figure()
-uplot = np.log10(np.abs(func(z)))
-plt.pcolor(x_, y_, uplot)
-plt.colorbar()
-
-fig = plt.figure()
-ax = fig.add_subplot(111)  # , aspect='equal')
-ax.set_xlim((x0, x1))
-ax.set_ylim((y0, y1))
-plt.xlabel(r"Re $z$")
-plt.ylabel(r"Im $z$")
-
-poles, residues, nb_cuts = tetrachotomy.pole_hunt(
[…]

### 2019-03-26 ferromtm/tools/parallelize.py

@@ -1,0 +1,56 @@
+from multiprocessing import Pool
+from functools import partial
+from gridmap import grid_map
+
+
+def parallel(function, partype="gridmap"):
+    """
+    Decorator to parallelize problems.
+
+    Inputs
+    ======
+    function : the function that will be parallelized. The FIRST
+        argument is the one to be iterated on (in parallel). The other
+        arguments are the same in all the parallel runs of the function
+        (they can be named or unnamedarguments).
+
+    partype : the module used for parallelisation (gridmap, scoop or multiprocessing)
+
+    Output
+    ======
+    A paralelized function. DO NOT NAME IT THE SAME AS THE INPUT
+    FUNCTION.
+
+    """
+    if partype == "multiprocessing":
+        # multiprocessing
+        pool = Pool()
+        parmap = pool.map
+    else:
+        # No parallelisation
+        parmap = map
+
+    def par(iterable_values, *args, **kwargs):
+        mapfunc = partial(function, *args, **kwargs)
+        result = [*parmap(mapfunc, iterable_values)]
+        return result
+
+    if partype == "gridmap":
+
+        def par(iterable_values):
+            result = grid_map(
+                function,
+                iterable_values,
+                quiet=False,
+                num_slots=1,
+                temp_dir=u"./tmp",
+                max_processes=len(iterable_values),
+                queue="all.q",
+                require_cluster=False,
+                local=False,
+                cleanup=True,
+            )
+
+            return result
+
+    return par

### 2019-03-26 ferromtm/visualization/postpro2D_random.py

@@ -235,11 +235,22 @@ if __name__ == "__main__":
     )
 
     plt.close("all")
-    fig, ax = plt.subplots(ncols=2, nrows=2)
-    plot_eff_par(fig, ax, lin=True)
+    # fig, ax = plt.subplots(ncols=2, nrows=2)
+    # plot_eff_par(fig, ax, lin=True)
 
-    fig, ax = plt.subplots(ncols=2, nrows=2)
+    fig, ax = plt.subplots(ncols=2, nrows=2, figsize=(6, 4))
+    fig.set_rasterized(True)
+    [a.set_rasterized(True) for a in ax.ravel()]
     plot_eff_par(fig, ax, lin=False)
+    plt.tight_layout()
+    fig.savefig("effpar_rand_cpl.eps", rasterized=True, dpi=300)
+
+    fig, ax = plt.subplots(ncols=2, nrows=2, figsize=(6, 4))
+    fig.set_rasterized(True)
+    [a.set_rasterized(True) for a in ax.ravel()]
+    plot_eff_par(fig, ax, lin=True)
+    plt.tight_layout()
+    fig.savefig("effpar_rand_uncpl.eps", rasterized=True, dpi=300)
 
 # data = norm_eps[:, :, iF].ravel()
 # sns.lineplot(x=Ebias_plot, y=data, ax=ax[0][0], ci="sd", color=clr)

### 2019-03-26 ferromtm/visualization/postpro_slab_angle.py

@@ -1,0 +1,32 @@
+from ferromtm.visualization.plots import *
+from ferromtm.models.slab_angle import *
+
+if __name__ == "__main__":
+    arch = np.load(save_arch)
+    out_meta = arch["out_meta"]
+    out_meta_uncpl = arch["out_meta_uncpl"]
+
+    R_hom = main_hom(np.array(angle), coupled=True)
+    R_hom_uncpl = main_hom(np.array(angle), coupled=False)
+
+    R_meta, T_meta, Q_meta, B_meta = extract_effs(out_meta)
+    R_meta_uncpl, T_meta_uncpl, Q_meta_uncpl, B_meta_uncpl = extract_effs(
+        out_meta_uncpl
+    )
+
+    # plt.figure()
+    fig, ax = plt.subplots(ncols=1, nrows=1, figsize=(5, 3))
+    fig.set_rasterized(True)
+    ax.set_rasterized(True)
+
+    plt.plot(angle, R_meta, "-r", alpha=0.5, lw=4, label="MTM coupled")
+    plt.plot(angle, R_hom, "--r", label="hom. coupled")
+    plt.plot(angle, R_meta_uncpl, "-b", alpha=0.5, lw=4, label="MTM uncoupled")
+    plt.plot(angle, R_hom_uncpl, "--b", label="hom. uncoupled")
+    plt.legend()
+    plt.xlabel("incident angle (degree)")
+    plt.ylabel("Reflection")
+    plt.xlim((0, 90))
+    plt.ylim((0, 1))
+    plt.tight_layout()
+    fig.savefig("Rslab_angle.eps", rasterized=True, dpi=300)

### 2019-03-26 ferromtm/visualization/postpro_slab_freq.py

@@ -1,0 +1,33 @@
+from ferromtm.visualization.plots import *
+from ferromtm.models.slab_freq import *
+
+if __name__ == "__main__":
+
+    arch = np.load(save_arch)
+    out_meta = arch["out_meta"]
+    out_meta_uncpl = arch["out_meta_uncpl"]
+
+    R_hom = main_hom(np.array(fnorm), coupled=True)
+    R_hom_uncpl = main_hom(np.array(fnorm), coupled=False)
+
+    R_meta, T_meta, Q_meta, B_meta = extract_effs(out_meta)
+    R_meta_uncpl, T_meta_uncpl, Q_meta_uncpl, B_meta_uncpl = extract_effs(
+        out_meta_uncpl
+    )
+
+    plt.close("all")
+    # plt.figure()
+    fig, ax = plt.subplots(ncols=1, nrows=1, figsize=(5, 3))
+    fig.set_rasterized(True)
+    ax.set_rasterized(True)
+    plt.plot(fnorm, R_meta, "-r", alpha=0.5, lw=4, label="MTM coupled")
+    plt.plot(fnorm, R_hom, "--r", label="hom. coupled")
+    plt.plot(fnorm, R_meta_uncpl, "-b", alpha=0.5, lw=4, label="MTM uncoupled")
+    plt.plot(fnorm, R_hom_uncpl, "--b", label="hom. uncoupled")
+    plt.legend(ncol=2)
+    plt.xlabel("Normalized frequency $d/\lambda$")
+    plt.ylabel("Reflection")
+    plt.xlim((fnorm[0], 0.06))
+    plt.ylim((0, 1.09))
+    plt.tight_layout()
+    fig.savefig("Rslab_freq.eps", rasterized=True, dpi=300)

### 2019-03-26 ferromtm/visualization/postpro_slab_modes.py

@@ -1,0 +1,99 @@
+from ferromtm.visualization.plots import *
+from ferromtm.models.slab_modes import *
+
+if __name__ == "__main__":
+    arch = np.load(save_arch)
+    ev_meta = arch["ev_meta"]
+    ev_meta_uncpl = arch["ev_meta_uncpl"]
+
+    omega0 = 2 * pi / fem.d
+    ev_meta_norma = np.array(ev_meta).conj() / omega0
+    ev_meta_uncpl_norma = np.array(ev_meta_uncpl).conj() / omega0
+
+    ev_slab_uncpl = [main_modes_analytical(e, coupled=False) for e in Ebias]
+    ev_slab_uncpl_norma = np.array(ev_slab_uncpl) / omega0
+    ev_slab = [main_modes_analytical(e, coupled=True) for e in Ebias]
+    ev_slab_norma = np.array(ev_slab) / omega0
+
+    dx = +0.002
+    x1, y1 = ev_slab_norma.real[13][1] + dx, ev_slab_norma.imag[13][1]
+    x2, y2 = ev_slab_norma.real[5][1] + dx, ev_slab_norma.imag[5][1]
+
+    locs = x1, y1, x2, y2
+
+    def draw_arrow(ax, locs, connectionstyle, label=None):
+        x1, y1, x2, y2 = locs
+        ax.annotate(
+            "",
+            xy=(x1, y1),
+            xycoords="data",
+            xytext=(x2, y2),
+            textcoords="data",
+            arrowprops=dict(
+                arrowstyle="->",
+                color="0.0",
+                shrinkA=5,
+                shrinkB=5,
+                patchA=None,
+                patchB=None,
+                connectionstyle=connectionstyle,
+            ),
+        )
+        ax.annotate(
+            label,
+            xy=(x1, y1),
+            xycoords="data",
+            xytext=((x1 + x2) / 2, (y1 + y2) / 2),
+            textcoords="data",
+        )
+
+    plt.close("all")
+    fig, ax = plt.subplots(ncols=1, nrows=1, figsize=(5, 3))
+    plt.plot(
+        ev_meta_norma.real.ravel(),
+        ev_meta_norma.imag.ravel(),
+        "ko",
+        alpha=0.3,
+        lw=4,
+        label="MTM coupled",
+    )
[…]

### 2019-03-28 paper/main.tex
makefile and paper

@@
 \usepackage{graphicx}
+
 \usepackage{amsmath}
@@
 Periodic and random arrays of dielectric rods in a ferroelectric matrix are investigated and we study the effective permittivity, losses, electrically induced anisotropy and tunability of those metamaterials using a two-scale homogenization method.
+
+\usepackage[outdir=./]{epstopdf}
+\graphicspath{{../data/figures/}}
 
@@
  \centering
- \includegraphics[width=1\textwidth]{conv_per}
+ \includegraphics[width=1\textwidth]{convergence_per}
  \caption{Convergence of the coupled problem.
@@
   permittivity tensor as a function of iteration step $i$. The distribution of
-  the normalized electric field (colormap: magnitude, arrows: direction) and of the
+  the normalized electric field (colour map: magnitude in logarithmic scale,
+  lines: equipotential contours) and of the
   $xx$ component of the permittivity tensor are shown for $i=1$
@@
  \centering
- \includegraphics[width=1\textwidth]{effpar_per}
+ \includegraphics[width=1\textwidth]{effective_params_per}
  \caption{Effective parameters of the 2D metamaterials as a function of the
@@
  \centering
- \includegraphics[width=0.8\columnwidth]{randmatepsi}
+ \includegraphics[width=0.8\columnwidth]{random_samples_f_50percent}
  \caption{Permittivity distribution of the numerical samples used for $f=0.5$. Dark
@@
  \centering
- \includegraphics[width=1\textwidth]{conv_rand}
+ \includegraphics[width=1\textwidth]{convergence_rand}
  \caption{Convergence of the coupled problem in the random case
@@
   permittivity tensor as a function of iteration step $i$. The distribution of
-  the normalized electric field (colour map: magnitude in logarithmic scale, arrows: direction) and of the
-  $xx$ component of the permittivity tensor are shown for $i=1$
-  (c and d) and $i=14$ (e and f).
+  the normalized electric field (colour map: magnitude in logarithmic scale,
+  lines: equipotential contours) and of the $xx$ component of the permittivity tensor are shown for $i=1$
+  (c and d) and $i=12$ (e and f).
  }

### 2019-03-28 ferromtm/__init__.py

@@ -10,3 +10,7 @@ from .__about__ import (
 )
 
 __doc__ = __description__
+
+import os
+
+rootdir = os.path.dirname(os.path.dirname(__file__))

### 2019-03-28 ferromtm/models/bst.py

@@ -1,13 +1,8 @@
-import scipy.constants as const
 import numpy as np
 import os
 import scipy as sc
-
-from ferromtm import __file__
-
-rootdir = os.path.dirname(os.path.dirname(__file__))
-
-eps0 = const.epsilon_0
+from scipy.optimize import minimize
+from ferromtm import rootdir
 
 
 def eps_norma_model(E0, alpha, beta):
@@ -41,7 +36,7 @@ def fun_fit(par, E, eps_meas_n):
 def retrieve_params(E, eps_meas_n):
     par0 = 1, 1
     cons = {"type": "ineq", "fun": lambda x: np.array([x[0]])}
-    opt = sc.optimize.minimize(
+    opt = minimize(
         fun_fit, par0, args=(E, eps_meas_n), options={"disp": True}, constraints=cons
     )
     xopt = opt["x"]
@@ -62,7 +57,6 @@ def fit():
     return fit_params
 
 
-#
 def epsf_real(E_applied, dc=False):
     if dc:
         eps00 = 3050
@@ -87,36 +81,5 @@ def epsilonr_ferroelectric(E_applied, tandelta=1e-2, dc=False):
 
 
 if __name__ == "__main__":
-    from ferromtm.visualization.plots import *
 
     fit()
-    fit_params = np.load(os.path.join(rootdir, "data", "fit_params.npz"))["fit_params"]
-    meas = np.load(os.path.join(rootdir, "data", "measurements.npz"))
-    E_exp = meas["E_exp"]
-    eps_norm_exp = meas["eps_norm_exp"]
-    eps_exp_0 = meas["eps_exp_0"]
-
-    E_fit = np.linspace(-6, 6, 101)
-    eps_norm_fit = []
-    for i in range(2):
-        alpha_opt = fit_params[i]
-        epsf0 = eps_exp_0[i]
-        eps_fit = eps_norma_model(E_fit, *alpha_opt)
-        eps_norm_fit.append(eps_fit)
-
-    plt.close("all")
-    fig = plt.figure(figsize=(5, 3))
-    plt.plot(E_exp, eps_norm_exp[0], "o", label="measured, static", color="#3e8b58")
-    plt.plot(E_fit, eps_norm_fit[0], "--", color="#3e8b58", label="fit, static")
-    plt.plot(
[…]

### 2019-03-28 ferromtm/models/circle_maps.py

@@ -1,4 +1,4 @@
-from .coupled2D import *
+from ferromtm.models.coupled2D import *
 from ferromtm.tools.parallelize import *
 
 

### 2019-03-28 ferromtm/models/coupled2D.py

@@ -3,8 +3,9 @@
 # Author: Benjamin Vial
 # License: MIT
 
-import ferromtm
 import numpy as np
+from ferromtm import rootdir
+
 
 import time
 
@@ -29,16 +30,11 @@ from pytheas.tools.utils import refine_mesh
 # )
 #
 
-rootdir = os.path.dirname(os.path.dirname(ferromtm.__file__))
-
 
 pi = np.pi
 eps_incl = 3
 data_folder = os.path.join(rootdir, "data", "results")
 mat_folder = os.path.join(rootdir, "data", "mat")
-cv_dir_ = "circ_rods"
-# cv_dir_ = "rand_circ_rods"
-cv_dir = os.path.join(data_folder, cv_dir_, "convergence")
 
 
 def ellipse(Rinclx, Rincly, rot_incl, x0, y0):
@@ -123,7 +119,7 @@ def ref_mesh(fem):
     return fem
 
 
-def init_es(f, E_bias, incl=True, mat=None):
+def init_es(f, E_bias, incl=True, mat=None, parmesh=20):
     r = (f / pi) ** (1 / 2)
     #####################################
     # # electrostatics
@@ -134,8 +130,8 @@ def init_es(f, E_bias, incl=True, mat=None):
     fem_es.getdp_verbose = 0  #: str: GetDP verbose (int between 0 and 4)
     fem_es.python_verbose = 0
     #: str: GetDP verbose (int between 0 and 1)
-    fem_es.parmesh = 34
-    fem_es.parmesh_incl = 34
+    fem_es.parmesh = parmesh
+    fem_es.parmesh_incl = parmesh
     fem_es.type_des = "elements"
     fem_es.inclusion_flag = incl
     # if not incl:
@@ -271,7 +267,15 @@ def ppEpsimap(fem):
     return eps_xx, eps_yy
 
 
-def coupling_loop(fem_es, epsi, tol=1e-2, max_iter=100, verbose=False, record_cv=False):
+def ppVmap(fem):
+    fem.postpro_fields()
+    v = fem.get_field_map("v.txt").real
+    return v
+
+
+def coupling_loop(
+    fem_es, epsi, tol=1e-2, max_iter=100, verbose=False, record_cv=False, cv_dir_=None
+):
     conv = False
     o = np.ones_like(epsi[0], dtype=float)
     E0 = np.array([fem_es.E_static * o, 0 * o, 0 * o])
[…]

### 2019-03-28 ferromtm/models/run_convergence.py

@@ -1,12 +1,18 @@
-from .coupled2D import *
+from ferromtm.models.coupled2D import *
 from ferromtm.tools.parallelize import *
-
+import sys
 
 if __name__ == "__main__":
+    if len(sys.argv) > 1:
+        percase = sys.argv[1]
+    else:
+        percase = "per"
+
     tstart = time.time()
-    print("TSART: {}".format(tstart))
-    out_cv = main_circle_conv(params[104])
+    if percase == "rand":
+        out_cv = main_random_conv(params[104])
+    else:
+        out_cv = main_circle_conv(params[104])
     tend = time.time()
     et = tend - tstart
-    print("TEND: {}".format(tend))
     print("ELAPSED: {}s".format(et))

### 2019-03-28 ferromtm/visualization/plot_bst.py

@@ -1,0 +1,35 @@
+from ferromtm.models.bst import *
+from ferromtm.visualization.plots import *
+
+
+if __name__ == "__main__":
+    fit_params = np.load(os.path.join(rootdir, "data", "fit_params.npz"))["fit_params"]
+    meas = np.load(os.path.join(rootdir, "data", "measurements.npz"))
+    E_exp = meas["E_exp"]
+    eps_norm_exp = meas["eps_norm_exp"]
+    eps_exp_0 = meas["eps_exp_0"]
+
+    E_fit = np.linspace(-6, 6, 101)
+    eps_norm_fit = []
+    for i in range(2):
+        alpha_opt = fit_params[i]
+        epsf0 = eps_exp_0[i]
+        eps_fit = eps_norma_model(E_fit, *alpha_opt)
+        eps_norm_fit.append(eps_fit.real)
+
+    plt.close("all")
+    fig = plt.figure(figsize=(5, 3))
+    plt.plot(E_exp, eps_norm_exp[0], "o", label="measured, static", color="#3e8b58")
+    plt.plot(E_fit, eps_norm_fit[0], "--", color="#3e8b58", label="fit, static")
+    plt.plot(
+        E_exp, eps_norm_exp[1], "o", label="measured, $f=3.8$ GHz", color="#eb931e"
+    )
+    plt.plot(E_fit, eps_norm_fit[1], "--", color="#eb931e", label="fit, $f=3.8$ GHz")
+    plt.ylabel(r"normalized permittivity")
+    # $\varepsilon^{\rm f}/\varepsilon^{\rm f}(E=0)$
+    plt.xlabel("electric field (MV/m)")
+    plt.legend()
+
+    plt.tight_layout()
+    plt.ylim((0.1, 1.04))
+    fig.savefig(os.path.join(rootdir, "data", "figures", "epsilon_fit.eps"))

### 2019-03-28 ferromtm/visualization/plot_random_fibers.py

@@ -1,0 +1,29 @@
+#!/usr/bin/env python
+
+from ferromtm.visualization.plots import *
+from ferromtm import rootdir
+import numpy as np
+import os
+
+frange = np.array([0.1, 0.2, 0.3, 0.4, 0.5])
+dirsave = os.path.join(rootdir, "data", "mat")
+plt.close("all")
+for f in frange:
+    name = "random_samples_f_" + "{0}.npz".format(f)
+    npzfile = np.load(os.path.join(dirsave, name))
+    sample = npzfile["sample"]
+    Npltx, Nplty = 3, 7
+    fig, axarr = plt.subplots(
+        Npltx, Nplty, figsize=(Nplty, Npltx), sharex=True, sharey=True
+    )
+    fig.subplots_adjust(hspace=0.1, wspace=0.1)
+    fig.suptitle(r"Random material samples, $f = $ " + str(f))
+
+    for i, ax in enumerate(axarr.ravel()):
+        ax.axis("off")
+        b = sample[i, :, :]
+        ax.imshow(b.T, cmap="Greens_r")
+
+    figname = "random_samples_f_" + "{0}percent.eps".format(int(f * 100))
+    plt.savefig(os.path.join(rootdir, "data", "figures", figname), bbox_inches="tight")
+    plt.pause(0.1)

### 2019-03-28 ferromtm/visualization/postpro2D.py

@@ -161,8 +161,10 @@ if __name__ == "__main__":
         load_results()
     )
     plt.close("all")
-    fig, ax = plt.subplots(ncols=2, nrows=2)
+    fig, ax = plt.subplots(ncols=2, nrows=2, figsize=(6.2, 4.2))
     plot_eff_par(fig, ax)
+    plt.tight_layout()
+    fig.savefig(os.path.join(rootdir, "data", "figures", "effective_params_per.eps"))
     #
     # fig, ax = plt.subplots()
     # plot_eff_cqf(fig, ax)

### 2019-03-28 ferromtm/visualization/postpro2D_conv.py

@@ -1,6 +1,16 @@
 from ferromtm.models.coupled2D import *
 from ferromtm.visualization.plots import *
 from matplotlib.ticker import MaxNLocator
+import sys
+
+# mpl.rcParams["axes.xmargin"] = "0.1"
+mpl.rcParams["axes.ymargin"] = "0.1"
+
+
+if len(sys.argv) > 1:
+    percase = sys.argv[1]
+else:
+    percase = "per"
 
 
 n_bulk = tunability(epsilonr_ferroelectric(Ebias), epsilonr_ferroelectric(0))
@@ -8,8 +18,14 @@ K_bulk = cqf(epsilonr_ferroelectric(Ebias), epsilonr_ferroelectric(0))
 eps_00 = epsilonr_ferroelectric(0).real
 tandelta_00 = -epsilonr_ferroelectric(0).imag / epsilonr_ferroelectric(0).real
 
-cv_dir_ = "circ_rods"
-cv_dir_ = "rand_circ_rods"
+if percase == "rand":
+    cv_dir_ = "rand_circ_rods"
+    ncv = 13  # random
+    figname = "convergence_rand.eps"
+else:
+    cv_dir_ = "circ_rods"
+    ncv = 13  # periodic
+    figname = "convergence_per.eps"
 cv_dir = os.path.join(data_folder, cv_dir_, "convergence")
 
 
@@ -20,11 +36,8 @@ def load_arch(iter):
     eps_hom = arch["eps_hom"]
     epsi = arch["epsi_map"]
     E = arch["E_map"]
-    return epsi, E, eps_hom
-
-
-ncv = 13  # periodic
-ncv = 15  # random
+    v = arch["v_map"]
+    return epsi, E, v, eps_hom
 
 
 def load_results():
@@ -32,20 +45,22 @@ def load_results():
     Eps_eff_yy = np.zeros(ncv, dtype=complex)
     Aniso_factor = np.zeros(ncv, dtype=float)
     E_cv = []
+    v_cv = []
     epsi_cv = []
     for icv in range(ncv):
-        epsi, E, eps_hom = load_arch(icv)
+        epsi, E, v, eps_hom = load_arch(icv)
         Eps_eff_xx[icv] = eps_hom[0, 0]
         Eps_eff_yy[icv] = eps_hom[1, 1]
         Aniso_factor[icv] = aniso_factor(eps_hom)
[…]

### 2019-03-28 ferromtm/visualization/postpro2D_random.py

@@ -230,27 +230,44 @@ def plot_eff_cqf(fig, ax):
 
 if __name__ == "__main__":
 
+    import sys
+
+    if len(sys.argv) > 1:
+        retrieve = True
+    else:
+        retrieve = False
+
     norm_eps, norm_eps_nl, norm_loss, norm_loss_nl, n_norm_lin, n_norm_nl, Aniso_factor_lin, Aniso_factor_nl = load_results(
-        retrieve=False
+        retrieve=retrieve
     )
 
-    plt.close("all")
-    # fig, ax = plt.subplots(ncols=2, nrows=2)
-    # plot_eff_par(fig, ax, lin=True)
+    if retrieve is False:
 
-    fig, ax = plt.subplots(ncols=2, nrows=2, figsize=(6, 4))
-    fig.set_rasterized(True)
-    [a.set_rasterized(True) for a in ax.ravel()]
-    plot_eff_par(fig, ax, lin=False)
-    plt.tight_layout()
-    fig.savefig("effpar_rand_cpl.eps", rasterized=True, dpi=300)
+        plt.close("all")
+        # fig, ax = plt.subplots(ncols=2, nrows=2)
+        # plot_eff_par(fig, ax, lin=True)
 
-    fig, ax = plt.subplots(ncols=2, nrows=2, figsize=(6, 4))
-    fig.set_rasterized(True)
-    [a.set_rasterized(True) for a in ax.ravel()]
-    plot_eff_par(fig, ax, lin=True)
-    plt.tight_layout()
-    fig.savefig("effpar_rand_uncpl.eps", rasterized=True, dpi=300)
+        fig, ax = plt.subplots(ncols=2, nrows=2, figsize=(6, 4))
+        fig.set_rasterized(True)
+        [a.set_rasterized(True) for a in ax.ravel()]
+        plot_eff_par(fig, ax, lin=False)
+        plt.tight_layout()
+        fig.savefig(
+            os.path.join(rootdir, "data", "figures", "effpar_rand_cpl.eps"),
+            rasterized=True,
+            dpi=300,
+        )
+
+        fig, ax = plt.subplots(ncols=2, nrows=2, figsize=(6, 4))
+        fig.set_rasterized(True)
+        [a.set_rasterized(True) for a in ax.ravel()]
+        plot_eff_par(fig, ax, lin=True)
+        plt.tight_layout()
+        fig.savefig(
[…]

### 2019-03-29 paper/arxiv/main.tex
submitted article

--- 2019-03-28 paper/main.tex
@@
-%% Author_tex.tex
-%% V1.0
-%% 2012/13/12
-%% developed by Techset
-%%
-%% This file describes the coding for rsproca.cls
-
-\documentclass[openacc]{rsproca_new}%%%%where rsproca is the template name
+\documentclass[aps,prb,11pt]{revtex4-1}
 
 \usepackage{graphicx}
-
 \usepackage{amsmath}
@@
 
+\usepackage{hyperref}
 \newcommand{\ie}{i.\,e.~}
@@
 
-%%%% *** Do not adjust lengths that control margins, column widths, etc. ***
-
-%%%%%%%%%%% Defining Enunciations  %%%%%%%%%%%
-\newtheorem{theorem}{\bf Theorem}[section]
-\newtheorem{condition}{\bf Condition}[section]
-\newtheorem{corollary}{\bf Corollary}[section]
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %
-% Coupled model and homogenization of dielectric-ferroelectric mixtures.
-%
-% We will present the study of the effective permittivity tensor of ferroelectric-dielectric composites under a static electric field.
-A refined model is used to take into account the coupling between the electrostatic problem and the electric field dependent permittivity of the ferroelectric medium.
-Periodic and random arrays of dielectric rods in a ferroelectric matrix are investigated and we study the effective permittivity, losses, electrically induced anisotropy and tunability of those metamaterials using a two-scale homogenization method.
-
-\usepackage[outdir=./]{epstopdf}
-\graphicspath{{../data/figures/}}
+% \usepackage[outdir=./]{epstopdf}
+% \graphicspath{{./}{../../data/figures/}}
 
@@
 %%%%%%%%% Insert author address here
-\address{School of Engineering and Computer Science, Queen Mary, University of London, London, E1 4NS, United Kingdom}
+\affiliation{School of Engineering and Computer Science, Queen Mary, University of London, London, E1 4NS, United Kingdom}
 
-%%%% Subject entries to be placed here %%%%
-\subject{xxxxx, xxxxx, xxxx}
+% %%%% Subject entries to be placed here %%%%
+% \subject{Electromagnetism, Computer modelling and simulation, Applied mathematics}
+%
+% %%%% Keyword entries to be placed here %%%%
+% \keywords{Homogenization, Ferroelectrics, Metamaterials , Tunability}
+%
+% %%%% Insert corresponding author and its email address}
+% \corres{Benjamin Vial\\
+%  \email{b.vial@qmul.ac.uk}}
 
-%%%% Keyword entries to be placed here %%%%
-\keywords{Homogenization, Ferroelectrics, Metamaterials , Tunability}
+%%%%%%%%%%%%%%% End of first page %%%%%%%%%%%%%%%%%%%%%
 
-%%%% Insert corresponding author and its email address}
-\corres{Benjamin Vial\\
- \email{b.vial@qmul.ac.uk}}
+%
 
@@
 
-%%%%%%%%%% Insert the texts which can accomdate on firstpage in the tag "fmtext" %%%%%
+\maketitle
 
-\begin{fmtext}
  \section{Introduction}
@@
  low-loss non-tunable dielectrics in order to reduce both permittivity
-\end{fmtext}
 
-%%%%%%%%%%%%%%% End of first page %%%%%%%%%%%%%%%%%%%%%
-
-\maketitle
-\noindent values and losses.\\
+\noindent values and losses.
 The effective parameters of those composites have been investigated \cite{sherman_ferroelectric-dielectric_2006, jylha_tunability_2008, sherman_tunability_2004, astafiev_can_2003} and it has been found that the
-permittivity can be greatly reduced while losses are much less sensitive to the dielectric phase addition, and in some can lead to a small increase of the tunability of the mixture.
+permittivity can be greatly reduced while losses are much less sensitive to the dielectric phase addition, and in some situations lead to a small increase of the tunability of the mixture.
 In the context of porous ferroelectrics, the homogenized properties strongly depends on the size and morphology of the pores \cite{okazaki_effects_1973,stanculescu_study_2015}.
@@
 the resulting effective permittivity, dielectric losses, tunability and
-anisotropy significantly differ.
-The difference between earlier sudies in the litterature \cite{padurariu_tailoring_2012,padurariu_field-dependent_2012} is that the non-linear coupling is taken into account beyond the first iteration and that we use two-scale
-convergence homogenization theory to compute the effective parameters at higher frequencies, instead of a capacitance based model.
-We study first a two-dimensional model of metamaterials made of parallel rods with circular cross section,
-considering both square periodic arrays and random distributions within the unit cell of
-a periodic array.
+anisotropy significantly differ. As compared to earlier sudies in the litterature \cite{padurariu_tailoring_2012,padurariu_field-dependent_2012}, we account for
+the non-linear coupling beyond the first iteration and use two-scale
+convergence homogenization analysis to obtain the effective parameters at higher frequencies, instead of a capacitance-based model.
+We first study metamaterials consisting of a squarre array of parallel dielectric rods with circular cross section in a ferroelectric host, and then investigate the effect of random distribution of those rods within the unit cell.
 
@@
 of invariance).
-A uniform biasing field is applied to the sample in order to be able to tune the
-permittivity of the dielectric phase.
-Modelling homogenized properties of this type of mixtures can be done by assuming
+A uniform biasing field is applied in order to be able to tune the effective permittivity. Modelling homogenized properties of this type of mixtures can be done by assuming
 that the electric field distribution is uniform throughout the sample,
 so that the study of the tunability is
-essentially achieved by changing the value of the properties in the ferroelectric phase and computing
-the effective permittivity
-of the composite. We refer this approach as to the uncoupled model in the following.
+essentially achieved by changing the value of the properties in the ferroelectric phase and computing the effective permittivity of the composite.
+We refer this approach as to the uncoupled model in the following.
 However, a more accurate description is to take into account the change of the
@@
  \centering
- \includegraphics[width=0.8\columnwidth]{epsilon_fit}
+ \includegraphics[width=0.75\columnwidth]{epsilon_fit}
  \caption{Variation of the ferroelectric permittivity as a function of the
@@
 However in the TM case, the situation is much more complex: this is a coupled problem since the
-electric field $E=-\grad V$ derived from the
+electric field $\B E=-\grad V$ derived from the
 solution of \equ{eq_elstat} depends on the permittivity distribution, which
@@
 \end{figure}
-Lets us now consider infinitely long dielectric rods of circular cross section
+Lets us now consider a periodc square array of infinitely long dielectric rods of circular cross section
 of radius $r$ embedded in a ferroelectric matrix.\\
@@
 $xx$ components change substantially from the initial conditions.
-This is due to the effect of the distribution
+This is due to the effect of the redistribution
 of the electrostatic field within the unit cell (see Figs.~(\ref{conv2D}.c) and (\ref{conv2D}.d)),
@@
 phase itself, and depending on the topology and permittivity of the rods, one effect would be predominant.
+In the case studied here, the equilibrium permittivity distribution varies strongly along the bias
+ direction and much less orthogonally to it, which adds anisotropy by diminishing the effective
+ permittivity in the $x$ direction. This is local field induced effect is what makes the anisotropy stronger
+ in our coupled model compared to the uncoupled one (cf. Fig.~(\ref{eff_par_2D_TM}.d)).
 Those subtle phenomena can only be rigorously taken into account by employing a coupling formalism
@@
  \centering
- \includegraphics[width=1\textwidth]{effective_params_per}
+ \includegraphics[width=0.9\textwidth]{effective_params_per}
  \caption{Effective parameters of the 2D metamaterials as a function of the
@@
 \subsection{Random case}
-\begin{figure}
- \centering
- \includegraphics[width=0.8\columnwidth]{random_samples_f_50percent}
- \caption{Permittivity distribution of the numerical samples used for $f=0.5$. Dark
-  colour indicates the ferroelectric material while light colour represents the
-  dielectric inclusions.}
- \label{randmatepsi}
-\end{figure}
 
@@
 for low biasing fields and for some particular samples can be greater than the bulk tunability. However,
-at higher applied eelectric fields, normalized tunability becomes smaller than unity and
-is reduced as one adds more dielectric. \\
+at higher applied electric fields, normalized tunability becomes smaller than unity and
+is reduced as one adds more dielectric. For comparison, the homogenized
+parameters are plotted on \fig{eff_par_2Drand_TM_uncpl} in the case where the coupling is
+neglected. One can see that the coupled and uncoupled models give
+similar results for the tunability whereas the losses are still smaller for the coupled case
+at higher fields.\\
 The redistribution of electric field, permittivity and convergence of
@@
 important in this case as well, as both the $x$ and $y$ components of the electrostatic field
-are playing a role. This result in an anisotropy factor that might be greater than $1$,
-but with high variability from sample to sample. However, on average, the anisotropy factor
-increases with increasing dielectric concentration, and the smaller the concentration the more tunable
-it will be.
+are playing a role.
+Because of the relative positions of the rods, both $\varepsilon_{xx}$ and $\varepsilon_{yy}$ are affected
+by the coupling, so that the anisotropy factor for higher fields is reduced as compared to the periodic case.
+However even if there is a substantial variability from sample to sample, on average, the anisotropy factor
+decreases with increasing dielectric concentration.
 
@@
  \centering
- \includegraphics[width=0.9\textwidth]{effpar_rand_cpl}
+ \includegraphics[width=0.9\textwidth]{effpar_rand_cpl.png}
  \caption{Effective parameters of the random 2D mixtures as a function of the
@@
 Importantly, adding more low index and low loss dielectric allows to decrease
-the overall permittivity significantly and slightly lower the losses. On the other hand,
-the higher the dielectric concentration the smaller the tunability would be while
-anisotropy gets higher as the concentration decreases.
+the overall permittivity significantly and slightly lower the losses.
+For the periodic case, the tunability is higher than the bulk due to local field enhancement, whereas
+this effect is strongly suppressed when disorder is introduced. The assymetric redistribution of the permittivity
+induce en effective anisotropy that is added to the one arising purely from the ferroelectric material.
 The properties of the composites are affected by multiple factors:
@@
 
+\section*{Additional information}
+
 \vskip6pt
 
-\enlargethispage{20pt}
-
-\ethics{Insert ethics text here.}
-
-\dataccess{Insert data accessibility text here. '(If no information, then please include the text ``This article has no additional data'').}
-
-\aucontribute{Benjamin Vial wrote devised the research, implemented
+\noindent{The codes necessary to reproduce the results in this article are freely
+available online at this address: \href{https://www.github.com/benvial/ferromtm}{https://www.github.com/benvial/ferromtm}.}\\
+{Benjamin Vial wrote devised the research, implemented
 the codes and wrote the paper. Yang Hao supervised the research and
-co-authored the manuscript.}
-
-\competing{The authors declare no competing interrests.}
-
-\funding{This work was funded by the Engineering and Physical Sciences Research
+co-authored the manuscript.}\\
+{The authors declare no competing interrests.}\\
+{This work was funded by the Engineering and Physical Sciences Research
 Council (EPSRC), UK, under a grant (EP/P005578/1) 'Adaptive Tools for
 Electromagnetics and Materials Modelling to Bridge the Gap between
-  Design and Manufacturing (AOTOMAT)'.}
+Design and Manufacturing (AOTOMAT)'.}\\
+{The authors would like to thanks Henry Giddens for performing the
+measurements of ferroelectric permittivity used in this paper.}\\
 
-\ack{The authors would like to thanks Henry Giddens for performing the
-measurements of ferroelectric permittivity used in this paper.}
+\appendix
 
-\disclaimer{Insert disclaimer text here.}
+\section{Random permittivity distribution and uncoupled effective parameters}
+
+\begin{figure}[h!]
+ \centering
+ \includegraphics[width=0.7\columnwidth]{random_samples_f_50percent}
+ \caption{Permittivity distribution of the numerical samples used for $f=0.5$. Dark
+  colour indicates the ferroelectric material while light colour represents the
+  dielectric inclusions.}
+ \label{randmatepsi}
+\end{figure}
+
+\begin{figure}[h!]
+ \centering
+ \includegraphics[width=0.8\textwidth]{effpar_rand_uncpl.png}
+ \caption{Effective parameters of the random 2D mixtures as a function of the
+  applied electric field for various filling fraction of dielectric, when the
+  coupling is neglected.
+  (a): normalized permittivity, (b): normalized loss tangent, (c): normalized tunability and
+  (d): anisotropy factor. The solid lines represent the average values
+  over the 21 samples and the lighter error bands show a confidence interval corresponding to
+  the standard deviation.}
+ \label{eff_par_2Drand_TM_uncpl}
+\end{figure}
+%
+
+% \disclaimer{Insert disclaimer text here.}
 
@@
 
-% \begin{thebibliography}{9}
-%
-% \end{thebibliography}
+\begin{thebibliography}{99}
 
-\bibliographystyle{RS}
-\bibliography{biblio}
+\bibitem{tagantsev_ferroelectric_2018}
+Tagantsev AK, Sherman VO, Astafiev KF, Venkatesh J, Setter N. 2018
+  Ferroelectric {Materials} for {Microwave} {Tunable} {Applications}. {\em J.
+  Electroceram.} \textbf{11}, 5--66.
+
+\bibitem{vendik_ferroelectric_1999}
+Vendik O, Hollmann E, Kozyrev A, Prudan A. 1999  Ferroelectric tuning of planar
+  and bulk microwave devices. {\em Journal of Superconductivity} \textbf{12},
+  325--338.
+
+\bibitem{lancaster_thin-film_1998}
+Lancaster M, Powell J, Porch A. 1998  Thin-film ferroelectric microwave
+  devices. {\em Superconductor Science and Technology} \textbf{11}, 1323.
+
+\bibitem{xi_oxide_2000}
+Xi X, Li HC, Si W, Sirenko A, Akimov I, Fox J, Clark A, Hao J. 2000  Oxide thin
+  films for tunable microwave devices. {\em Journal of Electroceramics}
+  \textbf{4}, 393--405.
+
+\bibitem{hand_frequency_2008}
+Hand TH, Cummer SA. 2008  Frequency tunable electromagnetic metamaterial using
+  ferroelectric loaded split rings. {\em Journal of Applied Physics}
+  \textbf{103}, 066105.
+
+\bibitem{zhao_experimental_2008}
+Zhao H, Kang L, Zhou J, Zhao Q, Li L, Peng L, Bai Y. 2008  Experimental
+  demonstration of tunable negative phase velocity and negative refraction in a
+  ferromagnetic/ferroelectric composite metamaterial. {\em Applied Physics
+  Letters} \textbf{93}, 201106.
+
+\bibitem{sherman_ferroelectric-dielectric_2006}
+Sherman VO, Tagantsev AK, Setter N, Iddles D, Price T. 2006
+  Ferroelectric-dielectric tunable composites. {\em Journal of Applied Physics}
+  \textbf{99}, 074104.
+
+\bibitem{jylha_tunability_2008}
+Jylha L, Sihvola AH. 2008  Tunability of granular ferroelectric dielectric
+  composites. {\em Progress in Electromagnetics Research} \textbf{78},
+  189--207.
+
+\bibitem{sherman_tunability_2004}
+Sherman VO, Tagantsev AK, Setter N. 2004  Tunability and loss of the
+  ferroelectric-dielectric composites. In {\em 14th {IEEE} {International}
+  {Symposium} on {Applications} of {Ferroelectrics}, 2004. {ISAF}-04. 2004} pp.
+  33--38.
+
+\bibitem{astafiev_can_2003}
+Astafiev KF, Sherman VO, Tagantsev AK, Setter N. 2003  Can the addition of a
+  dielectric improve the figure of merit of a tunable material?. {\em Journal
+  of the European Ceramic Society} \textbf{23}, 2381 -- 2386.
+
+\bibitem{okazaki_effects_1973}
+Okazaki K, Nagata K. 1973  Effects of {Grain} {Size} and {Porosity} on
+  {Electrical} and {Optical} {Properties} of {PLZT} {Ceramics}. {\em Journal of
+  the American Ceramic Society} \textbf{56}, 82--86.
+
+\bibitem{stanculescu_study_2015}
+Stanculescu R, Ciomaga CE, Padurariu L, Galizia P, Horchidan N, Capiani C,
+  Galassi C, Mitoseriu L. 2015  Study of the role of porosity on the functional
+  properties of ({Ba},{Sr}){TiO}3 ceramics. {\em Journal of Alloys and
+  Compounds} \textbf{643}, 79--87.
+
+\bibitem{padurariu_tailoring_2012}
+Padurariu L, Curecheriu L, Galassi C, Mitoseriu L. 2012a  Tailoring non-linear
+  dielectric properties by local field engineering in anisotropic porous
+  ferroelectric structures. {\em Appl. Phys. Lett.} \textbf{100}, 252905.
+
+\bibitem{padurariu_field-dependent_2012}
+Padurariu L, Curecheriu L, Buscaglia V, Mitoseriu L. 2012b  Field-dependent
+  permittivity in nanostructured {BaTiO}$_3$ ceramics: {Modeling} and
+  experimental verification. {\em Phys. Rev. B} \textbf{85}, 224111.
+
+\bibitem{cazacu_tunable_2013}
+Cazacu A, Curecheriu L, Neagu A, Padurariu L, Cernescu A, Lisiecki I, Mitoseriu
+  L. 2013  Tunable gold-chitosan nanocomposites by local field engineering.
+  {\em Appl. Phys. Lett.} \textbf{102}, 222903.
+
+\bibitem{allaire_homogenization_1992}
+Allaire G. 1992  Homogenization and {Two}-{Scale} {Convergence}. {\em SIAM
+  Journal on Mathematical Analysis} \textbf{23}, 1482--1518.
+
+\bibitem{guenneau_homogenization_2000}
+Guenneau S, Zolla F. 2000  Homogenization of {Three}-{Dimensional} {Finite}
+  {Photonic} {Crystals}. {\em Journal of Electromagnetic Waves and
+  Applications} \textbf{14}, 529--530.
+
+\bibitem{landau_electrodynamics_2013}
+Landau LD, Bell J, Kearsley M, Pitaevskii L, Lifshitz E, Sykes J. 2013 {\em
+  Electrodynamics of continuous media} vol.~8.
+elsevier.
+
+\bibitem{zhou_dielectric_2008}
+Zhou K, Boggs SA, Ramprasad R, Aindow M, Erkey C, Alpay SP. 2008  Dielectric
+  response and tunability of a dielectric-paraelectric composite. {\em Applied
+  Physics Letters} \textbf{93}, 102908.
+
+\bibitem{krowne_anisotropic_2002}
+Krowne CM, Daniel M, Kirchoefer SW, Pond JA. 2002  Anisotropic permittivity and
+  attenuation extraction from propagation constant measurements using an
+  anisotropic full-wave {Green}'s function solver for coplanar ferroelectric
+  thin-film devices. {\em IEEE Transactions on Microwave Theory and Techniques}
+  \textbf{50}, 537--548.
+
+\bibitem{geuzaine_gmsh:_2009}
+Geuzaine C, Remacle JF. 2009  Gmsh: {A} 3-{D} finite element mesh generator
+  with built-in pre- and post-processing facilities. {\em International Journal
+  for Numerical Methods in Engineering} \textbf{79}, 1309--1331.
+
+\bibitem{dular_general_1998}
+Dular P, Geuzaine C, Henrotte F, Legros W. 1998  A general environment for the
+  treatment of discrete problems and its application to the finite element
+  method. {\em IEEE Transactions on Magnetics} \textbf{34}, 3395--3398.
+
+\bibitem{amestoy_fully_2001}
+Amestoy PR, Duff IS, Koster J, L'Excellent JY. 2001  A {Fully} {Asynchronous}
+  {Multifrontal} {Solver} {Using} {Distributed} {Dynamic} {Scheduling}. {\em
+  SIAM Journal on Matrix Analysis and Applications} \textbf{23}, 15--41.
+
+\bibitem{bouchitte_homogenization_2004}
+Bouchitté G, Felbacq D. 2004  Homogenization near resonances and artificial
+  magnetism from dielectrics. {\em Comptes Rendus Mathématique} \textbf{339},
+  377 -- 382.
+
+\bibitem{cherednichenko_homogenization_2015}
+Cherednichenko K, Cooper S. 2015  Homogenization of the system of high-contrast
+  {Maxwell} equations. {\em Mathematika} \textbf{61}, 475--500.
+
+\end{thebibliography}
+
+% \bibliographystyle{RS}
+% \bibliography{biblio}
 
 \end{document}
-%
-%
-%
-% \begin{fmtext}
-% \section{Insert A head here}
-% %%%% Insert A head here
-%
-% This demo file is intended to serve as a ``starter file''
-% for rsproca journal papers produced under \LaTeX\ using
-% rsproca\_new.cls v1.0.
-%
-% \subsection{Insert B head here}
-% %%%% Insert B head here
-% Subsection text here.
-%
-% \subsubsection{Insert C head here}
-% %%%% Insert C head here
-% Subsubsection text here.
-%
-% \section{Equations}
-%
-% Sample equations.
-%
-% %%% Numbered equation
-% \begin{align}\label{1.1}
-% \begin{split}
-% \frac{\partial u(t,x)}{\partial t} &= Au(t,x) \left(1-\frac{u(t,x)}{K}\right)-B\frac{u(t-\tau,x) w(t,x)}{1+Eu(t-\tau,x)},\\
-% \frac{\partial w(t,x)}{\partial t} &=\delta \frac{\partial^2w(t,x)}{\partial x^2}-Cw(t,x)+D\frac{u(t-\tau,x)w(t,x)}{1+Eu(t-\tau,x)},
-% \end{split}
-% \end{align}
-%
-% \begin{align}\label{1.2}
-% \begin{split}
-% \frac{dU}{dt} &=\alpha U(t)(\gamma -U(t))-\frac{U(t-\tau)W(t)}{1+U(t-\tau)},\\
-% \frac{dW}{dt} &=-W(t)+\beta\frac{U(t-\tau)W(t)}{1+U(t-\tau)}.
-% \end{split}
-% \end{align}
-%
-% %%%% Unnumbered equation
-% \begin{eqnarray}
-% \frac{\partial(F_1,F_2)}{\partial(c,\omega)}_{(c_0,\omega_0)} = \left|
-% \begin{array}{ll}
-% \frac{\partial F_1}{\partial c} &\frac{\partial F_1}{\partial \omega} \\\noalign{\vskip3pt}
-% \frac{\partial F_2}{\partial c}&\frac{\partial F_2}{\partial \omega}
-% \end{array}\right|_{(c_0,\omega_0)}\notag\\
-% =-4c_0q\omega_0 -4c_0\omega_0p^2 =-4c_0\omega_0(q+p^2)>0.
-% \end{eqnarray}
-% \end{fmtext}
-%
-% %%%%%%%%%%%%%%% End of first page %%%%%%%%%%%%%%%%%%%%%
-%
-% \maketitle
-%
-% \section{Enunciations}
-%
-% \begin{theorem}\label{T0.1}
-% Assume that $\alpha>0, \gamma>1, \beta>\frac{\gamma+1}{\gamma-1}$.
-% Then there exists a small $\tau_1>0$, such that for $\tau\in
-% [0,\tau_1)$, if $c$ crosses $c(\tau)$ from the direction of
-% to  a small amplitude periodic traveling wave solution of
-% (2.1), and the period of $(\check{u}^p(s),\check{w}^p(s))$ is
-% \[
-% \check{T}(c)=c\cdot \left[\frac{2\pi}{\omega(\tau)}+O(c-c(\tau))\right].
-% \]
-% \end{theorem}
-%
-%
-% \begin{condition}\label{C2.2}
-% From (0.8) and (2.10), it holds
-% $\frac{d\omega}{d\tau}<0,\frac{dc}{d\tau}<0$ for $\tau\in
-% [0,\tau_1)$. This fact yields that the system (2.1) with delay
-% $\tau>0$ has the periodic traveling waves for smaller wave speed $c$
-% than that the system (2.1) with $\tau=0$ does. That is, the
-% delay perturbation stimulates an early occurrence of the traveling waves.
-% \end{condition}
-%
-%
-% \section{Figures \& Tables}
-%
-% The output for figure is:\vspace*{-7pt}
-%
-% \begin{figure}[!h]
-% %\centering\includegraphics[width=2.5in]{xxxxxx.eps}
-% %%% where xxxxxx name represents "figurename.eps"
-% \caption{Insert figure caption here}
-% \label{fig_sim}
-% \end{figure}
-%
-% \vspace*{-5pt}
-%
-% \noindent The output for table is:\vspace*{-7pt}
-%
-% \begin{table}[!h]
-% \caption{An Example of a Table}%%%Table caption goes here
-% \label{table_example}
-% \begin{tabular}{llll}%%%The number of columns has to be defined here
-% \hline
-% date &Dutch policy &date &European policy \\
-% \hline
-% 1988 &Memorandum Prevention &1985 &European Directive (85/339) \\
-% 1991--1997 &{\bf Packaging Covenant I} & & \\
-% 1994 &Law Environmental Management &1994 &European Directive (94/62) \\
-% 1997 &Agreement Packaging and Packaging Waste & & \\\hline
-% \end{tabular}
-% \vspace*{-4pt}
-% \end{table}%%%End of the table
-%
-% \section{Conclusion}
-% The conclusion text goes here.
-%
-% \vskip6pt
-%
-% \enlargethispage{20pt}
-%
-% \ethics{Insert ethics text here.}
-%
-% \dataccess{Insert data accessibility text here. '(If no information, then please include the text ``This article has no additional data'').}
-%
-% \aucontribute{Insert author contributions text here (to be included if more than one author).}
-%
-% \competing{Insert competing interests text here.}
-%
-% \funding{Insert funding text here.}
-%
-% \ack{Insert acknowledgment text here.}
-%
-% \disclaimer{Insert disclaimer text here.}
-%
-% %%%%%%%%%% Insert bibliography here %%%%%%%%%%%%%%
-%
-% \vskip2pc
-%
-% % \begin{thebibliography}{9}
-% %
-% % \end{thebibliography}
-%
-% \bibliographystyle{RS}
-% \bibliography{biblio}

### 2019-03-29 ferromtm/visualization/plot_random_fibers.py

@@ -22,7 +22,7 @@ for f in frange:
     for i, ax in enumerate(axarr.ravel()):
         ax.axis("off")
         b = sample[i, :, :]
-        ax.imshow(b.T, cmap="Greens_r")
+        ax.imshow(b, cmap="Greens_r")
 
     figname = "random_samples_f_" + "{0}percent.eps".format(int(f * 100))
     plt.savefig(os.path.join(rootdir, "data", "figures", figname), bbox_inches="tight")

### 2019-03-29 ferromtm/visualization/plots.py

@@ -1,7 +1,5 @@
 import matplotlib as mpl
 
-# mpl.use("Qt5Agg")
-
 mpl.rcParams["legend.fancybox"] = False
 mpl.rcParams["legend.fontsize"] = "small"
 mpl.rcParams["legend.frameon"] = False

### 2019-03-29 ferromtm/visualization/postpro2D.py

@@ -161,7 +161,7 @@ if __name__ == "__main__":
         load_results()
     )
     plt.close("all")
-    fig, ax = plt.subplots(ncols=2, nrows=2, figsize=(6.2, 4.2))
+    fig, ax = plt.subplots(ncols=2, nrows=2, figsize=(6.7, 3.8))
     plot_eff_par(fig, ax)
     plt.tight_layout()
     fig.savefig(os.path.join(rootdir, "data", "figures", "effective_params_per.eps"))

### 2019-03-29 ferromtm/visualization/postpro2D_conv.py

@@ -98,12 +98,12 @@ def plot_potential(ax, v):
     # V = V-np.mean(V)
     Vplot = (V - np.min(V)) / (np.max(V) - np.min(V))
 
-    # Vplot[epsp <= 3] = 0
-    # levels = list(np.linspace(0, 0.1, 15))
-    # levels.extend(list(np.linspace(0.1 + 0.000000001, 0.9, 11)))
-    # levels.extend(list(np.linspace(0.9 + 0.000000001, 1, 15)))
-    # levels = np.array(levels).ravel()
-    levels = 11
+    # Vplot[epsp <= 3] =  np.NaN
+    levels = list(np.linspace(0.0, 0.1, 5))
+    levels.extend(list(np.linspace(0.1 + 1e-9, 0.9, 7)))
+    levels.extend(list(np.linspace(0.9 + 1e-9, 1, 5)))
+    levels = np.array(levels).ravel()
+    # levels = 11
     ax.contour(X, Y, Vplot, levels, linewidths=1, colors="#ababab", linestyles="solid")
 
 
@@ -192,7 +192,7 @@ if __name__ == "__main__":
         load_results()
     )
     plt.close("all")
-    fig, ax = plt.subplots(ncols=3, nrows=2, figsize=(8, 4.2))
+    fig, ax = plt.subplots(ncols=3, nrows=2, figsize=(7, 4))
     plot_eps_conv(ax[0, 0])
     subplot_id(ax=ax[0, 0], id="a")
     plot_tand_conv(ax[1, 0])
@@ -212,12 +212,12 @@ if __name__ == "__main__":
     plt.tight_layout()
     fig.savefig(os.path.join(rootdir, "data", "figures", figname))
 
-    plt.close("all")
-    fig, ax = plt.subplots(ncols=2, nrows=1, figsize=(5, 2))
-    i = 1
-    plot_eps_map_conv(ax[0], i, j=1)
-    subplot_id(ax=ax[0], id="a")
-    i = ncv - 1
-    plot_eps_map_conv(ax[1], i, j=1)
-    subplot_id(ax=ax[1], id="b")
-    plt.tight_layout()
+    # plt.close("all")
+    # fig, ax = plt.subplots(ncols=2, nrows=1, figsize=(5, 2))
+    # i = 1
+    # plot_eps_map_conv(ax[0], i, j=1)
+    # subplot_id(ax=ax[0], id="a")
+    # i = ncv - 1
[…]

### 2019-03-29 ferromtm/visualization/postpro2D_random.py

@@ -247,7 +247,7 @@ if __name__ == "__main__":
         # fig, ax = plt.subplots(ncols=2, nrows=2)
         # plot_eff_par(fig, ax, lin=True)
 
-        fig, ax = plt.subplots(ncols=2, nrows=2, figsize=(6, 4))
+        fig, ax = plt.subplots(ncols=2, nrows=2, figsize=(6.7, 3.8))
         fig.set_rasterized(True)
         [a.set_rasterized(True) for a in ax.ravel()]
         plot_eff_par(fig, ax, lin=False)
@@ -258,7 +258,7 @@ if __name__ == "__main__":
             dpi=300,
         )
 
-        fig, ax = plt.subplots(ncols=2, nrows=2, figsize=(6, 4))
+        fig, ax = plt.subplots(ncols=2, nrows=2, figsize=(6.7, 3.8))
         fig.set_rasterized(True)
         [a.set_rasterized(True) for a in ax.ravel()]
         plot_eff_par(fig, ax, lin=True)

### 2019-04-23 paper/aip/aipsamp.tex
paper jap

% ****** Start of file aipsamp.tex ******
%
%   This file is part of the AIP files in the AIP distribution for REVTeX 4.
%   Version 4.1 of REVTeX, October 2009
%
%   Copyright (c) 2009 American Institute of Physics.
%
%   See the AIP README file for restrictions and more information.
%
% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
% as well as the rest of the prerequisites for REVTeX 4.1
% 
% It also requires running BibTeX. The commands are as follows:
%
%  1)  latex  aipsamp
%  2)  bibtex aipsamp
%  3)  latex  aipsamp
%  4)  latex  aipsamp
%
% Use this file as a source of example code for your aip document.
% Use the file aiptemplate.tex as a template for your document.
\documentclass[%
 aip,
% jmp,
% bmf,
% sd,
% rsi,
 amsmath,amssymb,
%preprint,%
 reprint,%
%author-year,%
%author-numerical,%
% Conference Proceedings
]{revtex4-1}

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{mathptmx}

\begin{document}

\preprint{AIP/123-QED}

\title[Sample title]{Sample Title:\\with Forced Linebreak}
% Force line breaks with \\

\author{A. Author}
 \altaffiliation[Also at ]{Physics Department, XYZ University.}%Lines break automatically or can be forced with \\
\author{B. Author}%
 \email{Second.Author@institution.edu.}
\affiliation{ 
Authors' institution and/or address%\\This line break forced with \textbackslash\textbackslash
}%

\author{C. Author}
 \homepage{http://www.Second.institution.edu/~Charlie.Author.}
\affiliation{%
Second institution and/or address%\\This line break forced% with \\
}%

\date{\today}% It is always \today, today,
             %  but any date may be explicitly specified

\begin{abstract}
An article usually includes an abstract, a concise summary of the work
covered at length in the main body of the article. It is used for
secondary publications and for information retrieval purposes. 
\end{abstract}

\maketitle

\begin{quotation}
The ``lead paragraph'' is encapsulated with the \LaTeX\ 
\verb+quotation+ environment and is formatted as a single paragraph before the first section heading. 
(The \verb+quotation+ environment reverts to its usual meaning after the first sectioning command.) 
Note that numbered references are allowed in the lead paragraph.
%
The lead paragraph will only be found in an article being prepared for the journal \textit{Chaos}.
\end{quotation}

\section{\label{sec:level1}First-level heading:\protect\\ The line
break was forced \lowercase{via} \textbackslash\textbackslash}

This sample document demonstrates proper use of REV\TeX~4.1 (and
\LaTeXe) in manuscripts prepared for submission to AIP
journals. Further information can be found in the documentation included in the distribution or available at
\url{http://authors.aip.org} and in the documentation for 
REV\TeX~4.1 itself.

When commands are referred to in this example file, they are always
shown with their required arguments, using normal \TeX{} format. In
this format, \verb+#1+, \verb+#2+, etc. stand for required
author-supplied arguments to commands. For example, in
\verb+\section{#1}+ the \verb+#1+ stands for the title text of the
author's section heading, and in \verb+\title{#1}+ the \verb+#1+
stands for the title text of the paper.

Line breaks in section headings at all levels can be introduced using
\textbackslash\textbackslash. A blank input line tells \TeX\ that the
paragraph has ended.

\subsection{\label{sec:level2}Second-level heading: Formatting}

This file may be formatted in both the \texttt{preprint} (the default) and
\texttt{reprint} styles; the latter format may be used to 
mimic final journal output. Either format may be used for submission
purposes; however, for peer review and production, AIP will format the
article using the \texttt{preprint} class option. Hence, it is
essential that authors check that their manuscripts format acceptably
under \texttt{preprint}. Manuscripts submitted to AIP that do not
format correctly under the \texttt{preprint} option may be delayed in
both the editorial and production processes.

The \texttt{widetext} environment will make the text the width of the
full page, as on page~\pageref{eq:wideeq}. (Note the use the
\verb+\pageref{#1}+ to get the page number right automatically.) The
width-changing commands only take effect in \texttt{twocolumn}
formatting. It has no effect if \texttt{preprint} formatting is chosen
instead.

\subsubsection{\label{sec:level3}Third-level heading: Citations and Footnotes}

Citations in text refer to entries in the Bibliography;
they use the commands \verb+\cite{#1}+ or \verb+\onlinecite{#1}+. 
Because REV\TeX\ uses the \verb+natbib+ package of Patrick Daly, 
its entire repertoire of commands are available in your document;
see the \verb+natbib+ documentation for further details.
The argument of \verb+\cite+ is a comma-separated list of \emph{keys};
a key may consist of letters and numerals.

By default, citations are numerical; \cite{feyn54} author-year citations are an option. 
To give a textual citation, use \verb+\onlinecite{#1}+: (Refs.~\onlinecite{witten2001,epr,Bire82}). 
REV\TeX\ ``collapses'' lists of consecutive numerical citations when appropriate. 
REV\TeX\ provides the ability to properly punctuate textual citations in author-year style;
this facility works correctly with numerical citations only with \texttt{natbib}'s compress option turned off. 
To illustrate, we cite several together \cite{feyn54,witten2001,epr,Berman1983}, 
and once again (Refs.~\onlinecite{epr,feyn54,Bire82,Berman1983}). 
Note that, when numerical citations are used, the references were sorted into the same order they appear in the bibliography.

A reference within the bibliography is specified with a \verb+\bibitem{#1}+ command,
where the argument is the citation key mentioned above. 
\verb+\bibitem{#1}+ commands may be crafted by hand or, preferably,
generated by using Bib\TeX. 
The AIP styles for REV\TeX~4 include Bib\TeX\ style files
\verb+aipnum.bst+ and \verb+aipauth.bst+, appropriate for
numbered and author-year bibliographies,
respectively. 
REV\TeX~4 will automatically choose the style appropriate for 
the document's selected class options: the default is numerical, and
you obtain the author-year style by specifying a class option of \verb+author-year+.

This sample file demonstrates a simple use of Bib\TeX\ 
via a \verb+\bibliography+ command referencing the \verb+aipsamp.bib+ file.
Running Bib\TeX\ (in this case \texttt{bibtex
aipsamp}) after the first pass of \LaTeX\ produces the file
\verb+aipsamp.bbl+ which contains the automatically formatted
\verb+\bibitem+ commands (including extra markup information via
\verb+\bibinfo+ commands). If not using Bib\TeX, the
\verb+thebibiliography+ environment should be used instead.

\paragraph{Fourth-level heading is run in.}%
Footnotes are produced using the \verb+\footnote{#1}+ command. 
Numerical style citations put footnotes into the 
bibliography\footnote{Automatically placing footnotes into the bibliography requires using BibTeX to compile the bibliography.}.
Author-year and numerical author-year citation styles (each for its own reason) cannot use this method. 
Note: due to the method used to place footnotes in the bibliography, \emph{you
must re-run BibTeX every time you change any of your document's
footnotes}.

\section{Math and Equations}
Inline math may be typeset using the \verb+$+ delimiters. Bold math
symbols may be achieved using the \verb+bm+ package and the
\verb+\bm{#1}+ command it supplies. For instance, a bold $\alpha$ can
be typeset as \verb+$\bm{\alpha}$+ giving $\bm{\alpha}$. Fraktur and
Blackboard (or open face or double struck) characters should be
typeset using the \verb+\mathfrak{#1}+ and \verb+\mathbb{#1}+ commands
respectively. Both are supplied by the \texttt{amssymb} package. For
example, \verb+$\mathbb{R}$+ gives $\mathbb{R}$ and
\verb+$\mathfrak{G}$+ gives $\mathfrak{G}$

In \LaTeX\ there are many different ways to display equations, and a
few preferred ways are noted below. Displayed math will center by
default. Use the class option \verb+fleqn+ to flush equations left.

Below we have numbered single-line equations, the most common kind: 
\begin{eqnarray}
\chi_+(p)\alt{\bf [}2|{\bf p}|(|{\bf p}|+p_z){\bf ]}^{-1/2}
\left(
\begin{array}{c}
|{\bf p}|+p_z\\
px+ip_y
\end{array}\right)\;,
\\
\left\{%
 \openone234567890abc123\alpha\beta\gamma\delta1234556\alpha\beta
 \frac{1\sum^{a}_{b}}{A^2}%
\right\}%
\label{eq:one}.
\end{eqnarray}
Note the open one in Eq.~(\ref{eq:one}).

Not all numbered equations will fit within a narrow column this
way. The equation number will move down automatically if it cannot fit
on the same line with a one-line equation:
\begin{equation}
\left\{
 ab12345678abc123456abcdef\alpha\beta\gamma\delta1234556\alpha\beta
 \frac{1\sum^{a}_{b}}{A^2}%
\right\}.
\end{equation}

When the \verb+\label{#1}+ command is used [cf. input for
Eq.~(\ref{eq:one})], the equation can be referred to in text without
knowing the equation number that \TeX\ will assign to it. Just
use \verb+\ref{#1}+, where \verb+#1+ is the same name that used in
the \verb+\label{#1}+ command.

Unnumbered single-line equations can be typeset
using the \verb+\[+, \verb+\]+ format:
\[g^+g^+ \rightarrow g^+g^+g^+g^+ \dots ~,~~q^+q^+\rightarrow
q^+g^+g^+ \dots ~. \]

\subsection{Multiline equations}

Multiline equations are obtained by using the \verb+eqnarray+
environment.  Use the \verb+\nonumber+ command at the end of each line
to avoid assigning a number:
\begin{eqnarray}
{\cal M}=&&ig_Z^2(4E_1E_2)^{1/2}(l_i^2)^{-1}
\delta_{\sigma_1,-\sigma_2}
(g_{\sigma_2}^e)^2\chi_{-\sigma_2}(p_2)\nonumber\\
&&\times
[\epsilon_jl_i\epsilon_i]_{\sigma_1}\chi_{\sigma_1}(p_1),
\end{eqnarray}
\begin{eqnarray}
\sum \vert M^{\text{viol}}_g \vert ^2&=&g^{2n-4}_S(Q^2)~N^{n-2}
        (N^2-1)\nonumber \\
 & &\times \left( \sum_{i<j}\right)
  \sum_{\text{perm}}
 \frac{1}{S_{12}}
 \frac{1}{S_{12}}
 \sum_\tau c^f_\tau~.
\end{eqnarray}
\textbf{Note:} Do not use \verb+\label{#1}+ on a line of a multiline
equation if \verb+\nonumber+ is also used on that line. Incorrect
cross-referencing will result. Notice the use \verb+\text{#1}+ for
using a Roman font within a math environment.

To set a multiline equation without \emph{any} equation
numbers, use the \verb+\begin{eqnarray*}+,
\verb+\end{eqnarray*}+ format:
\begin{eqnarray*}
\sum \vert M^{\text{viol}}_g \vert ^2&=&g^{2n-4}_S(Q^2)~N^{n-2}
        (N^2-1)\\
 & &\times \left( \sum_{i<j}\right)
 \left(
  \sum_{\text{perm}}\frac{1}{S_{12}S_{23}S_{n1}}
 \right)
 \frac{1}{S_{12}}~.
\end{eqnarray*}
To obtain numbers not normally produced by the automatic numbering,
use the \verb+\tag{#1}+ command, where \verb+#1+ is the desired
equation number. For example, to get an equation number of
(\ref{eq:mynum}),
\begin{equation}
g^+g^+ \rightarrow g^+g^+g^+g^+ \dots ~,~~q^+q^+\rightarrow
q^+g^+g^+ \dots ~. \tag{2.6$'$}\label{eq:mynum}
\end{equation}

A few notes on \verb=\tag{#1}=. \verb+\tag{#1}+ requires
\texttt{amsmath}. The \verb+\tag{#1}+ must come before the
\verb+\label{#1}+, if any. The numbering set with \verb+\tag{#1}+ is
\textit{transparent} to the automatic numbering in REV\TeX{};
therefore, the number must be known ahead of time, and it must be
manually adjusted if other equations are added. \verb+\tag{#1}+ works
with both single-line and multiline equations. \verb+\tag{#1}+ should
only be used in exceptional case - do not use it to number all
equations in a paper.

Enclosing single-line and multiline equations in
\verb+\begin{subequations}+ and \verb+\end{subequations}+ will produce
a set of equations that are ``numbered'' with letters, as shown in
Eqs.~(\ref{subeq:1}) and (\ref{subeq:2}) below:
\begin{subequations}
\label{eq:whole}
\begin{equation}
\left\{
 abc123456abcdef\alpha\beta\gamma\delta1234556\alpha\beta
 \frac{1\sum^{a}_{b}}{A^2}
\right\},\label{subeq:1}
\end{equation}
\begin{eqnarray}
{\cal M}=&&ig_Z^2(4E_1E_2)^{1/2}(l_i^2)^{-1}
(g_{\sigma_2}^e)^2\chi_{-\sigma_2}(p_2)\nonumber\\
&&\times
[\epsilon_i]_{\sigma_1}\chi_{\sigma_1}(p_1).\label{subeq:2}
\end{eqnarray}
\end{subequations}
Putting a \verb+\label{#1}+ command right after the
\verb+\begin{subequations}+, allows one to
reference all the equations in a subequations environment. For
example, the equations in the preceding subequations environment were
Eqs.~(\ref{eq:whole}).

\subsubsection{Wide equations}
The equation that follows is set in a wide format, i.e., it spans
across the full page. The wide format is reserved for long equations
that cannot be easily broken into four lines or less:
\begin{widetext}
\begin{equation}
{\cal R}^{(\text{d})}=
 g_{\sigma_2}^e
 \left(
   \frac{[\Gamma^Z(3,21)]_{\sigma_1}}{Q_{12}^2-M_W^2}
  +\frac{[\Gamma^Z(13,2)]_{\sigma_1}}{Q_{13}^2-M_W^2}
 \right)
 + x_WQ_e
 \left(
   \frac{[\Gamma^\gamma(3,21)]_{\sigma_1}}{Q_{12}^2-M_W^2}
  +\frac{[\Gamma^\gamma(13,2)]_{\sigma_1}}{Q_{13}^2-M_W^2}
 \right)\;. \label{eq:wideeq}
\end{equation}
\end{widetext}
This is typed to show the output is in wide format.
(Since there is no input line between \verb+\equation+ and
this paragraph, there is no paragraph indent for this paragraph.)
\section{Cross-referencing}
REV\TeX{} will automatically number sections, equations, figure
captions, and tables. In order to reference them in text, use the
\verb+\label{#1}+ and \verb+\ref{#1}+ commands. To reference a
particular page, use the \verb+\pageref{#1}+ command.

The \verb+\label{#1}+ should appear in a section heading, within an
equation, or in a table or figure caption. The \verb+\ref{#1}+ command
is used in the text where the citation is to be displayed.  Some
examples: Section~\ref{sec:level1} on page~\pageref{sec:level1},
Table~\ref{tab:table1},%
\begin{table}
\caption{\label{tab:table1}This is a narrow table which fits into a
text column when using \texttt{twocolumn} formatting. Note that
REV\TeX~4 adjusts the intercolumn spacing so that the table fills the
entire width of the column. Table captions are numbered
automatically. This table illustrates left-aligned, centered, and
right-aligned columns.  }
\begin{ruledtabular}
\begin{tabular}{lcr}
Left\footnote{Note a.}&Centered\footnote{Note b.}&Right\\
\hline
1 & 2 & 3\\
10 & 20 & 30\\
100 & 200 & 300\\
\end{tabular}
\end{ruledtabular}
\end{table}
and Fig.~\ref{fig:epsart}.

\section{Figures and Tables}
Figures and tables are typically ``floats''; \LaTeX\ determines their
final position via placement rules. 
\LaTeX\ isn't always successful in automatically placing floats where you wish them.

Figures are marked up with the \texttt{figure} environment, the content of which
imports the image (\verb+\includegraphics+) followed by the figure caption (\verb+\caption+).
The argument of the latter command should itself contain a \verb+\label+ command if you
wish to refer to your figure with \verb+\ref+.

Import your image using either the \texttt{graphics} or
\texttt{graphix} packages. These packages both define the
\verb+\includegraphics{#1}+ command, but they differ in the optional
arguments for specifying the orientation, scaling, and translation of the figure.
Fig.~\ref{fig:epsart}%
\begin{figure}
\includegraphics{fig_1}% Here is how to import EPS art
\caption{\label{fig:epsart} A figure caption. The figure captions are
automatically numbered.}
\end{figure}
is small enough to fit in a single column, while
Fig.~\ref{fig:wide}%
\begin{figure*}
\includegraphics{fig_2}% Here is how to import EPS art
\caption{\label{fig:wide}Use the \texttt{figure*} environment to get a wide
figure, spanning the page in \texttt{twocolumn} formatting.}
\end{figure*}
is too wide for a single column,
so instead the \texttt{figure*} environment has been used.

The analog of the \texttt{figure} environment is \texttt{table}, which uses
the same \verb+\caption+ command.
However, you should type your caption command first within the \texttt{table}, 
instead of last as you did for \texttt{figure}.

The heart of any table is the \texttt{tabular} environment,
which represents the table content as a (vertical) sequence of table rows,
each containing a (horizontal) sequence of table cells. 
Cells are separated by the \verb+&+ character;
the row terminates with \verb+\\+. 
The required argument for the \texttt{tabular} environment
specifies how data are displayed in each of the columns. 
For instance, a column
may be centered (\verb+c+), left-justified (\verb+l+), right-justified (\verb+r+),
or aligned on a decimal point (\verb+d+). 
(Table~\ref{tab:table4}%
\begin{table}
\caption{\label{tab:table4}Numbers in columns Three--Five have been
aligned by using the ``d'' column specifier (requires the
\texttt{dcolumn} package). 
Non-numeric entries (those entries without
a ``.'') in a ``d'' column are aligned on the decimal point. 
Use the
``D'' specifier for more complex layouts. }
\begin{ruledtabular}
\begin{tabular}{ccddd}
One&Two&\mbox{Three}&\mbox{Four}&\mbox{Five}\\
\hline
one&two&\mbox{three}&\mbox{four}&\mbox{five}\\
He&2& 2.77234 & 45672. & 0.69 \\
C\footnote{Some tables require footnotes.}
  &C\footnote{Some tables need more than one footnote.}
  & 12537.64 & 37.66345 & 86.37 \\
\end{tabular}
\end{ruledtabular}
\end{table}
illustrates the use of decimal column alignment.)

Extra column-spacing may be be specified as well, although
REV\TeX~4 sets this spacing so that the columns fill the width of the
table.
Horizontal rules are typeset using the \verb+\hline+
command.
The doubled (or Scotch) rules that appear at the top and
bottom of a table can be achieved by enclosing the \texttt{tabular}
environment within a \texttt{ruledtabular} environment.
Rows whose columns span multiple columns can be typeset using \LaTeX's
\verb+\multicolumn{#1}{#2}{#3}+ command
(for example, see the first row of Table~\ref{tab:table3}).%
\begin{table*}
\caption{\label{tab:table3}This is a wide table that spans the page
width in \texttt{twocolumn} mode. It is formatted using the
\texttt{table*} environment. It also demonstrates the use of
\textbackslash\texttt{multicolumn} in rows with entries that span
more than one column.}
\begin{ruledtabular}
\begin{tabular}{ccccc}
 &\multicolumn{2}{c}{$D_{4h}^1$}&\multicolumn{2}{c}{$D_{4h}^5$}\\
 Ion&1st alternative&2nd alternative&lst alternative
&2nd alternative\\ \hline
 K&$(2e)+(2f)$&$(4i)$ &$(2c)+(2d)$&$(4f)$ \\
 Mn&$(2g)$\footnote{The $z$ parameter of these positions is $z\sim\frac{1}{4}$.}
 &$(a)+(b)+(c)+(d)$&$(4e)$&$(2a)+(2b)$\\
 Cl&$(a)+(b)+(c)+(d)$&$(2g)$\footnote{This is a footnote in a table that spans the full page
width in \texttt{twocolumn} mode. It is supposed to set on the full width of the page, just as the caption does. }
 &$(4e)^{\text{a}}$\\
 He&$(8r)^{\text{a}}$&$(4j)^{\text{a}}$&$(4g)^{\text{a}}$\\
 Ag& &$(4k)^{\text{a}}$& &$(4h)^{\text{a}}$\\
\end{tabular}
\end{ruledtabular}
\end{table*}

The tables in this document illustrate various effects.
Tables that fit in a narrow column are contained in a \texttt{table}
environment.
Table~\ref{tab:table3} is a wide table, therefore set with the
\texttt{table*} environment.
Lengthy tables may need to break across pages.
A simple way to allow this is to specify
the \verb+[H]+ float placement on the \texttt{table} or
\texttt{table*} environment.
Alternatively, using the standard \LaTeXe\ package \texttt{longtable} 
gives more control over how tables break and allows headers and footers 
to be specified for each page of the table.
An example of the use of \texttt{longtable} can be found
in the file \texttt{summary.tex} that is included with the REV\TeX~4
distribution.

There are two methods for setting footnotes within a table (these
footnotes will be displayed directly below the table rather than at
the bottom of the page or in the bibliography).
The easiest
and preferred method is just to use the \verb+\footnote{#1}+
command. This will automatically enumerate the footnotes with
lowercase roman letters.
However, it is sometimes necessary to have
multiple entries in the table share the same footnote.
In this case,
create the footnotes using
\verb+\footnotemark[#1]+ and \verb+\footnotetext[#1]{#2}+.
\texttt{\#1} is a numeric value.
Each time the same value for \texttt{\#1} is used, 
the same mark is produced in the table. 
The \verb+\footnotetext[#1]{#2}+ commands are placed after the \texttt{tabular}
environment. 
Examine the \LaTeX\ source and output for Tables~\ref{tab:table1} and 
\ref{tab:table2}%
\begin{table}
\caption{\label{tab:table2}A table with more columns still fits
properly in a column. Note that several entries share the same
footnote. Inspect the \LaTeX\ input for this table to see
exactly how it is done.}
\begin{ruledtabular}
\begin{tabular}{cccccccc}
 &$r_c$ (\AA)&$r_0$ (\AA)&$\kappa r_0$&
 &$r_c$ (\AA) &$r_0$ (\AA)&$\kappa r_0$\\
\hline
Cu& 0.800 & 14.10 & 2.550 &Sn\footnotemark[1]
& 0.680 & 1.870 & 3.700 \\
Ag& 0.990 & 15.90 & 2.710 &Pb\footnotemark[2]
& 0.450 & 1.930 & 3.760 \\
Au& 1.150 & 15.90 & 2.710 &Ca\footnotemark[3]
& 0.750 & 2.170 & 3.560 \\
Mg& 0.490 & 17.60 & 3.200 &Sr\footnotemark[4]
& 0.900 & 2.370 & 3.720 \\
Zn& 0.300 & 15.20 & 2.970 &Li\footnotemark[2]
& 0.380 & 1.730 & 2.830 \\
Cd& 0.530 & 17.10 & 3.160 &Na\footnotemark[5]
& 0.760 & 2.110 & 3.120 \\
Hg& 0.550 & 17.80 & 3.220 &K\footnotemark[5]
&  1.120 & 2.620 & 3.480 \\
Al& 0.230 & 15.80 & 3.240 &Rb\footnotemark[3]
& 1.330 & 2.800 & 3.590 \\
Ga& 0.310 & 16.70 & 3.330 &Cs\footnotemark[4]
& 1.420 & 3.030 & 3.740 \\
In& 0.460 & 18.40 & 3.500 &Ba\footnotemark[5]
& 0.960 & 2.460 & 3.780 \\
Tl& 0.480 & 18.90 & 3.550 & & & & \\
\end{tabular}
\end{ruledtabular}
\footnotetext[1]{Here's the first, from Ref.~\onlinecite{feyn54}.}
\footnotetext[2]{Here's the second.}
\footnotetext[3]{Here's the third.}
\footnotetext[4]{Here's the fourth.}
\footnotetext[5]{And etc.}
\end{table}
for an illustration.

All AIP journals require that the initial citation of
figures or tables be in numerical order.
\LaTeX's automatic numbering of floats is your friend here:
just put each \texttt{figure} environment immediately following 
its first reference (\verb+\ref+), as we have done in this example file.

\begin{acknowledgments}
We wish to acknowledge the support of the author community in using
REV\TeX{}, offering suggestions and encouragement, testing new versions,
\dots.
\end{acknowledgments}

\appendix

\section{Appendixes}

To start the appendixes, use the \verb+\appendix+ command.
This signals that all following section commands refer to appendixes
instead of regular sections. Therefore, the \verb+\appendix+ command
should be used only once---to set up the section commands to act as
appendixes. Thereafter normal section commands are used. The heading
for a section can be left empty. For example,
\begin{verbatim}
\appendix
\section{}
\end{verbatim}
will produce an appendix heading that says ``APPENDIX A'' and
\begin{verbatim}
\appendix
\section{Background}
\end{verbatim}
will produce an appendix heading that says ``APPENDIX A: BACKGROUND''
(note that the colon is set automatically).

If there is only one appendix, then the letter ``A'' should not
appear. This is suppressed by using the star version of the appendix
command (\verb+\appendix*+ in the place of \verb+\appendix+).

\section{A little more on appendixes}

Observe that this appendix was started by using
\begin{verbatim}
\section{A little more on appendixes}
\end{verbatim}

Note the equation number in an appendix:
\begin{equation}
E=mc^2.
\end{equation}

\subsection{\label{app:subsec}A subsection in an appendix}

You can use a subsection or subsubsection in an appendix. Note the
numbering: we are now in Appendix~\ref{app:subsec}.

\subsubsection{\label{app:subsubsec}A subsubsection in an appendix}
Note the equation numbers in this appendix, produced with the
subequations environment:
\begin{subequations}
\begin{eqnarray}
E&=&mc, \label{appa}
\\
E&=&mc^2, \label{appb}
\\
E&\agt& mc^3. \label{appc}
\end{eqnarray}
\end{subequations}
They turn out to be Eqs.~(\ref{appa}), (\ref{appb}), and (\ref{appc}).

\nocite{*}
\bibliography{aipsamp}% Produces the bibliography via BibTeX.

\end{document}
%
% ****** End of file aipsamp.tex ******

### 2019-04-23 paper/arxiv/main.tex
paper jap

@@
-\documentclass[aps,prb,11pt]{revtex4-1}
+\documentclass[%
+ aip,
+% jmp,
+% bmf,
+% sd,
+% rsi,
+ amsmath,amssymb,
+%preprint,%
+ reprint,%
+%author-year,%
+%author-numerical,%
+% Conference Proceedings
+]{revtex4-1}
 
@@
 %%%% Article title to be placed here
-\title{Homogenization of periodic and random ferroelectric-dielectric composites}
+\title{Enhanced tunability in ferroelectric metamaterials through local field enhancement and the effect of disorder}
 \author{Benjamin Vial and Yang Hao}
@@
 \begin{abstract}
- We investigate the homogenized permittivity of ferroelectric-dielectric mixtures under
+ We investigate the homogenized permittivities of metamaterials made of low index dielectric inclusions
+ in a feroelectric matrix under
  a static electric field. A refined model is used to take into account the coupling
  between the electrostatic problem and the electric field dependent permittivity of the
- ferroelectric material. Periodic and random structures in two dimensions are investigated and
+ ferroelectric material, leading to a local field enhancement and permittivity change in the ferroelectric.
+ Periodic and pseudo-random structures in two dimensions are investigated and
  we study the effective permittivity, losses, electrically induced anisotropy and tunability
- of those metamaterials.
+ of those metamaterials. We show that the tunability of such composites might be substantially
+ enhanced in the periodic case, wherehas introducing disorder in the microstructure
+ weaken the effect of enhanced local permittivity change. Our results may be useful to guide the synthesis of novel
+ composite ceramics with improved characteristics for controllable microwave devices.
 \end{abstract}
@@
  matching networks \cite{tagantsev_ferroelectric_2018}. Both bulk ceramics and thin films have
- been employed to design frequency agile components \cite{vendik_ferroelectric_1999, lancaster_thin-film_1998,xi_oxide_2000} and metamaterials \cite{hand_frequency_2008, zhao_experimental_2008}.
+ been employed to design frequency agile components \cite{vendik_ferroelectric_1999,
+ lancaster_thin-film_1998,xi_oxide_2000} and metamaterials \cite{hand_frequency_2008, zhao_experimental_2008}.
  The main reason of using
  ferroelectric materials is their strong dependence of their permittivity $\varepsilon$
- on an applied electric field $E$, which is measured by their tunability defined as $n = \varepsilon(0)/\varepsilon(E)$.
+ on an applied electric field $E$, which is measured by their tunability defined as $n = \varepsilon(0)/\varepsilon(E)$,
+ along with a non hysteresis behaviour when used in their paraelectric state.
  The key requirements for antenna and microwave applications are large tunability and low losses.
- These two characteristics are correlated and one has to find a trade-off for optimal device performance, which can be quantified by the so called commutation quality factor
+ These two characteristics are correlated and one has to find a trade-off for optimal
+  device performance, which can be quantified by the so called commutation quality factor
  $K = (n -1)^2/(n\, \tan\delta(0)\,\tan\delta(E))$, where $\tan\delta$ is the loss tangent.\\
- These materials have usually high permittivity values,
+ These materials have usually high permittivity values even at microwave frequencies,
  often leading to slow response time and impedance mismatch, which can be an issue in some practical
  applications. Thus it has been considered to mix ferroelectric ceramics to low-index and
- low-loss non-tunable dielectrics in order to reduce both permittivity
-
-\noindent values and losses.
-The effective parameters of those composites have been investigated \cite{sherman_ferroelectric-dielectric_2006, jylha_tunability_2008, sherman_tunability_2004, astafiev_can_2003} and it has been found that the
-permittivity can be greatly reduced while losses are much less sensitive to the dielectric phase addition, and in some situations lead to a small increase of the tunability of the mixture.
-In the context of porous ferroelectrics, the homogenized properties strongly depends on the size and morphology of the pores \cite{okazaki_effects_1973,stanculescu_study_2015}.
-In addition, the influence
-of local field enhancement in the tunability has been shown to be of particular importance \cite{padurariu_tailoring_2012,padurariu_field-dependent_2012,cazacu_tunable_2013}.
+ low-loss non-tunable dielectrics in order to reduce both permittivity values and losses, or to
+ use porous ceramics to achieve the same goals without unwanted chemical reactions at the boundaries between dissimilar materials.
+The effective parameters of those composites have been investigated
+\cite{sherman_ferroelectric-dielectric_2006, jylha_tunability_2008, sherman_tunability_2004, astafiev_can_2003}
+and it has been found that the permittivity can be greatly reduced while losses are much less
+ sensitive to the dielectric phase addition, and in some situations lead to a small
+  increase of the tunability of the mixtures. Analytical models based on the Bruggeman effective
+medium approach for low concentration of dielectrics were derived for diferent configurations (columnar, layered and spherical
+inclusions models) and have succesfully be compared with numerical simulations and experiments \cite{sherman_ferroelectric-dielectric_2006}.
+  In the context of porous ferroelectrics,
+   the homogenized properties strongly depends on the size and morphology of the pores
+    \cite{okazaki_effects_1973,stanculescu_study_2015}.
+    Recently, the concept of tailoring the nonlinear properties of ferroelectric
+     and dielectric structures by local field engineering has been introduced \cite{padurariu_tailoring_2012,padurariu_field-dependent_2012,cazacu_tunable_2013}.
+      It was shown through finite element calculation including the nonlinear coupling, that by employing
+      composite materials made of linear dielectric inclusions into a ferroelectric matrix, one can lower the permittivity while maintaining
+      high tunability, due to the local field in the ferroelectric phase which is tuned by the linear dielectric phase.
+Moreover, the effect of grain sizes in ferroelectric
+ceramics was studied using a model taking the field enhancement into account at
+the grain boundaries, and the predicted behavior succesfully compared to experimental data \cite{padurariu_field-dependent_2012}.
+Generally, there is a need for refined theoretical and numerical models to explain and design
+tunable materials and composites with tailored nonlinear properties.
 \\
-This study investigates the effective permittivity of composites made of dielectric inclusions in a ferroelectric matrix
-by using a two-scale convergence method \cite{allaire_homogenization_1992, guenneau_homogenization_2000}.
+This study investigates the effective permittivity of composites made of
+ dielectric inclusions in a ferroelectric matrix
+by using a two-scale convergence method \cite{allaire_homogenization_1992,
+ guenneau_homogenization_2000}.
 The originality lies in the fact that a fully coupling model is employed to
@@
 the resulting effective permittivity, dielectric losses, tunability and
-anisotropy significantly differ. As compared to earlier sudies in the litterature \cite{padurariu_tailoring_2012,padurariu_field-dependent_2012}, we account for
+anisotropy significantly differ. As compared to earlier sudies in the
+litterature \cite{padurariu_tailoring_2012,padurariu_field-dependent_2012}, we account for
 the non-linear coupling beyond the first iteration and use two-scale
-convergence homogenization analysis to obtain the effective parameters at higher frequencies, instead of a capacitance-based model.
-We first study metamaterials consisting of a squarre array of parallel dielectric rods with circular cross section in a ferroelectric host, and then investigate the effect of random distribution of those rods within the unit cell.
+convergence homogenization analysis to obtain the effective parameters at
+higher frequencies, instead of a capacitance-based model.
+We first study metamaterials consisting of a squarre array of parallel
+dielectric rods with circular cross section in a ferroelectric host, and
+then investigate the effect of random distribution of those rods within the unit cell.
 
@@
 of invariance).
-A uniform biasing field is applied in order to be able to tune the effective permittivity. Modelling homogenized properties of this type of mixtures can be done by assuming
+A uniform biasing field is applied in order to be able to tune the effective permittivity.
+ Modelling homogenized properties of this type of mixtures can be done by assuming
 that the electric field distribution is uniform throughout the sample,
 so that the study of the tunability is
-essentially achieved by changing the value of the properties in the ferroelectric phase and computing the effective permittivity of the composite.
+essentially achieved by changing the value of the properties in the
+ferroelectric phase and computing the effective permittivity of the composite.
 We refer this approach as to the uncoupled model in the following.
@@
 
+\begin{figure}[!t]
+ \centering
+ \includegraphics[width=1\columnwidth]{epsilon_fit}
+ \caption{Variation of the ferroelectric permittivity as a function of the
+  applied electric field (dots: measurements, dashed lines: fit to
+  formula~(\ref{eq_epsf})), for the static case (green) and at microwave frequencies
+  (orange, $f=3.8$ GHz). The fitting parameters are given in Table \ref{table_params_fit}.}
+ \label{fig1}
+\end{figure}
 We use barium strontium titanate (BST) as our ferroelectric material. Measurements
@@
 bell curve typical for a ferroelectric material in its paraelectric state.
-\begin{figure}[!t]
- \centering
- \includegraphics[width=0.75\columnwidth]{epsilon_fit}
- \caption{Variation of the ferroelectric permittivity as a function of the
-  applied electric field (dots: measurements, dashed lines: fit to
-  formula~(\ref{eq_epsf})), for the static case (green) and at microwave frequencies
-  (orange, $f=3.8$ GHz). The fitting parameters are given in Table \ref{table_params_fit}.}
- \label{fig1}
-\end{figure}
 Furthermore, assuming the crystalline principal axes of the ferroelectric material
@@
 \end{table}
+
+\begin{figure*}[!t]
+ \centering
+ \includegraphics[width=0.75\textwidth]{convergence_per}
+ \caption{Convergence of the coupled problem.
+  Real part (a) and loss tangent (b) of the components of the homogenized
+  permittivity tensor as a function of iteration step $i$. The distribution of
+  the normalized electric field (colour map: magnitude in logarithmic scale,
+  lines: equipotential contours) and of the
+  $xx$ component of the permittivity tensor are shown for $i=1$
+  (c and d) and $i=12$ (e and f).
+ }
+ \label{conv2D}
+\end{figure*}
 
@@
 
-% -------------------------------------------------------------------------------
-\subsection{Numerical setup}
+%#########################################################################################
+
+\begin{figure*}[!t]
+ \centering
+ \includegraphics[width=0.75\textwidth]{effective_params_per}
+ \caption{Effective parameters of the 2D metamaterials as a function of the
+  applied electric field for various filling fraction of dielectric.
+  (a): normalized permittivity, (b): normalized loss tangent, (c): normalized tunability and
+  (d): anisotropy factor. The solid lines correspond to the coupled model and
+  the dashed lines to the uncoupled model.}
+ \label{eff_par_2D_TM}
+\end{figure*}
+
+\section{Numerical results}
+In the following numerical results, the dielectric phase is supposed to be
+lossless and non dispersive with $\epsd = 3$ while the ferroelectric material follows the
+permittivity described in section~\ref{permmodel} and has a constant loss
+tangent $\tan \delta^{\rm f} = 10^{-2}$.
 Equations~(\ref{eq_elstat}) and (\ref{eq_hom_annex}) are solved with a Finite Element
@@
 
-%#########################################################################################
-
-\section{Numerical results}
-In the following numerical results, the dielectric phase is supposed to be
-lossless and non dispersive with $\epsd = 3$ while the ferroelectric material follows the
-permittivity described in section~\ref{permmodel} and has a constant loss
-tangent $\tan \delta^{\rm f} = 10^{-2}$.
+\begin{figure*}[!t]
+ \centering
+ \includegraphics[width=0.75\textwidth]{effpar_rand_cpl.png}
+ \caption{Effective parameters of the pseudo-random composites as a function of the
+  applied electric field for various filling fraction of dielectric, when the
+  coupling is taken into account.
+  (a): normalized permittivity, (b): normalized loss tangent, (c): normalized tunability and
+  (d): anisotropy factor. The solid lines represent the average values
+  over the 21 samples and the lighter error bands show a confidence interval corresponding to
+  the standard deviation.}
+ \label{eff_par_2Drand_TM}
+\end{figure*}
+%
+%
+%
 
@@
 \subsection{Two dimensional periodic metamaterial}
-\begin{figure}[!t]
- \centering
- \includegraphics[width=1\textwidth]{convergence_per}
- \caption{Convergence of the coupled problem.
-  Real part (a) and loss tangent (b) of the components of the homogenized
-  permittivity tensor as a function of iteration step $i$. The distribution of
-  the normalized electric field (colour map: magnitude in logarithmic scale,
-  lines: equipotential contours) and of the
-  $xx$ component of the permittivity tensor are shown for $i=1$
-  (c and d) and $i=12$ (e and f).
- }
- \label{conv2D}
-\end{figure}
+
 Lets us now consider a periodc square array of infinitely long dielectric rods of circular cross section
@@
 and are responsible for the difference observed when compared to a simple uncoupled model.\\
-
-\begin{figure}[!t]
+\begin{figure*}[!t]
  \centering
- \includegraphics[width=0.9\textwidth]{effective_params_per}
- \caption{Effective parameters of the 2D metamaterials as a function of the
-  applied electric field for various filling fraction of dielectric.
-  (a): normalized permittivity, (b): normalized loss tangent, (c): normalized tunability and
-  (d): anisotropy factor. The solid lines correspond to the coupled model and
-  the dashed lines to the uncoupled model.}
- \label{eff_par_2D_TM}
-\end{figure}
+ \includegraphics[width=0.75\textwidth]{convergence_rand}
+ \caption{Convergence of the coupled problem in the random case
+  for one sample.
+  Real part (a) and loss tangent (b) of the components of the homogenized
+  permittivity tensor as a function of iteration step $i$. The distribution of
+  the normalized electric field (colour map: magnitude in logarithmic scale,
+  lines: equipotential contours) and of the $xx$ component of the permittivity tensor are shown for $i=1$
+  (c and d) and $i=12$ (e and f).
+ }
+ \label{conv_random}
+\end{figure*}
 
 % -------------------------------------------------------------------------------
-\subsection{Random case}
+\subsection{Pseudo-random case}
 
-We finally study the effect of random particle distribution on the effective parameters of the
+We finally study the effect of random distribution of the inclusions within the unit cell on the effective parameters of the
 composites. This is an important point as fabrication of randomly dispersed
@@
 in between neighbouring inclusions and the smaller the gap the higher the field, hence
-a greater local permittivity change. In addition, even if the distribution of particle is
+a greater local permittivity change. In addition, even if the distribution is
 random, one expects that the anisotropy due to geometry would cancel for a sufficiently large number
-of particles (which is the case as the mean anisotropy factor is close to $1$ when no
+of rods (which is the case as the mean anisotropy factor is close to $1$ when no
 bias field is applied). However, the anisotropy due to ferroelectric properties is
@@
 decreases with increasing dielectric concentration.
-
-\begin{figure}[!t]
- \centering
- \includegraphics[width=0.9\textwidth]{effpar_rand_cpl.png}
- \caption{Effective parameters of the random 2D mixtures as a function of the
-  applied electric field for various filling fraction of dielectric, when the
-  coupling is taken into account.
-  (a): normalized permittivity, (b): normalized loss tangent, (c): normalized tunability and
-  (d): anisotropy factor. The solid lines represent the average values
-  over the 21 samples and the lighter error bands show a confidence interval corresponding to
-  the standard deviation.}
- \label{eff_par_2Drand_TM}
-\end{figure}
-%
-%
-%
-\begin{figure}[!t]
- \centering
- \includegraphics[width=1\textwidth]{convergence_rand}
- \caption{Convergence of the coupled problem in the random case
-  for one sample.
-  Real part (a) and loss tangent (b) of the components of the homogenized
-  permittivity tensor as a function of iteration step $i$. The distribution of
-  the normalized electric field (colour map: magnitude in logarithmic scale,
-  lines: equipotential contours) and of the $xx$ component of the permittivity tensor are shown for $i=1$
-  (c and d) and $i=12$ (e and f).
- }
- \label{conv_random}
-\end{figure}
 
@@
 this effect is strongly suppressed when disorder is introduced. The assymetric redistribution of the permittivity
-induce en effective anisotropy that is added to the one arising purely from the ferroelectric material.
+induce an effective anisotropy that is added to the one arising purely from the ferroelectric material.
 The properties of the composites are affected by multiple factors:
@@
 
-\begin{figure}[h!]
+\begin{figure*}[h!]
  \centering
- \includegraphics[width=0.7\columnwidth]{random_samples_f_50percent}
+ \includegraphics[width=0.8\textwidth]{random_samples_f_50percent}
  \caption{Permittivity distribution of the numerical samples used for $f=0.5$. Dark
@@
  \label{randmatepsi}
-\end{figure}
+\end{figure*}
 
-\begin{figure}[h!]
+\begin{figure*}[h!]
  \centering
@@
  \label{eff_par_2Drand_TM_uncpl}
-\end{figure}
+\end{figure*}
 %

### 2019-04-26 paper/arxiv/main.tex
dev optim

@@
 %
+\begin{figure*}[h!]
+ \centering
+ \includegraphics[width=0.8\textwidth]{random_samples_f_50percent}
+ \caption{Permittivity distribution of the numerical samples used for $f=0.5$. Dark
+  colour indicates the ferroelectric material while light colour represents the
+  dielectric inclusions.}
+ \label{randmatepsi}
+\end{figure*}
 
+\begin{figure*}[h!]
+ \centering
+ \includegraphics[width=0.8\textwidth]{effpar_rand_uncpl.png}
+ \caption{Effective parameters of the random 2D mixtures as a function of the
+  applied electric field for various filling fraction of dielectric, when the
+  coupling is neglected.
+  (a): normalized permittivity, (b): normalized loss tangent, (c): normalized tunability and
+  (d): anisotropy factor. The solid lines represent the average values
+  over the 21 samples and the lighter error bands show a confidence interval corresponding to
+  the standard deviation.}
+ \label{eff_par_2Drand_TM_uncpl}
+\end{figure*}
+%
 \section{Conclusion}
@@
 
-\section*{Additional information}
-
-\vskip6pt
-
-\noindent{The codes necessary to reproduce the results in this article are freely
-available online at this address: \href{https://www.github.com/benvial/ferromtm}{https://www.github.com/benvial/ferromtm}.}\\
-{Benjamin Vial wrote devised the research, implemented
-the codes and wrote the paper. Yang Hao supervised the research and
-co-authored the manuscript.}\\
-{The authors declare no competing interrests.}\\
-{This work was funded by the Engineering and Physical Sciences Research
+\begin{acknowledgments}
+This work was funded by the Engineering and Physical Sciences Research
 Council (EPSRC), UK, under a grant (EP/P005578/1) 'Adaptive Tools for
 Electromagnetics and Materials Modelling to Bridge the Gap between
-Design and Manufacturing (AOTOMAT)'.}\\
-{The authors would like to thanks Henry Giddens for performing the
-measurements of ferroelectric permittivity used in this paper.}\\
+Design and Manufacturing (AOTOMAT)'.\\
+The authors would like to thanks Henry Giddens for performing the
+measurements of ferroelectric permittivity used in this paper.\\
+%
+% Benjamin Vial wrote devised the research, implemented
+% the codes and wrote the paper. Yang Hao supervised the research and
+% co-authored the manuscript.\\
+% The authors declare no competing interrests.\\
+The codes necessary to reproduce the results in this article are freely
+available online at this address: \href{https://www.github.com/benvial/ferromtm}{https://www.github.com/benvial/ferromtm}.
+\end{acknowledgments}
 
-\appendix
+% \appendix
 
-\section{Random permittivity distribution and uncoupled effective parameters}
-
-\begin{figure*}[h!]
- \centering
- \includegraphics[width=0.8\textwidth]{random_samples_f_50percent}
- \caption{Permittivity distribution of the numerical samples used for $f=0.5$. Dark
-  colour indicates the ferroelectric material while light colour represents the
-  dielectric inclusions.}
- \label{randmatepsi}
-\end{figure*}
-
-\begin{figure*}[h!]
- \centering
- \includegraphics[width=0.8\textwidth]{effpar_rand_uncpl.png}
- \caption{Effective parameters of the random 2D mixtures as a function of the
-  applied electric field for various filling fraction of dielectric, when the
-  coupling is neglected.
-  (a): normalized permittivity, (b): normalized loss tangent, (c): normalized tunability and
-  (d): anisotropy factor. The solid lines represent the average values
-  over the 21 samples and the lighter error bands show a confidence interval corresponding to
-  the standard deviation.}
- \label{eff_par_2Drand_TM_uncpl}
-\end{figure*}
-%
-
-% \disclaimer{Insert disclaimer text here.}
+% \section{Random permittivity distribution and uncoupled effective parameters}
 

### 2019-04-26 ferromtm/models/coupled2D.py

@@ -119,7 +119,7 @@ def ref_mesh(fem):
     return fem
 
 
-def init_es(f, E_bias, incl=True, mat=None, parmesh=20, mesh_refine=True):
+def init_es(f, E_bias, incl=True, mat=None, parmesh=20, mesh_refine=True, tmp_dir=None):
     r = (f / pi) ** (1 / 2)
     #####################################
     # # electrostatics
@@ -148,7 +148,10 @@ def init_es(f, E_bias, incl=True, mat=None, parmesh=20, mesh_refine=True):
     fem_es.E_static = E_bias
     fem_es.coupling_flag = True
     # fem_es.tmp_dir = "./estat"
-    fem_es.tmp_dir = tempfile.mkdtemp(prefix="/tmp/benjaminv.")
+    if tmp_dir:
+        fem_es.tmp_dir = tmp_dir
+    else:
+        fem_es.tmp_dir = tempfile.mkdtemp()
     fem_es.mesh_refine = mesh_refine
     fem_es.initialize()
     if incl:
@@ -169,7 +172,7 @@ def init_es(f, E_bias, incl=True, mat=None, parmesh=20, mesh_refine=True):
     return fem_es
 
 
-def init_hom(fem_es):
+def init_hom(fem_es, tmp_dir=None):
     #####################################
     # # homogenization
     #####################################
@@ -189,7 +192,10 @@ def init_hom(fem_es):
     fem_hom.Niy = fem_es.Niy
     fem_hom.eps_incl = fem_es.eps_incl
     fem_hom.eps_host = fem_es.eps_host
-    fem_hom.tmp_dir = tempfile.mkdtemp(prefix="/tmp/benjaminv.")
+    if tmp_dir:
+        fem_hom.tmp_dir = tmp_dir
+    else:
+        fem_hom.tmp_dir = tempfile.mkdtemp()
     fem_hom.coupling_flag = fem_es.coupling_flag
     fem_hom.aniso = True
 

### 2019-04-26 ferromtm/models/optim_test_mean.py

@@ -9,18 +9,6 @@ from aotomat.tools.plottools import *
 eps_interp = [1, 21]
 
 
-import autograd.numpy as np  # Thinly-wrapped version of Numpy
-from autograd import grad as grad_auto
-
-#
-# def taylor_sine(x):  # Taylor approximation to sine function
-#     ca = np.mean(x)
-#     return ca
-#
-# grad_sine = grad(taylor_sine)
-# print( "Gradient of sin(pi) is", grad_sine(np.linspace(0,1,100)))
-
-
 def init_pattern():
     # # material pattern
     nmatx, nmaty = 2 ** 8, 2 ** 8
@@ -38,13 +26,12 @@ def init_pattern():
 mat = init_pattern()
 mat.pattern = mat.normalized_pattern
 
-parmesh = 33
+parmesh = 30
 
 fem_es = init_es(0, 0, incl=False, mat=mat, parmesh=parmesh, mesh_refine=False)
-
 fem_es.quad_mesh_flag = True
 # fem_es.gmsh_verbose = 4
-fem_hom = init_hom(fem_es, tmp_dir="./tmp/test0")
+fem_hom = init_hom(fem_es)
 fem_hom.pola = "TM"
 
 # fem_hom.open_gmsh_gui()
@@ -83,8 +70,8 @@ to.dp = 1e-7
 to.m = 1
 
 ratio_hdes = 1
-n_x = 207
-n_y = 203  # int(n_x * ratio_hdes) +1
+n_x = 203
+n_y = 205  # int(n_x * ratio_hdes) +1
 n_z = 1
 
 to.n_x, to.n_y, to.n_z = n_x, n_y, n_z
@@ -95,9 +82,6 @@ def compute_hom_pb_y(fem_hom, epsi, verbose=False):
     interp = False
     make_pos_tensor_eps(fem_hom, epsi, interp=interp)
     fem_hom.y_flag = True
-
-    fem_hom.path_pos += " ./tmp/test0/source_adj.pos"
-    # print(fem_hom.path_pos)
     fem_hom.compute_solution()
     fem_hom.postprocessing()
     V = fem_hom.get_vol()
@@ -129,94 +113,49 @@ def f_obj(
     fem_hom.adjoint = sens_ana
 
     epsilon, depsilon_dp = to.make_epsilon(p, filt=filt, proj=proj, grad=True)
-    epsi = epsilon, epsilon, epsilon
[…]

### 2019-06-07 paper/arxiv/response_letter.tex
theo experiments and correction of paper

\documentclass[%
 aip,
 amsmath,amssymb,
%preprint,%
 reprint,%
]{revtex4-1}

\usepackage{xcolor}
\definecolor{correction}{HTML}{de5e5e}
\definecolor{reply}{HTML}{249150}
\newcommand{\co}[1]{\textcolor{correction}{#1}}
\newcommand{\rep}[1]{\textcolor{reply}{\textit{Reply:} #1}}

\begin{document}

%%%% Article title to be placed here
\title{Reponse letter for the manuscript "Enhanced tunability in ferroelectric metamaterials through local field enhancement and the effect of disorder"}
\author{Benjamin Vial and Yang Hao}

%%%%%%%%% Insert author address here
\affiliation{School of Engineering and Computer Science, Queen Mary, University of London, London, E1 4NS, United Kingdom}

%

%%%% Abstract text to be placed here %%%%%%%%%%%%
\begin{abstract}
 We would like first to thank the reviewers for their constructive comments and remarks that will surely
 improve the overall quality and clarity of the article. We address here point by point the reviewers concerns and indicate how the manuscript has been revised, with the hope that those changes will satisfy the standards of publication in \textit{Journal of Applied Physics.}
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\maketitle

\section{Reviewer \#1}
\subsection{Evaluations}
\begin{itemize}
  \item Does the manuscript present original and timely results that significantly advance the knowledge in applied physics: Yes
  \item Does the manuscript report on convincing and rigorous data methods and analysis: Yes
  \item Is the manuscript clearly written in correct English well organized and free from ambiguities: Yes
  \item Is the title descriptive of the contents concise interesting and free of acronyms: No
  \item Does the abstract adequately and clearly describe the contents (problem approach findings) of the paper: No
  \item Are the figures in the manuscript necessary adequate well presented and clearly labeled: No
  \item Is the reference list appropriate: No

\end{itemize}

\subsection{Remarks to author(s)}

In this paper the authors present a computational study of dielectric tunability of ferroelectric
 metamaterials. The authors apply a numerical method to a new system that takes into account the
 local near-field effects of metamaterial resonators on the dielectric tunability of ferroelectric
 materials in the metamaterial unit cell.

Overall I found the approach described by the authors to be interesting and I expect it will be useful to
 introduce this two-scale convergence method to microwave metamaterial engineering and perhaps to
  metamaterial research in higher frequency ranges as well.

In principle I think this study is publishable, but I would like to see some important clarifying revisions
 made, all are outlined below. After these revisions are adaquately addressed, I expect to be able to
  recommend publication in JAP. The authors need to address the following:

\begin{enumerate}
\item Title/Abstract/ Introduction of Paper: I think the title/abstract and overall introduction of the
 paper is somewhat misleading. These sections should be revised to make clear that the authors are
  presenting a numerical and computational study. As written, it is unclear whether the paper is presenting
   an experimental observation, or a numerical prediction.\\

\rep{It has been clarified in the abstract and introduction that this is a computational and numerical study.}

\item In the introduction, please outline the actual ferroelectric composites in common use in this field.
 It is useful to know what materials this method can be used to model.

\item In the introduction: Local field engineering and field amplification has become more and more useful
 at other frequency ranges, especially in the THz and near-IR, to control the properties of other materials
  (eg. \href{https://doi.org/10.3390/photonics6010022}{Photonics 2019, 6(1), 22}). Could the authors expand
   on some other systems, besides ferro-electric metamaterials, that this method might apply to. For
    instance maybe tunable
    \href{https://journals.aps.org/prl/abstract/10.1103/PhysRevLett.110.217404}{GaAs meta-devices}.

\item In the introduction: The authors mention that there are generally limitations to the current
 numerical and theoretical models used in the field, but do not go into any detail. Could the authors
  expand on this point? What are the limitations?

\item Theory Section, A. In figure 1, are these electrostatics measurements performed by the authors? It is
 unclear based on the figure and surrounding paragraphs. I assume they are as no citation is provided for
  the data. Could the authors discuss the details of how these measurements were made? This would be useful
   for metamaterials researchers who do not work in this frequency range.

\item Theory: Equation 3 is normally referred to as Gauss' Law (or it is at least Gauss' Law written in
 terms of V).

\item Figure 3 c) It is unclear what is being plotted here. Is this the tunability, n, defined at the
 beginning of the introduction? If so, please label using previously defined notation.

\item Overall the English usage is quite good and the paper is very readable. I did find a few typos
 however and the paper should be proofread again before the next submission. Here are some of the typos I
  found:
\begin{itemize}
  \item Abstract line 7: I believe "wherehas" should be "whereas"

  \item Intro par.2 line 5 "ceramics to" should be "ceramics with"

  \item Intro par 3 line 13 "litterature" should be "literature".

  \item Theory A, last two lines "interrested" should be "interested".
\end{itemize}

\end{enumerate}

\section{Reviewer \#2}
\subsection{Evaluations}

\begin{itemize}
  \item Does the manuscript present original and timely results that significantly advance the knowledge in
   applied physics: Yes
  \item Does the manuscript report on convincing and rigorous data methods and analysis: Yes
  \item Is the manuscript clearly written in correct English well organized and free from ambiguities: Yes
  \item Is the title descriptive of the contents concise interesting and free of acronyms: No
  \item Does the abstract adequately and clearly describe the contents (problem approach findings) of the
   paper: Yes
  \item Are the figures in the manuscript necessary adequate well presented and clearly labeled: Yes
  \item Is the reference list appropriate: Yes
\end{itemize}

\subsection{Remarks to author(s)}

  The paper is interesting and can be published with very small revisions.

  \begin{enumerate}
  \item Although composites are engineered materials, in my opinion, we cannot call "metamaterial" a
   composite if we do not demonstrate specific frequency-dependent behavior and if the regular repeated
    units characteristic to the metamaterial are not smaller than the corresponding wavelength where we
     found the mentioned property. In this paper there is not an analysis vs frequency of the properties,
      so that your material is a di-phase composite. I suggest to change the title.
  \item You gave experimental data for BST ceramics that were used to derive Landau coefficients. It is
   necessary to give some details of the sample (composition?) and measurements or to cite an experimental
    work.
  \item You may compare the results of your simulations with the results of other studies.

\end{enumerate}

\end{document}

### 2019-06-07 paper/arxiv/marked_manuscript.tex
theo experiments and correction of paper

--- 2019-04-26 paper/arxiv/main.tex
@@
 % Conference Proceedings
+linenumbers
 ]{revtex4-1}
@@
 
+\usepackage{xcolor}
+\definecolor{correction}{HTML}{de5e5e}
+\newcommand{\co}[1]{\textcolor{correction}{#1}}
+
 %
@@
 %%%% Article title to be placed here
-\title{Enhanced tunability in ferroelectric metamaterials through local field enhancement and the effect of disorder}
+\title{\co{Enhanced tunability in ferroelectric composites through local field enhancement and the effect of disorder}}
 \author{Benjamin Vial and Yang Hao}
@@
 \begin{abstract}
- We investigate the homogenized permittivities of metamaterials made of low index dielectric inclusions
- in a feroelectric matrix under
+ We investigate \co{numerically} the homogenized permittivities of metamaterials made of low index dielectric inclusions in a feroelectric matrix under
  a static electric field. A refined model is used to take into account the coupling
@@
  Periodic and pseudo-random structures in two dimensions are investigated and
- we study the effective permittivity, losses, electrically induced anisotropy and tunability
+ we \co{compute} the effective permittivity, losses, electrically induced anisotropy and tunability
  of those metamaterials. We show that the tunability of such composites might be substantially
  enhanced in the periodic case, wherehas introducing disorder in the microstructure
- weaken the effect of enhanced local permittivity change. Our results may be useful to guide the synthesis of novel
- composite ceramics with improved characteristics for controllable microwave devices.
+ weaken the effect of enhanced local permittivity change. Our results may be useful to guide the synthesis of novel composite ceramics with improved characteristics for controllable microwave devices.
 \end{abstract}
@@
 \\
-This study investigates the effective permittivity of composites made of
+This study investigates \co{numerically} the effective permittivity of composites made of
  dielectric inclusions in a ferroelectric matrix
@@
 the resulting effective permittivity, dielectric losses, tunability and
-anisotropy significantly differ. As compared to earlier sudies in the
+anisotropy significantly differ. \co{In contrast with} earlier sudies in the
 litterature \cite{padurariu_tailoring_2012,padurariu_field-dependent_2012}, we account for
@@
 higher frequencies, instead of a capacitance-based model.
-We first study metamaterials consisting of a squarre array of parallel
+\co{The model we developped has been implemented with the finite element method (FEM)
+and we realise a systematic computational study of ferroelecric-dielectric mixtures.
+First, we consider} metamaterials consisting of a squarre array of parallel
 dielectric rods with circular cross section in a ferroelectric host, and

### 2019-06-07 ferromtm/models/bst.py

@@ -33,8 +33,7 @@ def fun_fit(par, E, eps_meas_n):
     return np.mean(err) ** 0.5
 
 
-def retrieve_params(E, eps_meas_n):
-    par0 = 1, 1
+def retrieve_params(E, eps_meas_n, par0=(1, 1)):
     cons = {"type": "ineq", "fun": lambda x: np.array([x[0]])}
     opt = minimize(
         fun_fit, par0, args=(E, eps_meas_n), options={"disp": True}, constraints=cons
@@ -44,8 +43,8 @@ def retrieve_params(E, eps_meas_n):
     return xopt
 
 
-def fit():
-    meas = np.load(os.path.join(rootdir, "data", "measurements.npz"))
+def fit(filename, fitname):
+    meas = np.load(os.path.join(rootdir, "data", filename))
     E_exp = meas["E_exp"]
     eps_norm_exp = meas["eps_norm_exp"]
     eps_exp_0 = meas["eps_exp_0"]
@@ -53,7 +52,7 @@ def fit():
     for i in range(2):
         alpha_opt = retrieve_params(E_exp, eps_norm_exp[i])
         fit_params.append(alpha_opt)
-    np.savez(os.path.join(rootdir, "data", "fit_params.npz"), fit_params=fit_params)
+    np.savez(os.path.join(rootdir, "data", fitname), fit_params=fit_params)
     return fit_params
 
 
@@ -82,4 +81,4 @@ def epsilonr_ferroelectric(E_applied, tandelta=1e-2, dc=False):
 
 if __name__ == "__main__":
 
-    fit()
+    fit("measurements.npz", "fit_params.npz")

### 2019-06-07 ferromtm/models/electrostatics/nonper2D/femmodel.py

@@ -1,0 +1,125 @@
+import os
+import subprocess
+import numpy as np
+import scipy as sc
+from pytheas.tools import femio
+from pytheas.basefem import BaseFEM, get_file_path
+
+pi = np.pi
+
+
+class FemModel(BaseFEM):
+    """A class for computing electrostatic fields of
+    a periodic 2D medium using a finite element model.
+    See the base class :class:`BaseFEM` documentation for more info.
+    """
+
+    def __init__(self):
+        super().__init__()
+        self.dir_path = get_file_path(__file__)
+
+        #: flt: caracteristic length (for mesh)
+        self.lambda0 = 1.0
+        #: flt: static applied electric field
+        self.E_static = 1.0
+        self.theta = 0
+
+        #: flt: global mesh parameter
+        #: `MeshElementSize = lambda0/(parmesh*n)`, `n`: refractive index
+        self.parmesh = 10.0
+        self.quad_mesh_flag = False
+        self.coupling_flag = True
+        self.type_des = "elements"
+
+        self.nb_incl = 1
+        #: flt: wavelength to use for meshing
+        self.lambda_mesh = 1.0
+
+        # opto-geometric parameters  -------------------------------------------
+        self.h_pml = 1.0  #: flt: thickness pml
+        self.hx_des = 2.0  #: flt: x - thickness scattering box (design)
+        self.hy_des = 2.0  #: flt: y - thickness scattering box
+        self.a_pml = 1  #: flt: PMLs parameter, real part
+        self.b_pml = 1  #: flt: PMLs parameter, imaginary part
+        self.eps_host = 1 - 0j  #: flt: permittivity host
+        self.eps_des = 1 - 0j  #: flt: permittivity scattering box
+        self.eps_incl = 1 - 0j  #: flt: permittivity inclusion
+        self.dom_des = 5  #: design domain number (check .geo/.pro files)
+
+        # postprocessing -------------------------------------------------
+        #: coords of point for PostProcessing
+        self.xpp, self.ypp = 0, 0
+        self.space2pml_L, self.space2pml_R = 1.0, 1.0
+        self.space2pml_T, self.space2pml_B = 1.0, 1.0
+
+        #: int: number of x points for postprocessing field maps
+        self.Nix = 100
+        self.Niy = 100
+
+    @property
+    def corners_des(self):
+        return -self.hx_des / 2, +self.hx_des / 2, -self.hy_des / 2, +self.hy_des / 2
+
+    @property
[…]

### 2019-06-07 ferromtm/models/nonper.py

@@ -1,0 +1,216 @@
+#!/usr/bin/env python
+
+
+from ferromtm.models.coupled2D import *
+
+# from ferromtm.models.electrostatics.per2D import femmodel
+from ferromtm.models.electrostatics.nonper2D import femmodel
+import importlib
+
+importlib.reload(femmodel)
+
+from ferromtm.tools.utils import *
+
+from ferromtm.models.theo import *
+
+from pytheas.homogenization import *
+
+fem = femmodel.FemModel()
+fem.rm_tmp_dir()
+
+fem.dom_des = 9
+
+# fem.gmsh_verbose=4
+# fem.getdp_verbose=4
+
+fem.parmesh = 11
+fem.parmesh_des = 11
+
+fem.parmesh_incl = 11
+
+
+fem.E_static = 1
+
+epsi0 = epsilonr_ferroelectric(0)
+epsiE = epsilonr_ferroelectric(fem.E_static)
+
+fem.eps_host = epsiE
+
+fem.eps_incl = 2.4
+
+fem.b_pml = 0
+fem.h_pml = 0.1
+
+fem.space2pml_L = 0.1
+fem.space2pml_R = 0.1
+fem.space2pml_B = 0.1
+fem.space2pml_T = 0.1
+
+
+fem.inclusion_flag = True
+
+dx, dy = 1.6, 1.6
+nb_inclx, nb_incly = 2, 3
+
+
+fem.hx_des = nb_inclx * dx
+fem.hy_des = nb_incly * dy
+nb_incl = nb_inclx * nb_incly
+fem.nb_incl = nb_incl
+
+r = 0.5 * 1.1
+
+# Rx = (0.1 + np.random.random(nb_incl) * 0.3) * dx
+# Ry = (0.1 + np.random.random(nb_incl) * 0.3) * dy
+# rot_ = np.random.random(nb_incl) * 2 * pi
+x00 = fem.hx_des / 2 - dx / 2
+y00 = fem.hy_des / 2 - dy / 2
+X0 = np.linspace(-x00, x00, nb_inclx)
+Y0 = np.linspace(-y00, y00, nb_incly)
+X0, Y0 = np.meshgrid(X0, Y0)
+X0 = X0.ravel()
+Y0 = Y0.ravel()
+# Y0 = np.ones(nb_incl) * 0
+# Y0 = (-0.5 + np.random.random(nb_incl) * 1) * dy
[…]

### 2019-06-07 ferromtm/models/per.py

@@ -1,0 +1,102 @@
+#!/usr/bin/env python
+
+
+from ferromtm.models.coupled2D import *
+from ferromtm.models.electrostatics.per2D import femmodel
+import importlib
+
+importlib.reload(femmodel)
+
+from ferromtm.tools.utils import *
+
+
+fem = femmodel.FemModel()
+fem.rm_tmp_dir()
+
+# fem.gmsh_verbose=4
+# fem.getdp_verbose=4
+
+fem.parmesh = 4
+fem.parmesh_des = 4
+
+fem.parmesh_incl = 9
+
+
+fem.E_static = 1
+
+epsi0 = epsilonr_ferroelectric(0)
+epsiE = epsilonr_ferroelectric(fem.E_static)
+
+fem.eps_host = epsiE
+
+# fem.eps_incl = epsiE
+
+fem.b_pml = 0
+fem.h_pml = 0.1
+
+fem.space2pml_L = 0.1
+fem.space2pml_R = 0.1
+fem.space2pml_B = 0.1
+fem.space2pml_T = 0.1
+
+
+fem.inclusion_flag = True
+
+dx, dy = 1, 1
+nb_inclx, nb_incly = 1, 1
+
+
+fem.hx_des = nb_inclx * dx
+fem.hy_des = nb_incly * dy
+nb_incl = nb_inclx * nb_incly
+fem.nb_incl = nb_incl
+
+
+r = 0.4
+
+# Rx = (0.1 + np.random.random(nb_incl) * 0.3) * dx
+# Ry = (0.1 + np.random.random(nb_incl) * 0.3) * dy
+# rot_ = np.random.random(nb_incl) * 2 * pi
+x00 = fem.hx_des / 2 - dx / 2
+y00 = fem.hy_des / 2 - dy / 2
+X0 = np.linspace(-x00, x00, nb_inclx)
+Y0 = np.linspace(-y00, y00, nb_incly)
+X0, Y0 = np.meshgrid(X0, Y0)
+X0 = X0.ravel()
+Y0 = Y0.ravel()
+# Y0 = np.ones(nb_incl) * 0
+# Y0 = (-0.5 + np.random.random(nb_incl) * 1) * dy
+Rx = np.ones(nb_incl) * r * dx
+Ry = np.ones(nb_incl) * r * dy
+rot_ = np.linspace(-pi / 2, pi / 2, nb_incl)
+# rot_ = np.ones(nb_incl) * 0
+
+
[…]

### 2019-06-07 ferromtm/models/theo.py

@@ -1,0 +1,131 @@
+#!/usr/bin/env python
+
+import numpy as np
+
+from ferromtm import rootdir
+from ferromtm.models.bst import *
+
+epsilon0 = 8.8541878128e-12
+
+# fname = "drilled vs undrilled"
+fname = "/home/ben/Documents/projects/animate/results/theo/drilled bst/drilled vs undrilled simalr feild pe"
+f_ = np.loadtxt(fname)
+
+ind0 = 180
+ind1 = 311
+ind2 = 455
+ind3 = 601
+#
+# ind0 = 0
+# ind1 = 601
+
+# f = np.vstack((f_[ind0:ind1, :], np.flipud(f_[ind2:ind3, :])))
+# f = np.vstack((f_[ind0:ind1],(f_[ind2:ind3])))
+
+# f = f_[ind0:ind1, :]
+# f = np.flipud(f_[ind2:ind3, :])
+f = f_
+
+Eh = f[:, 0]
+Ph = f[:, 1]
+E = f[:, 2]
+P = f[:, 3]
+
+
+# ind0 = 460
+# ind1 = 601
+# #
+# # ind0 = 0
+# # ind1 = 601
+#
+# Eh = f[ind0:ind1,0]
+# Ph = f[ind0:ind1,1]
+# E = f[ind0:ind1,2]
+# P = f[ind0:ind1,3]
+#
+
+
+eps = np.gradient(P) / np.gradient(E) * 1e-6 / epsilon0
+eps0 = eps[300]
+eps = np.hstack((eps[ind0:ind1], np.flipud(eps[ind2:ind3])))
+E = np.hstack((E[ind0:ind1], np.flipud(E[ind2:ind3])))
+# eps0 = np.max(eps)
+# eps0 = eps[601-ind0]
+eps /= eps0
+epsh = np.gradient(Ph) / np.gradient(Eh) * 1e-6 / epsilon0
+epsh0 = epsh[300]
+epsh = np.hstack((epsh[ind0:ind1], np.flipud(epsh[ind2:ind3])))
+Eh = np.hstack((Eh[ind0:ind1], np.flipud(Eh[ind2:ind3])))
+epsh /= epsh0
+
+
+def fit(filename, fitname, par0=(1, 1)):
+    meas = np.load(os.path.join(rootdir, "data", filename))
+    E_exp = meas["E_exp"]
+    eps_norm_exp = meas["eps_norm_exp"]
[…]

### 2019-06-10 poster/main_poster.tex
poster

\documentclass[final,12pt]{beamer} % use beamer
\include{preamble}

\begin{document}
\color{fresnelblack}
\date{\today}
\title{Effective parameters of ferroelectric dielectric mixtures}
\subtitle{}
\author{B. Vial and Y. Hao }

\begin{frame}

%%%%%%%%%%%%%%%%%%Title, authors and affiliations   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{textblock*}{80cm}(2cm,2cm)
{\hfill \blackfont\fontsize{1.9cm}{1em}\selectfont \textcolor{fresnelorange}{\MakeUppercase{\inserttitle}}\\}\vspace*{2em}
{\hfill \textcolor{white}{\Large\insertauthor}\\}
\vspace*{16pt}
{\hfill \itshape\large\textcolor{white}{
School of Electronic Engineering \& Computer Science, Queen Mary, University of London}}
\end{textblock*}

%%%%%%%%%%%  ABSTRACT %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{textblock*}{79.5cm}(2.5cm,16.2cm)
% \textcolor{fresneldarkblue}{\rule{\columnwidth}{5pt}}\\
%  {\color{fresneldarkblue}\bfseries Abstract:}
{\color{white}{ \blackfont  \bfseries \large \uppercase{Abstract}\\} \vspace{0.5em} 
  \large \itshape
  We investigate the homogenized parameters of ferroelectric-dielectric composites under a static electric field. A numerical model that takes into account the coupling
  between the electrostatic problem and the electric field dependent permittivity of the
  ferroelectric material is used. Metamaterials consisting of periodic and random arrays of rods
  are considered for transverse electric polarization case
  and we study their effective permittivity, losses, electrically induced anisotropy
  and tunability by a two scale convergence homogenization method.}
\end{textblock*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%% Left column  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% 
%%%%%%%%%%%  BOX1 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{textblock*}{38.5cm}(2.5cm,29cm)

\begin{posterblock}{Method}{benchcolor1}

\begin{columns}[t,totalwidth=\columnwidth]
\begin{column}{.55\columnwidth}

  Ferroelectric materials play a crucial role in reconfigurable
  microwave devices, with typical applications including antenna beam steering,
  phase shifters, tunable power splitters, filters, voltage controlled oscillators and
  matching networks \cite{tagantsev_ferroelectric_2018}.

\mysubtitle{Ferroelectric permittivity}

\begin{equation}
 \epsf(E) = \left[\frac{\partial^2 F (P, E)}{\partial P^2} \right]^{-1} = \frac{\epsf(0)}{1 + \alpha P_0^2 + \beta P_0^4},
 \label{eq_epsf}
\end{equation}

\mysubtitle{Normalization of modes}

\mysubtitle{Expansion of the coupled modes}

\end{column}
\begin{column}{.40\columnwidth}
% \vspace*{2cm}
% \begin{figure}
% \centering
% \input{./figures/schemafig1}
%  \end{figure}

\end{column}
\end{columns}

\end{posterblock}
\end{textblock*}
% 
% % 
% %%%%%%%%%%%%% BOX 3 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% \begin{textblock*}{38.5cm}(2.5cm,72cm)
% \begin{posterblock}{Results}{benchcolor1}
%  \mysubtitle{Dielectric rod dimmer}\vspace{-1.5cm}
% 
% \vspace*{0.7cm}
% TE polarization $\B E=E_z\B z$, $\varepsilon_a=\varepsilon_b=10-0.01\ic$, $\varepsilon_h=1$, 
% $\mu_a=\mu_b=\mu_h=1$, $L_x=10^{-2}\,$m, $L_y=3L_x$, gap $d$, $\omega_0=2\pi c/L_y$.
% 
% \begin{columns}[b,totalwidth=\columnwidth]
% \begin{column}{.49\columnwidth}
%  \begin{figure}
%  \centering
%  \includegraphics[width=\columnwidth]{./figures/figd2}
%  \caption{Real (top) and imaginary (bottom) parts of the eigenfrequencies for the first four 
%  coupled modes as a function of normalized gap $d/L_x$. Circles: coupled modes (full wave direct computation), 
%  solid lines: 1 mode coupling model.}
% \end{figure}
% \end{column}
% \begin{column}{.49\columnwidth}
% \vspace*{1cm}\\
% \begin{figure}
%  \centering
%  \includegraphics[width=0.5\columnwidth]{./figures/singlerod1}
%   \includegraphics[width=0.5\columnwidth]{./figures/singlerod2}
%  \caption{Eigenfield $\re(E_z)$ for the modes of the isolated rod.}
% \end{figure}
% \begin{figure}
%  \centering
%  \includegraphics[width=0.5\columnwidth]{./figures/test1}
%   \includegraphics[width=0.5\columnwidth]{./figures/test2}\\
%    \includegraphics[width=0.5\columnwidth]{./figures/test3}
%   \includegraphics[width=0.5\columnwidth]{./figures/test4}\\
%  \caption{Eigenfield $\re(E_z)$ for the coupled modes, $d/L_x=2.1$.}
% \end{figure}
% 
% \end{column}
% \end{columns}
% \vspace*{1cm}
% Very good agreement is obtained with this simple one mode model. \\
% The study of the phase difference between the coefficients $A_i$ and $B_i$ 
% indicates an in-phase (resp. out of phase) hybridization mechanism 
% for modes $C1$ and $C3$ (resp. $C2$ and $C4$).
% 
% \end{posterblock}
% 
% \end{textblock*}
% % 
% % 
% % % 
% % % %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % % 
% % %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % %%%%%%%%%%% Right column  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % 
% % %%%%%%%%%%%%%%%%%%  BOX %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % 
% \begin{textblock*}{38.5cm}(43.5cm,29cm)
% \begin{posterblock}{Results}{benchcolor1}
% 
%  \mysubtitle{Breaking the symmetry}
% Shift $e$ along $y$, $d/L_x=1$.
% 
% \begin{columns}[b,totalwidth=\columnwidth]
% \begin{column}{.49\columnwidth}
% 
% \begin{figure}
% \includegraphics[width=\columnwidth]{./figures/figfne}
%  \caption{Real (top) and imaginary (bottom) parts of the eigenfrequencies for the first four 
%  coupled modes as a function of normalized shift $e/L_y$. Circles: coupled modes (full wave direct computation), 
%  solid lines: 4 modes coupling model.}
%  \end{figure}
% \end{column}
% \begin{column}{.49\columnwidth}
% 
%  \begin{figure}
%   \includegraphics[width=\columnwidth]{./figures/AN}\\
%   \includegraphics[width=0.5\columnwidth]{./figures/etest3}
%   \includegraphics[width=0.5\columnwidth]{./figures/etest4}
%  \caption{Top: norm of coupling coefficient $A$ as a function of 
%  normalized shift $e/L_y$. Bottom: coupled modes for $e/L_y=0.2$.}
%  \end{figure}
% \end{column}
% \end{columns}
% 
% \vspace*{1cm}
% Good agreement is obtained between full wave calculations and our model. \\
% The shift breaks the symmetry of the coupling mechanism, as revealed by 
% the study of the coefficients $A_i$ and $B_i$. For modes $C3$ and $C4$, 
% both modes $A1$ and $A2$ are significantly coupled when $e\neq0$.
% \end{posterblock}
% \end{textblock*}
% % 
% % 
% %%%%%%%%%%%%%%%%%%  BOX %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% \begin{textblock*}{38.5cm}(43.5cm,68.3cm)
% \begin{posterblock}{Conclusion and outlook}{benchcolor1}
% We developped a model for the coupling of quasi-normal modes in meta-molecules, allowing 
% for a fast computation of coupled complex eigenfrequencies and QNMs. The validity of 
% our approach has been illustrated with an example of a dielectric nanorod dimmer. It 
% is found that shifting one of the resonator perpendicular to the dimmer axis induce a 
% symmetry breaking of the coupling mechanism.\\
% Future research directions includes:
% \begin{itemize}
%    \item model for TM polarization
%    \item include magnetic material	
%    \item include dispersion \cite{QNM3}
%    \item more than two coupled resonators
%     \item 3D model
%   \end{itemize}
% 
% \end{posterblock}
% 
% \end{textblock*}
% % % 
% % % 
% %%%%%%%%%%%%%%%%%%%%%  Reference box %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
\begin{textblock*}{38.5cm}(43.5cm,86.cm)
\myblocktitle{References}{fresnelgreenblue}
\color{fresnelblack}
\printbibliography
\end{textblock*}

%%%%%%%%%%%%%%%%%%%%%  Acknowledgments box %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{textblock*}{38.5cm}(43.5cm,105.cm)
\myblocktitle{Acknowledgments}{fresnelgreenblue}
\color{fresnelblack}
This work was funded by the Engineering and Physical
Sciences Research Council (EPSRC), UK under a
Programme Grant (EP/I034548/1) ‘‘The Quest for
Ultimate Electromagnetics using Spatial Transformations
(QUEST).’’
\end{textblock*}
%

\begin{textblock*}{70cm}(12cm,113cm)

{\hfill\semiboldfont \bfseries \color{fresnelorange} \Large CONTACT \& LINKS}\\
\vspace*{0.5em}
\color{white}
\hfill Corresponding author: Benjamin Vial |~\textcolor{fresnelorange}{\href{mailto:b.vial@qmul.ac.uk}{\faEnvelope~b.vial@qmul.ac.uk}}\\
\hfill QUEST |~\textcolor{fresnelorange}{\href{http://www.quest-spatial-transformation.org}{\faExternalLink~www.quest-spatial-transformation.org}}\\
\hfill Antennas \& Electromagnetics Research Group |~\textcolor{fresnelorange}{\href{http://antennas.eecs.qmul.ac.uk}{\faExternalLink~antennas.eecs.qmul.ac.uk}}

\end{textblock*}
%% LOGOS %%%%%%%%%%%

\begin{textblock*}{5.5cm}(2.5cm,114cm)
 \includegraphics[width=\columnwidth]{./logos/logo_epsrc.png}
\end{textblock*}

\begin{textblock*}{6cm}(10cm,114.5cm)
 \includegraphics[width=\columnwidth]{./logos/logo_qmul.png}
\end{textblock*}
% 
% \begin{textblock*}{10.8cm}(17.6cm,114cm)
%  \includegraphics[width=\columnwidth]{./logos/logo_qmul.png}%{logo_black.png}
% \end{textblock*}
% 
% \begin{textblock*}{8cm}(30.cm,114cm)
%  \includegraphics[width=\columnwidth]{./logos/logo_exeter.png}
% \end{textblock*}
% 
% \begin{textblock*}{8.7cm}(39.5cm,114cm)
%  \includegraphics[width=\columnwidth]{./logos/logo_oxford.png}
% \end{textblock*}

\end{frame}

\end{document}

### 2019-06-10 paper/arxiv/response_letter.tex
poster and corrections

@@
 
+\rep{Details about the composition, fabrication and measurements of the samples at DC and microwaves have been added at the beginning of Theory Section, A.}
+
 \item Theory: Equation 3 is normally referred to as Gauss' Law (or it is at least Gauss' Law written in
@@
 
+ \rep{Reference to Gauss' law has been added before Eq. 3}
+
 \item Figure 3 c) It is unclear what is being plotted here. Is this the tunability, n, defined at the
  beginning of the introduction? If so, please label using previously defined notation.
+
+ \rep{The captions of Figure 3 and other plots have been updated with more details (we are plotting normalized values),
+ and more precisions have been added in the main text (section III. A)}
 
@@
 \end{itemize}
+\rep{Those typos and a few other ones have been corrected.}
 

### 2019-06-10 paper/arxiv/marked_manuscript.tex
poster and corrections

@@
 
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{bm}
+\usepackage{graphicx}% Include figure files
+\usepackage{dcolumn}% Align table columns on decimal point
+\usepackage{bm}% bold math
+%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
+%\linenumbers\relax % Commence numbering lines
+
+\usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
+\usepackage{mathptmx}
 
@@
 \begin{abstract}
- We investigate \co{numerically} the homogenized permittivities of metamaterials made of low index dielectric inclusions in a feroelectric matrix under
+ We investigate \co{numerically} the homogenized permittivities of metamaterials made of low index dielectric inclusions in a ferroelectric matrix under
  a static electric field. A refined model is used to take into account the coupling
@@
  of those metamaterials. We show that the tunability of such composites might be substantially
- enhanced in the periodic case, wherehas introducing disorder in the microstructure
+ enhanced in the periodic case, \co{whereas} introducing disorder in the microstructure
  weaken the effect of enhanced local permittivity change. Our results may be useful to guide the synthesis of novel composite ceramics with improved characteristics for controllable microwave devices.
@@
  often leading to slow response time and impedance mismatch, which can be an issue in some practical
- applications. Thus it has been considered to mix ferroelectric ceramics to low-index and
+ applications. Thus it has been considered to mix ferroelectric \co{ceramics with} low-index and
  low-loss non-tunable dielectrics in order to reduce both permittivity values and losses, or to
@@
   increase of the tunability of the mixtures. Analytical models based on the Bruggeman effective
-medium approach for low concentration of dielectrics were derived for diferent configurations (columnar, layered and spherical
-inclusions models) and have succesfully be compared with numerical simulations and experiments \cite{sherman_ferroelectric-dielectric_2006}.
+medium approach for low concentration of dielectrics were derived for different configurations (columnar, layered and spherical
+inclusions models) and have been successfully compared with numerical simulations and experiments \cite{sherman_ferroelectric-dielectric_2006}.
   In the context of porous ferroelectrics,
@@
 ceramics was studied using a model taking the field enhancement into account at
-the grain boundaries, and the predicted behavior succesfully compared to experimental data \cite{padurariu_field-dependent_2012}.
+the grain boundaries, and the predicted behaviour successfully compared to experimental data \cite{padurariu_field-dependent_2012}.
 Generally, there is a need for refined theoretical and numerical models to explain and design
@@
 anisotropy significantly differ. \co{In contrast with} earlier sudies in the
-litterature \cite{padurariu_tailoring_2012,padurariu_field-dependent_2012}, we account for
+\co{literature} \cite{padurariu_tailoring_2012,padurariu_field-dependent_2012}, we account for
 the non-linear coupling beyond the first iteration and use two-scale
@@
 higher frequencies, instead of a capacitance-based model.
-\co{The model we developped has been implemented with the finite element method (FEM)
+\co{The model we developed has been implemented with the finite element method (FEM)
 and we realise a systematic computational study of ferroelecric-dielectric mixtures.
-First, we consider} metamaterials consisting of a squarre array of parallel
+First, we consider} metamaterials consisting of a square array of parallel
 dielectric rods with circular cross section in a ferroelectric host, and
@@
 \end{figure}
-We use barium strontium titanate (BST) as our ferroelectric material. Measurements
-have been carried out at electrostatics and at microwave frequencies, and the normalized permittivity value
-as a function of biasing field are reported on \fig{fig1}.\\
+We use barium strontium titanate (BST) as our ferroelectric material.
+\co{
+${\rm Ba}_{x}{\rm Sr}_{1-x}{\rm TiO}_3$ samples were fabricated using the conventional sintering method with a barium ratio of $x = 0.6$ to obtain a dielectrically tunable material as reported in the literature \cite{agrawal_tunable_2004, hu_preparation_2015}.
+The tunability was measured using an impedance analyzer up to 100 MHz, and at 3.8 GHz using a loaded microstrip split ring resonator \cite{ansari_design_2015}.
+The measured tunability of the in-house BST samples of 27\% under 1kv/mm DC bias was in agreement with those reported elsewhere \cite{agrawal_tunable_2004, hu_preparation_2015}.
+The method presented is however general and only relies of the gradient of the dielectric tunability vs electric field and could be applied to any tunable host material.
+The normalized permittivity value
+as a function of biasing field are reported on \fig{fig1}.\\}
 To describe the permittivity, we make use of the Landau potential
@@
 given by \equ{eq_epsf}. Note that we will use the static values of permittivity
-for the electrostatic modelling, while we are interrested in the homogenized values
+for the electrostatic modelling, while we are \co{interested} in the homogenized values
 of permittivity at microwaves.\\
@@
  \caption{Fitting parameters to model (\ref{eq_epsf}) for the measured permittivity values as a function
-  of applied electrc field shown on \fig{fig1}. }
+  of applied electric field shown on \fig{fig1}. }
  \label{table_params_fit}
@@
   Real part (a) and loss tangent (b) of the components of the homogenized
-  permittivity tensor as a function of iteration step $i$. The distribution of
+  permittivity tensor as a function of iteration step $i$. \co{The values are normalized to the corresponding quantities for the bulk ferroelectric material.} The distribution of
   the normalized electric field (colour map: magnitude in logarithmic scale,
@@
 $\B E_0 = E_{0} \B e_x$ for the TM polarization case.
-To calculate the total electric field in the material, one
-has to solve the electrostatic equation for the potential $V$:
+To calculate the total electric field in the material, \co{one
+has to solve for the potential $V$ satisfying Gauss' law:}
 \begin{equation}
@@
 \subsection{Homogenization}
+\co{When the period of the composite metamaterial is much smaller than the wavelength, one can
+describe the properties of the composite by a bulk medium with homogenized parameters.}
 The effective permittivity for TM polarization is calculated
-using two scale homogenization technique \cite{allaire_homogenization_1992, guenneau_homogenization_2000}.
+using a two scale convergence homogenization technique \cite{allaire_homogenization_1992, guenneau_homogenization_2000}.
 For this purpose, one has to find the solutions
@@
   (d): anisotropy factor. The solid lines correspond to the coupled model and
-  the dashed lines to the uncoupled model.}
+  the dashed lines to the uncoupled model. \co{The values are normalized to the corresponding quantities for the bulk ferroelectric material.}}
  \label{eff_par_2D_TM}
@@
   over the 21 samples and the lighter error bands show a confidence interval corresponding to
-  the standard deviation.}
+  the standard deviation. \co{The values are normalized to the corresponding quantities for the bulk ferroelectric material.}}
  \label{eff_par_2Drand_TM}
 \end{figure*}
-%
-%
 %
@@
 
-Lets us now consider a periodc square array of infinitely long dielectric rods of circular cross section
+Lets us now consider a periodic square array of infinitely long dielectric rods of circular cross section
 of radius $r$ embedded in a ferroelectric matrix.\\
@@
 higher dielectric concentration, and that is larger than the tunability
- of bulk ferroelectric. Two concurrent effects are at stake here: on the one hand
+ of bulk ferroelectric. \co{This can be seen in \fig{eff_par_2D_TM}.c where we plot the tunability of the composites
+ along the $x$ axis, $\tilde{n}(E) = \tilde{\varepsilon_{xx}}(E) / \tilde{\varepsilon_{xx}}(0)$, normalized to the tunability of the bulk ferroelectric $n(E) = \epsf_{xx}(E) / \epsf_{xx}(0)$.}
+ Two concurrent effects are at stake here: on the one hand
 the dilution of ferroelectric makes the composite less tunable, but on the other hand,
@@
  permittivity in the $x$ direction. This is local field induced effect is what makes the anisotropy stronger
- in our coupled model compared to the uncoupled one (cf. Fig.~(\ref{eff_par_2D_TM}.d)).
+ in our coupled model compared to the uncoupled one (cf. Fig.~(\ref{eff_par_2D_TM}.d) \co{where we plot the anisotropy factor \co{$\alpha =\varepsilon_{xx} / \varepsilon_{yy}$}}).
 Those subtle phenomena can only be rigorously taken into account by employing a coupling formalism
@@
   Real part (a) and loss tangent (b) of the components of the homogenized
-  permittivity tensor as a function of iteration step $i$. The distribution of
+  permittivity tensor as a function of iteration step $i$ \co{The values are normalized to the corresponding quantities for the bulk ferroelectric material.}. The distribution of
   the normalized electric field (colour map: magnitude in logarithmic scale,
@@
   over the 21 samples and the lighter error bands show a confidence interval corresponding to
-  the standard deviation.}
+  the standard deviation. \co{The values are normalized to the corresponding quantities for the bulk ferroelectric material.}}
  \label{eff_par_2Drand_TM_uncpl}
@@
 For the periodic case, the tunability is higher than the bulk due to local field enhancement, whereas
-this effect is strongly suppressed when disorder is introduced. The assymetric redistribution of the permittivity
+this effect is strongly suppressed when disorder is introduced. The asymmetric redistribution of the permittivity
 induce an effective anisotropy that is added to the one arising purely from the ferroelectric material.
@@
 This would reveal the frequency dependant artificial magnetism due to "micro-resonances"
-in the high index phase and potentially lead to composites with tunable effective permeability.
+in the high index phase and potentially lead to composites with tunable effective permeability.\\
+To finish, the general method followed by this model could be applied to other type of tunable
+systems including for example ferromagnetic materials, liquid crystals, or
+ field-enhanced carrier dynamics in doped semiconductors
+\cite{keiser_terahertz_2019}
+\cite{fan_nonlinear_2013}
 
@@
 
-\vskip2pc
-
-\begin{thebibliography}{99}
-
-\bibitem{tagantsev_ferroelectric_2018}
-Tagantsev AK, Sherman VO, Astafiev KF, Venkatesh J, Setter N. 2018
-  Ferroelectric {Materials} for {Microwave} {Tunable} {Applications}. {\em J.
-  Electroceram.} \textbf{11}, 5--66.
-
-\bibitem{vendik_ferroelectric_1999}
-Vendik O, Hollmann E, Kozyrev A, Prudan A. 1999  Ferroelectric tuning of planar
-  and bulk microwave devices. {\em Journal of Superconductivity} \textbf{12},
-  325--338.
-
-\bibitem{lancaster_thin-film_1998}
-Lancaster M, Powell J, Porch A. 1998  Thin-film ferroelectric microwave
-  devices. {\em Superconductor Science and Technology} \textbf{11}, 1323.
-
-\bibitem{xi_oxide_2000}
-Xi X, Li HC, Si W, Sirenko A, Akimov I, Fox J, Clark A, Hao J. 2000  Oxide thin
-  films for tunable microwave devices. {\em Journal of Electroceramics}
-  \textbf{4}, 393--405.
-
-\bibitem{hand_frequency_2008}
-Hand TH, Cummer SA. 2008  Frequency tunable electromagnetic metamaterial using
-  ferroelectric loaded split rings. {\em Journal of Applied Physics}
-  \textbf{103}, 066105.
-
-\bibitem{zhao_experimental_2008}
-Zhao H, Kang L, Zhou J, Zhao Q, Li L, Peng L, Bai Y. 2008  Experimental
-  demonstration of tunable negative phase velocity and negative refraction in a
-  ferromagnetic/ferroelectric composite metamaterial. {\em Applied Physics
-  Letters} \textbf{93}, 201106.
-
-\bibitem{sherman_ferroelectric-dielectric_2006}
-Sherman VO, Tagantsev AK, Setter N, Iddles D, Price T. 2006
-  Ferroelectric-dielectric tunable composites. {\em Journal of Applied Physics}
-  \textbf{99}, 074104.
-
-\bibitem{jylha_tunability_2008}
-Jylha L, Sihvola AH. 2008  Tunability of granular ferroelectric dielectric
-  composites. {\em Progress in Electromagnetics Research} \textbf{78},
-  189--207.
-
-\bibitem{sherman_tunability_2004}
-Sherman VO, Tagantsev AK, Setter N. 2004  Tunability and loss of the
-  ferroelectric-dielectric composites. In {\em 14th {IEEE} {International}
-  {Symposium} on {Applications} of {Ferroelectrics}, 2004. {ISAF}-04. 2004} pp.
-  33--38.
-
-\bibitem{astafiev_can_2003}
-Astafiev KF, Sherman VO, Tagantsev AK, Setter N. 2003  Can the addition of a
-  dielectric improve the figure of merit of a tunable material?. {\em Journal
-  of the European Ceramic Society} \textbf{23}, 2381 -- 2386.
-
-\bibitem{okazaki_effects_1973}
-Okazaki K, Nagata K. 1973  Effects of {Grain} {Size} and {Porosity} on
-  {Electrical} and {Optical} {Properties} of {PLZT} {Ceramics}. {\em Journal of
-  the American Ceramic Society} \textbf{56}, 82--86.
-
-\bibitem{stanculescu_study_2015}
-Stanculescu R, Ciomaga CE, Padurariu L, Galizia P, Horchidan N, Capiani C,
-  Galassi C, Mitoseriu L. 2015  Study of the role of porosity on the functional
-  properties of ({Ba},{Sr}){TiO}3 ceramics. {\em Journal of Alloys and
-  Compounds} \textbf{643}, 79--87.
-
-\bibitem{padurariu_tailoring_2012}
-Padurariu L, Curecheriu L, Galassi C, Mitoseriu L. 2012a  Tailoring non-linear
-  dielectric properties by local field engineering in anisotropic porous
-  ferroelectric structures. {\em Appl. Phys. Lett.} \textbf{100}, 252905.
-
-\bibitem{padurariu_field-dependent_2012}
-Padurariu L, Curecheriu L, Buscaglia V, Mitoseriu L. 2012b  Field-dependent
-  permittivity in nanostructured {BaTiO}$_3$ ceramics: {Modeling} and
-  experimental verification. {\em Phys. Rev. B} \textbf{85}, 224111.
-
-\bibitem{cazacu_tunable_2013}
-Cazacu A, Curecheriu L, Neagu A, Padurariu L, Cernescu A, Lisiecki I, Mitoseriu
-  L. 2013  Tunable gold-chitosan nanocomposites by local field engineering.
-  {\em Appl. Phys. Lett.} \textbf{102}, 222903.
-
-\bibitem{allaire_homogenization_1992}
-Allaire G. 1992  Homogenization and {Two}-{Scale} {Convergence}. {\em SIAM
-  Journal on Mathematical Analysis} \textbf{23}, 1482--1518.
-
-\bibitem{guenneau_homogenization_2000}
-Guenneau S, Zolla F. 2000  Homogenization of {Three}-{Dimensional} {Finite}
-  {Photonic} {Crystals}. {\em Journal of Electromagnetic Waves and
-  Applications} \textbf{14}, 529--530.
-
-\bibitem{landau_electrodynamics_2013}
-Landau LD, Bell J, Kearsley M, Pitaevskii L, Lifshitz E, Sykes J. 2013 {\em
-  Electrodynamics of continuous media} vol.~8.
-elsevier.
-
-\bibitem{zhou_dielectric_2008}
-Zhou K, Boggs SA, Ramprasad R, Aindow M, Erkey C, Alpay SP. 2008  Dielectric
-  response and tunability of a dielectric-paraelectric composite. {\em Applied
-  Physics Letters} \textbf{93}, 102908.
-
-\bibitem{krowne_anisotropic_2002}
-Krowne CM, Daniel M, Kirchoefer SW, Pond JA. 2002  Anisotropic permittivity and
-  attenuation extraction from propagation constant measurements using an
-  anisotropic full-wave {Green}'s function solver for coplanar ferroelectric
-  thin-film devices. {\em IEEE Transactions on Microwave Theory and Techniques}
-  \textbf{50}, 537--548.
-
-\bibitem{geuzaine_gmsh:_2009}
-Geuzaine C, Remacle JF. 2009  Gmsh: {A} 3-{D} finite element mesh generator
-  with built-in pre- and post-processing facilities. {\em International Journal
-  for Numerical Methods in Engineering} \textbf{79}, 1309--1331.
-
-\bibitem{dular_general_1998}
-Dular P, Geuzaine C, Henrotte F, Legros W. 1998  A general environment for the
-  treatment of discrete problems and its application to the finite element
-  method. {\em IEEE Transactions on Magnetics} \textbf{34}, 3395--3398.
-
-\bibitem{amestoy_fully_2001}
-Amestoy PR, Duff IS, Koster J, L'Excellent JY. 2001  A {Fully} {Asynchronous}
-  {Multifrontal} {Solver} {Using} {Distributed} {Dynamic} {Scheduling}. {\em
-  SIAM Journal on Matrix Analysis and Applications} \textbf{23}, 15--41.
-
-\bibitem{bouchitte_homogenization_2004}
-Bouchitté G, Felbacq D. 2004  Homogenization near resonances and artificial
-  magnetism from dielectrics. {\em Comptes Rendus Mathématique} \textbf{339},
-  377 -- 382.
-
-\bibitem{cherednichenko_homogenization_2015}
-Cherednichenko K, Cooper S. 2015  Homogenization of the system of high-contrast
-  {Maxwell} equations. {\em Mathematika} \textbf{61}, 475--500.
-
-\end{thebibliography}
-
 % \bibliographystyle{RS}
-% \bibliography{biblio}
+\bibliography{../biblio}
 

### 2019-06-10 poster/main_poster.tex
poster and corrections

@@
 %%%%%%%%%%%  ABSTRACT %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{textblock*}{79.5cm}(2.5cm,16.2cm)
+\begin{textblock*}{79.5cm}(2.5cm,12.2cm)
 % \textcolor{fresneldarkblue}{\rule{\columnwidth}{5pt}}\\
@@
   \large \itshape
+  \begin{columns}[t,totalwidth=\columnwidth]
+
+  \begin{column}{.48\columnwidth}
     We investigate the homogenized parameters of ferroelectric-dielectric composites under a static electric field. A numerical model that takes into account the coupling
     between the electrostatic problem and the electric field dependent permittivity of the
-  ferroelectric material is used. Metamaterials consisting of periodic and random arrays of rods
+    ferroelectric material is used.
+  \end{column}
+
+  \begin{column}{.48\columnwidth}
+    Metamaterials consisting of periodic and random arrays of rods
       are considered for transverse electric polarization case
       and we study their effective permittivity, losses, electrically induced anisotropy
-  and tunability by a two scale convergence homogenization method.}
+      and tunability by a two scale convergence homogenization method.
+  \end{column}
+
+\end{columns}
+
+}
 \end{textblock*}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%  BOX1 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{textblock*}{38.5cm}(2.5cm,29cm)
+
+%%%%%%%%%%%  BOX1 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{textblock*}{38.5cm}(2.5cm,22.5cm)
+  \begin{posterblock}{Context}{benchcolor1}
+    Ferroelectric materials play a crucial role in reconfigurable
+    microwave devices, with typical applications including antenna beam steering,
+    phase shifters, tunable power splitters, filters, voltage controlled oscillators and
+    matching networks \cite{tagantsev_ferroelectric_2018}, and the key requirements are large tunability and low losses.
+     These materials have high permittivity values even at microwave frequencies, which can be an issue in some practical
+     applications. Thus it has been considered to mix ferroelectrics to low-index and
+     low-loss non-tunable dielectrics in order to reduce both permittivity values and losses, or to
+     use porous ceramics \cite{sherman_ferroelectric-dielectric_2006,padurariu_tailoring_2012}.
+
+\end{posterblock}
+\end{textblock*}
+
+\begin{textblock*}{38.5cm}(2.5cm,35cm)
 
@@
 \begin{columns}[t,totalwidth=\columnwidth]
-\begin{column}{.55\columnwidth}
-
-  Ferroelectric materials play a crucial role in reconfigurable
-  microwave devices, with typical applications including antenna beam steering,
-  phase shifters, tunable power splitters, filters, voltage controlled oscillators and
-  matching networks \cite{tagantsev_ferroelectric_2018}.
+\begin{column}{.5\columnwidth}
 
 \mysubtitle{Ferroelectric permittivity}
-
+Landau potential
+given by $F(P,E) = F_0 +  a P^2/2 + b P^4/4 + cP^6/6 - EP$, where $E$ is
+the applied electric field and $P$ is the polarization \cite{landau_electrodynamics_2013, zhou_dielectric_2008}
 \begin{equation}
@@
 \end{equation}
+Anisotropy
+\begin{equation}
+ \epsftens (\B E) =
+ \left(
+ \begin{matrix}
+   \epsf_{xx}(E_x) & 0               & 0 \cr
+   0               & \epsf_{yy}(E_y) & 0 \cr
+   0               & 0               & \epsf_{zz}(E_z) \cr
 
-\mysubtitle{Normalization of modes}
+  \end{matrix}
+ \right)
+ \label{eq_epsftens}
+\end{equation}
 
-\mysubtitle{Expansion of the coupled modes}
+\mysubtitle{Electrostatic model}
+Gauss' law for the potential $V$:
+\begin{equation}
+ \div (\epstens \grad V) = 0
+ \label{eq_elstat}
+\end{equation}
 
 \end{column}
-\begin{column}{.40\columnwidth}
+\begin{column}{.45\columnwidth}
 % \vspace*{2cm}
-% \begin{figure}
-% \centering
-% \input{./figures/schemafig1}
-%  \end{figure}
+\begin{figure}[!t]
+ \centering
+ \includegraphics[width=1.\columnwidth]{epsilon_fit}
+ \caption{Variation of the ferroelectric permittivity as a function of the
+  applied electric field.\vspace*{0.4em}
+  \begin{tabular}{llll}
+   case        & $\epsf(0)$ & $\alpha$ ($\rm \mu m^2/V^2$) & $\beta$ ($\rm \mu m^4/V^4$) \\ \hline
+   static      & 3050       & 0.120                        & 0.024                       \\
+   $f=3.8$ GHz & 165        & 0.240                        & 0.079                       \\
+  \end{tabular}
+  }
+ \label{fig1}
+\end{figure}
+
+\mysubtitle{Coupled problem}
+
+The electric field $\B E=-\grad V$ derived from the
+solution of \equ{eq_elstat} depends on the permittivity distribution, which
+itself depends on the electric field through \equ{eq_epsf}.
 
@@
 \end{columns}
+
+\begin{columns}[t,totalwidth=\columnwidth]
+
+\begin{column}{.64\columnwidth}
+  \mysubtitle{Homogenization}
+  Two scale convergence homogenization \cite{allaire_homogenization_1992, guenneau_homogenization_2000}, TE case:
+  solutions $\psi_j$ of two annex problems
+  % $\mathcal P_j$, $j=\{1, 2\}$:
+  \begin{equation}
+   \div \left[ \xitens \grad(\psi_j + r_j) \right] = 0,
+   \label{eq_hom_annex}
+  \end{equation}
+  where $\B r = (x, y)^{\rm T}$ and $\xitens=\epstens^{\rm T}/ {\rm det }(\epstens)$.
+  The homogenized tensor $\xihom$ is obtained with:
+  \begin{equation}
+   \xihom = \langle \xitens \rangle + \B \phi,
+   \label{eq_hom}
+  \end{equation}
+  where $\langle . \rangle$ denotes the mean value over the unit cell.
+  Correction terms $\B \phi_{ij} = \langle \xitens \grad \psi_i \rangle_j$.\\
+\end{column}
+
+\begin{column}{.3\columnwidth}
+
+  \begin{figure}[!t]
+   \centering
+   \includegraphics[width=1.\columnwidth]{unit_cell}
+   \caption{Periodic unit cell}
+   \label{fig_cell}
+  \end{figure}
+
+  Effective permittivity tensor: $\epshom=\xihom^{\rm T}/ {\rm det }(\xihom)$.
+
+\end{column}
+\end{columns}
+
+\mysubtitle{Open source numerical implementation}
+Equations~(\ref{eq_elstat}) and (\ref{eq_hom_annex}) are solved with a Finite Element
+Method using the freewares Gmsh \cite{geuzaine_gmsh:_2009} and GetDP \cite{dular_general_1998} driven by a Python package.
 
@@
 %
-% \begin{textblock*}{38.5cm}(2.5cm,72cm)
-% \begin{posterblock}{Results}{benchcolor1}
-%  \mysubtitle{Dielectric rod dimmer}\vspace{-1.5cm}
-% 
-% \vspace*{0.7cm}
-% TE polarization $\B E=E_z\B z$, $\varepsilon_a=\varepsilon_b=10-0.01\ic$, $\varepsilon_h=1$, 
-% $\mu_a=\mu_b=\mu_h=1$, $L_x=10^{-2}\,$m, $L_y=3L_x$, gap $d$, $\omega_0=2\pi c/L_y$.
-% 
-% \begin{columns}[b,totalwidth=\columnwidth]
-% \begin{column}{.49\columnwidth}
-%  \begin{figure}
-%  \centering
-%  \includegraphics[width=\columnwidth]{./figures/figd2}
-%  \caption{Real (top) and imaginary (bottom) parts of the eigenfrequencies for the first four 
-%  coupled modes as a function of normalized gap $d/L_x$. Circles: coupled modes (full wave direct computation), 
-%  solid lines: 1 mode coupling model.}
-% \end{figure}
-% \end{column}
-% \begin{column}{.49\columnwidth}
-% \vspace*{1cm}\\
-% \begin{figure}
-%  \centering
-%  \includegraphics[width=0.5\columnwidth]{./figures/singlerod1}
-%   \includegraphics[width=0.5\columnwidth]{./figures/singlerod2}
-%  \caption{Eigenfield $\re(E_z)$ for the modes of the isolated rod.}
-% \end{figure}
-% \begin{figure}
-%  \centering
-%  \includegraphics[width=0.5\columnwidth]{./figures/test1}
-%   \includegraphics[width=0.5\columnwidth]{./figures/test2}\\
-%    \includegraphics[width=0.5\columnwidth]{./figures/test3}
-%   \includegraphics[width=0.5\columnwidth]{./figures/test4}\\
-%  \caption{Eigenfield $\re(E_z)$ for the coupled modes, $d/L_x=2.1$.}
-% \end{figure}
-% 
-% \end{column}
-% \end{columns}
-% \vspace*{1cm}
-% Very good agreement is obtained with this simple one mode model. \\
-% The study of the phase difference between the coefficients $A_i$ and $B_i$ 
-% indicates an in-phase (resp. out of phase) hybridization mechanism 
-% for modes $C1$ and $C3$ (resp. $C2$ and $C4$).
-% 
-% \end{posterblock}
-% 
-% \end{textblock*}
+\begin{textblock*}{38.5cm}(2.5cm,80cm)
+\begin{posterblock}{Results}{benchcolor1}
+ \mysubtitle{Periodic case}
+ \begin{figure}[!t]
+   \centering
+   \includegraphics[width=0.9\textwidth]{convergence_per}
+   \caption{Convergence of the coupled problem.
+    Real part (a) and loss tangent (b) of the components of the homogenized
+    permittivity tensor as a function of iteration step $i$. The distribution of
+    the normalized electric field (colour map: magnitude in logarithmic scale,
+    lines: equipotential contours) and of the
+    $xx$ component of the permittivity tensor are shown for $i=1$
+    (c and d) and $i=12$ (e and f).
+   }
+   \label{conv2D}
+ \end{figure}
+\end{posterblock}
+
+\end{textblock*}
 % %
@@
 % %
-% \begin{textblock*}{38.5cm}(43.5cm,29cm)
-% \begin{posterblock}{Results}{benchcolor1}
-% 
-%  \mysubtitle{Breaking the symmetry}
-% Shift $e$ along $y$, $d/L_x=1$.
-% 
-% \begin{columns}[b,totalwidth=\columnwidth]
-% \begin{column}{.49\columnwidth}
-% 
-% \begin{figure}
-% \includegraphics[width=\columnwidth]{./figures/figfne}
-%  \caption{Real (top) and imaginary (bottom) parts of the eigenfrequencies for the first four 
-%  coupled modes as a function of normalized shift $e/L_y$. Circles: coupled modes (full wave direct computation), 
-%  solid lines: 4 modes coupling model.}
-%  \end{figure}
-% \end{column}
-% \begin{column}{.49\columnwidth}
-% 
-%  \begin{figure}
-%   \includegraphics[width=\columnwidth]{./figures/AN}\\
-%   \includegraphics[width=0.5\columnwidth]{./figures/etest3}
-%   \includegraphics[width=0.5\columnwidth]{./figures/etest4}
-%  \caption{Top: norm of coupling coefficient $A$ as a function of 
-%  normalized shift $e/L_y$. Bottom: coupled modes for $e/L_y=0.2$.}
-%  \end{figure}
-% \end{column}
-% \end{columns}
-% 
-% \vspace*{1cm}
-% Good agreement is obtained between full wave calculations and our model. \\
-% The shift breaks the symmetry of the coupling mechanism, as revealed by 
-% the study of the coefficients $A_i$ and $B_i$. For modes $C3$ and $C4$, 
-% both modes $A1$ and $A2$ are significantly coupled when $e\neq0$.
-% \end{posterblock}
-% \end{textblock*}
-% % 
-% % 
-% %%%%%%%%%%%%%%%%%%  BOX %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% 
-% \begin{textblock*}{38.5cm}(43.5cm,68.3cm)
-% \begin{posterblock}{Conclusion and outlook}{benchcolor1}
-% We developped a model for the coupling of quasi-normal modes in meta-molecules, allowing 
-% for a fast computation of coupled complex eigenfrequencies and QNMs. The validity of 
-% our approach has been illustrated with an example of a dielectric nanorod dimmer. It 
-% is found that shifting one of the resonator perpendicular to the dimmer axis induce a 
-% symmetry breaking of the coupling mechanism.\\
-% Future research directions includes:
-% \begin{itemize}
-%    \item model for TM polarization
-%    \item include magnetic material	
-%    \item include dispersion \cite{QNM3}
-%    \item more than two coupled resonators
-%     \item 3D model
-%   \end{itemize}
-% 
-% \end{posterblock}
-% 
-% \end{textblock*}
+\begin{textblock*}{38.5cm}(43.5cm,22.5cm)
+\begin{posterblock}{Results}{benchcolor1}
+  \vspace*{-0.7em}
+   \mysubtitle{Effective parameters}
+Tunability $n = \varepsilon_{xx}(0)/\varepsilon_{xx}(E)$, anisotropy factor
+$a = \varepsilon_{xx}(E)/\varepsilon_{yy}(E)$
+
+\begin{figure}[!t]
+ \centering
+ \includegraphics[width=0.9\textwidth]{effective_params_per}
+ \caption{Effective parameters of the 2D metamaterials as a function of the
+  applied electric field for various filling fraction of dielectric.
+  (a): normalized permittivity, (b): normalized loss tangent, (c): normalized tunability and
+  (d): anisotropy factor. The solid lines correspond to the coupled model and
+  the dashed lines to the uncoupled model. Values are normalized with respect to the bulk properties.}
+ \label{eff_par_2D_TM}
+\end{figure}
+
+ \mysubtitle{Pseudo-random case}
+   \vspace*{-0.7em}
+ \begin{figure}[!t]
+  \centering
+  \includegraphics[width=0.9\textwidth]{rand}
+  \includegraphics[width=0.9\textwidth]{effpar_rand_cpl}
+  \caption{Effective parameters of the pseudo-random composites as a function of the
+   applied electric field for various filling fraction of dielectric, when the
+   coupling is taken into account.
+   (a): normalized permittivity, (b): normalized loss tangent, (c): normalized tunability and
+   (d): anisotropy factor. The solid lines represent the average values
+   over the 21 samples and the lighter error bands show a confidence interval corresponding to
+   the standard deviation.}
+  \label{eff_par_2Drand_TM}
+ \end{figure}
+\end{posterblock}
+
+\end{textblock*}
 % % %
@@
 %
-\begin{textblock*}{38.5cm}(43.5cm,86.cm)
+\begin{textblock*}{38.5cm}(43.5cm,85.1cm)
 \myblocktitle{References}{fresnelgreenblue}
@@
 \color{fresnelblack}
-This work was funded by the Engineering and Physical
-Sciences Research Council (EPSRC), UK under a
-Programme Grant (EP/I034548/1) ‘‘The Quest for
-Ultimate Electromagnetics using Spatial Transformations
-(QUEST).’’
+This work was funded by the Engineering and Physical Sciences Research
+Council (EPSRC), UK, under a grant (EP/P005578/1) 'Adaptive Tools for
+Electromagnetics and Materials Modelling to Bridge the Gap between
+Design and Manufacturing (AOTOMAT)'
 \end{textblock*}
@@
 \color{white}
-\hfill Corresponding author: Benjamin Vial |~\textcolor{fresnelorange}{\href{mailto:b.vial@qmul.ac.uk}{\faEnvelope~b.vial@qmul.ac.uk}}\\
-\hfill QUEST |~\textcolor{fresnelorange}{\href{http://www.quest-spatial-transformation.org}{\faExternalLink~www.quest-spatial-transformation.org}}\\
+\hfill Corresponding author: Benjamin Vial |~\textcolor{fresnelorange}{\href{mailto:b.vial@qmul.ac.uk}{\faEnvelope~b.vial@qmul.ac.uk}}
+|~\textcolor{fresnelorange}{\href{http://bvial.info}{\faExternalLink~bvial.info}}\\
+\hfill Github |~\textcolor{fresnelorange}{\href{https://github.com/benvial/ferromtm}{\faGithub~github.com/benvial/ferromtm}}\\
 \hfill Antennas \& Electromagnetics Research Group |~\textcolor{fresnelorange}{\href{http://antennas.eecs.qmul.ac.uk}{\faExternalLink~antennas.eecs.qmul.ac.uk}}
@@
 
-\begin{textblock*}{6cm}(10cm,114.5cm)
+\begin{textblock*}{11cm}(10cm,114cm)
  \includegraphics[width=\columnwidth]{./logos/logo_qmul.png}
 \end{textblock*}
+
+\begin{textblock*}{5.5cm}(42.9cm,112.7cm)
+ \includegraphics[width=\columnwidth]{./figs/qrcode.png}
+\end{textblock*}
+
 %

### 2019-06-11 paper/arxiv/response_letter.tex
correc paper

@@
 
+    \rep{We have expanded on this point in the introduction and added possible applications of the model and corresponding references.}
+
 \item In the introduction: The authors mention that there are generally limitations to the current
@@
 
-\rep{Details about the composition, fabrication and measurements of the samples at DC and microwaves have been added at the beginning of Theory Section, A.}
+\rep{Details about the composition, fabrication and measurements of the samples at DC and microwave frequencies have been added at the beginning of Section II A.}
 
@@
   \item Is the reference list appropriate: Yes
+
 \end{itemize}
 
+% ~\\
 \subsection{Remarks to author(s)}
@@
       so that your material is a di-phase composite. I suggest to change the title.
+
+\rep{The title has been changed to \textit{Enhanced tunability in ferroelectric composites through local field
+enhancement and the effect of disorder}}
+
   \item You gave experimental data for BST ceramics that were used to derive Landau coefficients. It is
@@
     work.
+
+    \rep{Details about the composition, fabrication and measurements of the samples at DC and microwave frequencies have been added at the beginning of Section II A.}
+
   \item You may compare the results of your simulations with the results of other studies.

### 2019-06-11 paper/arxiv/marked_manuscript.tex
correc paper

@@
 \begin{abstract}
- We investigate \co{numerically} the homogenized permittivities of metamaterials made of low index dielectric inclusions in a ferroelectric matrix under
+ We investigate \co{numerically} the homogenized permittivities of \co{composites} made of low index dielectric inclusions in a ferroelectric matrix under
  a static electric field. A refined model is used to take into account the coupling
@@
   device performance, which can be quantified by the so called commutation quality factor
- $K = (n -1)^2/(n\, \tan\delta(0)\,\tan\delta(E))$, where $\tan\delta$ is the loss tangent.\\
+ $K = (n -1)^2/(n\, \tan\delta(0)\,\tan\delta(E))$, where $\tan\delta$ is the loss tangent. 
  These materials have usually high permittivity values even at microwave frequencies,
@@
  use porous ceramics to achieve the same goals without unwanted chemical reactions at the boundaries between dissimilar materials.
+\co{In particular, the addition of magnesium oxide in barium strontium titanate (BST) ceramics have been shown to decrease the losses while keeping good tunability \cite{irvin_three-dimensional_2005,chung_low-losses_2008}.
+Ceramics
+ such as $\rm Pb(Zr,Ti)O_3$ (PZT) and $\rm BaTiO_3$ (BT) have been used as fillers in polymer
+ based composites with high dielectric constant \cite{wang_piezoelectric_2012}. Other mixtures include metal–polymer composites \cite{li_ferroelectric_2013}
+ and electroactive polymers such as poly(vinylidene fluoride) (PVDF) with high index dielectric inclusions \cite{hu_preparation_2015}.
+ }
+
 The effective parameters of those composites have been investigated
@@
 tunable materials and composites with tailored nonlinear properties.
-\\
+\co{Note that the general method followed by our coupled model could be applied to other type of tunable
+systems where local field enhancement and amplification is relevant, including for example ferromagnetic metamaterials \cite{carignan_ferromagnetic_2011}, liquid crystals based devices \cite{werner_liquid_2007}, or field-enhanced carrier dynamics in doped semiconductors at other frequency ranges, particularly in the THz and near-infrared
+\cite{keiser_terahertz_2019, fan_nonlinear_2013}.
+}
+
 This study investigates \co{numerically} the effective permittivity of composites made of
@@
 the resulting effective permittivity, dielectric losses, tunability and
-anisotropy significantly differ. \co{In contrast with} earlier sudies in the
+anisotropy significantly differ. \co{In contrast with} earlier studies in the
 \co{literature} \cite{padurariu_tailoring_2012,padurariu_field-dependent_2012}, we account for
@@
 Equations~(\ref{eq_elstat}) and (\ref{eq_hom_annex}) are solved with a Finite Element
-Method using the open source packages Gmsh \cite{geuzaine_gmsh:_2009} and GetDP \cite{dular_general_1998}.
+Method using the open source packages Gmsh \cite{geuzaine_gmsh_2009} and GetDP \cite{dular_general_1998}.
 In both cases we use a square unit cell $\Omega$ of length $d$ with periodic boundary
@@
 in the high index phase and potentially lead to composites with tunable effective permeability.\\
-To finish, the general method followed by this model could be applied to other type of tunable
-systems including for example ferromagnetic materials, liquid crystals, or
- field-enhanced carrier dynamics in doped semiconductors
-\cite{keiser_terahertz_2019}
-\cite{fan_nonlinear_2013}
 
@@
 This work was funded by the Engineering and Physical Sciences Research
-Council (EPSRC), UK, under a grant (EP/P005578/1) 'Adaptive Tools for
+Council (EPSRC), UK, under a grant (EP/P005578/1) "Adaptive Tools for
 Electromagnetics and Materials Modelling to Bridge the Gap between
-Design and Manufacturing (AOTOMAT)'.\\
+Design and Manufacturing (AOTOMAT)".\\
 The authors would like to thanks Henry Giddens for performing the

### 2019-06-11 poster/main_poster.tex
correc paper

@@
     Metamaterials consisting of periodic and random arrays of rods
-      are considered for transverse electric polarization case
+      are considered for the transverse electric polarization case
       and we study their effective permittivity, losses, electrically induced anisotropy
@@
      These materials have high permittivity values even at microwave frequencies, which can be an issue in some practical
-     applications. Thus it has been considered to mix ferroelectrics to low-index and
+     applications. Thus it has been considered to mix ferroelectrics with low-index and
      low-loss non-tunable dielectrics in order to reduce both permittivity values and losses, or to
@@
   Two scale convergence homogenization \cite{allaire_homogenization_1992, guenneau_homogenization_2000}, TE case:
-  solutions $\psi_j$ of two annex problems
-  % $\mathcal P_j$, $j=\{1, 2\}$:
+  solutions $\psi_j$ of two annex problems $\mathcal P_j$, $j=\{1, 2\}$:
   \begin{equation}
@@
   \end{equation}
-  where $\B r = (x, y)^{\rm T}$ and $\xitens=\epstens^{\rm T}/ {\rm det }(\epstens)$.
+  where $\B r = (x, y)^{\rm T}$ and $\xitens=\epstens^{\rm T}/ {\rm det }(\epstens)$.\\
   The homogenized tensor $\xihom$ is obtained with:
@@
 Equations~(\ref{eq_elstat}) and (\ref{eq_hom_annex}) are solved with a Finite Element
-Method using the freewares Gmsh \cite{geuzaine_gmsh:_2009} and GetDP \cite{dular_general_1998} driven by a Python package.
+Method using the libre software Gmsh \cite{geuzaine_gmsh_2009} and GetDP \cite{dular_general_1998} driven by a Python package.
 
@@
 This work was funded by the Engineering and Physical Sciences Research
-Council (EPSRC), UK, under a grant (EP/P005578/1) 'Adaptive Tools for
+Council (EPSRC), UK, under a grant (EP/P005578/1) \textit{"Adaptive Tools for
 Electromagnetics and Materials Modelling to Bridge the Gap between
-Design and Manufacturing (AOTOMAT)'
+Design and Manufacturing (AOTOMAT)"}
 \end{textblock*}

### 2019-06-11 ferromtm/models/nonper.py

@@ -15,127 +15,120 @@ from ferromtm.models.theo import *
 
 from pytheas.homogenization import *
 
-fem = femmodel.FemModel()
-fem.rm_tmp_dir()
-
-fem.dom_des = 9
-
-# fem.gmsh_verbose=4
-# fem.getdp_verbose=4
-
-fem.parmesh = 11
-fem.parmesh_des = 11
-
-fem.parmesh_incl = 11
-
-
-fem.E_static = 1
-
-epsi0 = epsilonr_ferroelectric(0)
-epsiE = epsilonr_ferroelectric(fem.E_static)
-
-fem.eps_host = epsiE
-
-fem.eps_incl = 2.4
-
-fem.b_pml = 0
-fem.h_pml = 0.1
-
-fem.space2pml_L = 0.1
-fem.space2pml_R = 0.1
-fem.space2pml_B = 0.1
-fem.space2pml_T = 0.1
-
-
-fem.inclusion_flag = True
-
-dx, dy = 1.6, 1.6
-nb_inclx, nb_incly = 2, 3
-
-
-fem.hx_des = nb_inclx * dx
-fem.hy_des = nb_incly * dy
-nb_incl = nb_inclx * nb_incly
-fem.nb_incl = nb_incl
-
-r = 0.5 * 1.1
-
-# Rx = (0.1 + np.random.random(nb_incl) * 0.3) * dx
-# Ry = (0.1 + np.random.random(nb_incl) * 0.3) * dy
-# rot_ = np.random.random(nb_incl) * 2 * pi
-x00 = fem.hx_des / 2 - dx / 2
-y00 = fem.hy_des / 2 - dy / 2
-X0 = np.linspace(-x00, x00, nb_inclx)
-Y0 = np.linspace(-y00, y00, nb_incly)
-X0, Y0 = np.meshgrid(X0, Y0)
-X0 = X0.ravel()
-Y0 = Y0.ravel()
-# Y0 = np.ones(nb_incl) * 0
-# Y0 = (-0.5 + np.random.random(nb_incl) * 1) * dy
-Rx = np.ones(nb_incl) * r
-Ry = np.ones(nb_incl) * r
-rot_ = np.linspace(-pi / 2, pi / 2, nb_incl)
-# rot_ = np.ones(nb_incl) * 0
-
-
-fem.initialize()
-
-if fem.inclusion_flag:
-    i = 0
[…]

### 2019-06-11 ferromtm/models/per.py

@@ -1,102 +1,0 @@
-#!/usr/bin/env python
-
-
-from ferromtm.models.coupled2D import *
-from ferromtm.models.electrostatics.per2D import femmodel
-import importlib
-
-importlib.reload(femmodel)
-
-from ferromtm.tools.utils import *
-
-
-fem = femmodel.FemModel()
-fem.rm_tmp_dir()
-
-# fem.gmsh_verbose=4
-# fem.getdp_verbose=4
-
-fem.parmesh = 4
-fem.parmesh_des = 4
-
-fem.parmesh_incl = 9
-
-
-fem.E_static = 1
-
-epsi0 = epsilonr_ferroelectric(0)
-epsiE = epsilonr_ferroelectric(fem.E_static)
-
-fem.eps_host = epsiE
-
-# fem.eps_incl = epsiE
-
-fem.b_pml = 0
-fem.h_pml = 0.1
-
-fem.space2pml_L = 0.1
-fem.space2pml_R = 0.1
-fem.space2pml_B = 0.1
-fem.space2pml_T = 0.1
-
-
-fem.inclusion_flag = True
-
-dx, dy = 1, 1
-nb_inclx, nb_incly = 1, 1
-
-
-fem.hx_des = nb_inclx * dx
-fem.hy_des = nb_incly * dy
-nb_incl = nb_inclx * nb_incly
-fem.nb_incl = nb_incl
-
-
-r = 0.4
-
-# Rx = (0.1 + np.random.random(nb_incl) * 0.3) * dx
-# Ry = (0.1 + np.random.random(nb_incl) * 0.3) * dy
-# rot_ = np.random.random(nb_incl) * 2 * pi
-x00 = fem.hx_des / 2 - dx / 2
-y00 = fem.hy_des / 2 - dy / 2
-X0 = np.linspace(-x00, x00, nb_inclx)
-Y0 = np.linspace(-y00, y00, nb_incly)
-X0, Y0 = np.meshgrid(X0, Y0)
-X0 = X0.ravel()
-Y0 = Y0.ravel()
-# Y0 = np.ones(nb_incl) * 0
-# Y0 = (-0.5 + np.random.random(nb_incl) * 1) * dy
-Rx = np.ones(nb_incl) * r * dx
-Ry = np.ones(nb_incl) * r * dy
-rot_ = np.linspace(-pi / 2, pi / 2, nb_incl)
-# rot_ = np.ones(nb_incl) * 0
-
-
[…]

### 2019-06-11 ferromtm/models/theo.py

@@ -5,107 +5,100 @@ import numpy as np
 from ferromtm import rootdir
 from ferromtm.models.bst import *
 
-epsilon0 = 8.8541878128e-12
-
-# fname = "drilled vs undrilled"
-fname = "/home/ben/Documents/projects/animate/results/theo/drilled bst/drilled vs undrilled simalr feild pe"
-f_ = np.loadtxt(fname)
-
-ind0 = 180
-ind1 = 311
-ind2 = 455
-ind3 = 601
-#
-# ind0 = 0
-# ind1 = 601
-
-# f = np.vstack((f_[ind0:ind1, :], np.flipud(f_[ind2:ind3, :])))
-# f = np.vstack((f_[ind0:ind1],(f_[ind2:ind3])))
-
-# f = f_[ind0:ind1, :]
-# f = np.flipud(f_[ind2:ind3, :])
-f = f_
-
-Eh = f[:, 0]
-Ph = f[:, 1]
-E = f[:, 2]
-P = f[:, 3]
-
-
-# ind0 = 460
-# ind1 = 601
-# #
-# # ind0 = 0
-# # ind1 = 601
-#
-# Eh = f[ind0:ind1,0]
-# Ph = f[ind0:ind1,1]
-# E = f[ind0:ind1,2]
-# P = f[ind0:ind1,3]
-#
-
-
-eps = np.gradient(P) / np.gradient(E) * 1e-6 / epsilon0
-eps0 = eps[300]
-eps = np.hstack((eps[ind0:ind1], np.flipud(eps[ind2:ind3])))
-E = np.hstack((E[ind0:ind1], np.flipud(E[ind2:ind3])))
-# eps0 = np.max(eps)
-# eps0 = eps[601-ind0]
-eps /= eps0
-epsh = np.gradient(Ph) / np.gradient(Eh) * 1e-6 / epsilon0
-epsh0 = epsh[300]
-epsh = np.hstack((epsh[ind0:ind1], np.flipud(epsh[ind2:ind3])))
-Eh = np.hstack((Eh[ind0:ind1], np.flipud(Eh[ind2:ind3])))
-epsh /= epsh0
-
-
-def fit(filename, fitname, par0=(1, 1)):
-    meas = np.load(os.path.join(rootdir, "data", filename))
-    E_exp = meas["E_exp"]
-    eps_norm_exp = meas["eps_norm_exp"]
-    eps_exp_0 = meas["eps_exp_0"]
-    fit_params = []
[…]

### 2019-06-11 ferromtm/visualization/plot_random_fibers.py

@@ -5,25 +5,29 @@ from ferromtm import rootdir
 import numpy as np
 import os
 
-frange = np.array([0.1, 0.2, 0.3, 0.4, 0.5])
-dirsave = os.path.join(rootdir, "data", "mat")
-plt.close("all")
-for f in frange:
-    name = "random_samples_f_" + "{0}.npz".format(f)
-    npzfile = np.load(os.path.join(dirsave, name))
-    sample = npzfile["sample"]
-    Npltx, Nplty = 3, 7
-    fig, axarr = plt.subplots(
-        Npltx, Nplty, figsize=(Nplty, Npltx), sharex=True, sharey=True
-    )
-    fig.subplots_adjust(hspace=0.1, wspace=0.1)
-    fig.suptitle(r"Random material samples, $f = $ " + str(f))
 
-    for i, ax in enumerate(axarr.ravel()):
-        ax.axis("off")
-        b = sample[i, :, :]
-        ax.imshow(b, cmap="Greens_r")
+if __name__ == "__main__":
+    frange = np.array([0.1, 0.2, 0.3, 0.4, 0.5])
+    dirsave = os.path.join(rootdir, "data", "mat")
+    plt.close("all")
+    for f in frange:
+        name = "random_samples_f_" + "{0}.npz".format(f)
+        npzfile = np.load(os.path.join(dirsave, name))
+        sample = npzfile["sample"]
+        Npltx, Nplty = 3, 7
+        fig, axarr = plt.subplots(
+            Npltx, Nplty, figsize=(Nplty, Npltx), sharex=True, sharey=True
+        )
+        fig.subplots_adjust(hspace=0.1, wspace=0.1)
+        fig.suptitle(r"Random material samples, $f = $ " + str(f))
 
-    figname = "random_samples_f_" + "{0}percent.eps".format(int(f * 100))
-    plt.savefig(os.path.join(rootdir, "data", "figures", figname), bbox_inches="tight")
-    plt.pause(0.1)
+        for i, ax in enumerate(axarr.ravel()):
+            ax.axis("off")
+            b = sample[i, :, :]
+            ax.imshow(b, cmap="Greens_r")
+
+        figname = "random_samples_f_" + "{0}percent.eps".format(int(f * 100))
+        plt.savefig(
+            os.path.join(rootdir, "data", "figures", figname), bbox_inches="tight"
+        )
+        plt.pause(0.1)

### 2019-06-28 paper/arxiv/response_letter.tex
optim GA ferro

@@
 \definecolor{correction}{HTML}{de5e5e}
-\definecolor{reply}{HTML}{249150}
+\definecolor{reply}{HTML}{de5e5e}
 \newcommand{\co}[1]{\textcolor{correction}{#1}}
-\newcommand{\rep}[1]{\textcolor{reply}{\textit{Reply:} #1}}
+\newcommand{\rep}[1]{\textcolor{reply}{{\bfseries Reply:} #1}}
 
@@
 
-\rep{It has been clarified in the abstract and introduction that this is a computational and numerical study.}
+\rep{It has been clarified in the abstract and introduction (lines 104-107) that this is a computational and numerical study.}
 
@@
  It is useful to know what materials this method can be used to model.
+
+\rep{Some example and references about commonly used ferroelectric composites have been
+added in the introduction (lines 32-40).}
 
@@
 
-    \rep{We have expanded on this point in the introduction and added possible applications of the model and corresponding references.}
+    \rep{We have expanded on this point in the introduction and added possible applications of the model and corresponding references (lines 67-73).}
 
@@
   expand on this point? What are the limitations?
+
+  \rep{In the end of the introduction (lines 89-103), we have expanded on this point by outlining the limitations of other methods and
+  the advantages of our approach in the context of this study.}
 
@@
 
-\rep{Details about the composition, fabrication and measurements of the samples at DC and microwave frequencies have been added at the beginning of Section II A.}
+\rep{Details about the composition, fabrication and measurements of the samples at DC and microwave frequencies have been added at the beginning of Section II A (from line 137).}
 
@@
 
- \rep{Reference to Gauss' law has been added before Eq. 3}
+ \rep{Reference to Gauss' law has been added before Eq. 3 (lines 173-174)}
 
@@
  \rep{The captions of Figure 3 and other plots have been updated with more details (we are plotting normalized values),
- and more precisions have been added in the main text (section III. A)}
+ and more precisions have been added in the main text (section III. A, lines 249-252)}
 
@@
    paper: Yes
-  \item Are the figures in the manuscript necessary adequate well presented and clearly labeled: Yes
+  \item Are the figures in the manuscript necessary adequate well presented and clearly labelled: Yes
   \item Is the reference list appropriate: Yes
@@
 
-    \rep{Details about the composition, fabrication and measurements of the samples at DC and microwave frequencies have been added at the beginning of Section II A.}
+    \rep{Details about the composition, fabrication and measurements of the samples at DC and microwave frequencies have been added at the beginning of Section II A  (from line 137).}
 
   \item You may compare the results of your simulations with the results of other studies.
+
+  \rep{We added comparison of our results with previously published studies in section III. A (lines 261-268).}
 

### 2019-06-28 paper/arxiv/submit_final/manuscript.tex
optim GA ferro

--- 2019-06-11 paper/arxiv/marked_manuscript.tex
@@
  reprint,%
-%author-year,%
-%author-numerical,%
-% Conference Proceedings
-linenumbers
 ]{revtex4-1}
@@
 
-\usepackage{xcolor}
-\definecolor{correction}{HTML}{de5e5e}
-\newcommand{\co}[1]{\textcolor{correction}{#1}}
+%
+% \usepackage{xcolor}
+% \definecolor{correction}{HTML}{de5e5e}
+\newcommand{\co}[1]{#1}
 
@@
 \title{\co{Enhanced tunability in ferroelectric composites through local field enhancement and the effect of disorder}}
-\author{Benjamin Vial and Yang Hao}
+\author{Benjamin Vial}
+\email{b.vial@qmul.ac.uk}
+\author{Yang Hao}
+\email{y.hao@qmul.ac.uk}
 
@@
 \affiliation{School of Engineering and Computer Science, Queen Mary, University of London, London, E1 4NS, United Kingdom}
+\date{\today}
 
@@
 convergence homogenization analysis to obtain the effective parameters at
-higher frequencies, instead of a capacitance-based model.
+higher frequencies, instead of a capacitance-based model \co{valid in the static regime.
+This is an important point, as contrarily to most homogenization procedures that are based on a
+quasi-static approximation, the two scale convergence method fixes the frequency and lets the characteristic
+size of the system (the periodicity of the composites) tend to zero \cite{guenneau_homogenization_2000}.
+This asymptotic analysis allows one to study the frequency dependence of the effective parameters.
+In addition, analytical models for the effective permittivity routinely employed in the literature
+such as Maxwell-Garnett or Bruggeman theories are limited to a few canonical shapes of the inclusions, and
+cannot handle arbitrary geometries and media with spatially varying properties. This last point is
+of particular importance in the context of this study since we have to account for the field induced local permittivity change.}\\
 \co{The model we developed has been implemented with the finite element method (FEM)
@@
  \label{table_params_fit}
+ \begin{ruledtabular}
  \begin{tabular}{llll}
+  case        & $\epsf(0)$ & $\alpha$ ($\rm \mu m^2/V^2$) & $\beta$ ($\rm \mu m^4/V^4$) \\
   \hline
-  case        & $\epsf(0)$ & $\alpha$ ($\rm \mu m^2/V^2$) & $\beta$ ($\rm \mu m^4/V^4$) \\ \hline
   static      & 3050       & 0.120                        & 0.024                       \\
-  $f=3.8$ GHz & 165        & 0.240                        & 0.079                       \\\hline
+  $f=3.8$ GHz & 165        & 0.240                        & 0.079                       \\
  \end{tabular}
+ \end{ruledtabular}
 \end{table}
@@
  \centering
- \includegraphics[width=0.75\textwidth]{effpar_rand_cpl.png}
+ \includegraphics[width=0.75\textwidth]{effpar_rand_cpl}
  \caption{Effective parameters of the pseudo-random composites as a function of the
@@
 and so it is envisioned that the performance of the composites might be enhanced by engineering
-their microstructure.
+their microstructure. \co{Those observations are consistent with previously published numerical and experimental results \cite{padurariu_tailoring_2012}
+ where the local field enhancement in porous ferroelectrics has been shown to possibly increase tunability with reducing permittivity for small porosity levels.
+Our appraoch also agrees with an analytical spherical inclusion model predicting an increase of the tunability with the dilution of the ferroelectric \cite{sherman_ferroelectric-dielectric_2006}.}\\
 The geometry of the unit cell is symmetric so the homogenized material is
@@
  \centering
- \includegraphics[width=0.8\textwidth]{effpar_rand_uncpl.png}
+ \includegraphics[width=0.8\textwidth]{effpar_rand_uncpl}
  \caption{Effective parameters of the random 2D mixtures as a function of the
@@
 % \bibliographystyle{RS}
-\bibliography{../biblio}
+\bibliography{biblio}
 

### 2019-06-28 ferromtm/models/coupled2D.py

@@ -119,7 +119,16 @@ def ref_mesh(fem):
     return fem
 
 
-def init_es(f, E_bias, incl=True, mat=None, parmesh=20, mesh_refine=True, tmp_dir=None):
+def init_es(
+    f,
+    E_bias,
+    incl=True,
+    mat=None,
+    parmesh=20,
+    mesh_refine=True,
+    tmp_dir=None,
+    quad=False,
+):
     r = (f / pi) ** (1 / 2)
     #####################################
     # # electrostatics
@@ -135,7 +144,7 @@ def init_es(f, E_bias, incl=True, mat=None, parmesh=20, mesh_refine=True, tmp_di
     fem_es.type_des = "elements"
     fem_es.inclusion_flag = incl
     # if not incl:
-    # fem_es.quad_mesh_flag=True
+    fem_es.quad_mesh_flag = quad
     fem_es.dx = 1
     fem_es.dy = 1
     fem_es.dz = 1
@@ -402,7 +411,6 @@ def main(
     id = np.ones(nvar)
     if incl:
         epsi = id * eps_f, id * eps_f0, id * eps_f0
-
     else:
         id = mat2des(fem_es)
         epsi_xx = np.ones_like(id, dtype=complex) * eps_incl

### 2019-06-28 ferromtm/models/optim.py

@@ -6,7 +6,7 @@ from pytheas.optim import TopOpt
 import tempfile
 from aotomat.tools.plottools import *
 
-# plt.close("all")
+plt.close("all")
 
 eps_interp = [1, 21]
 
@@ -38,12 +38,12 @@ def init_pattern():
 mat = init_pattern()
 mat.pattern = mat.normalized_pattern
 
-parmesh = 21
+parmesh = 4
 
 fem_es = init_es(0, 0, incl=False, mat=mat, parmesh=parmesh, mesh_refine=False)
+fem_es.rm_tmp_dir()
 
-
-debug = False
+debug = True
 if debug:
     fem_es.getdp_verbose = 4
     fem_es.gmsh_verbose = 4
@@ -51,9 +51,15 @@ if debug:
 
 
 fem_es.quad_mesh_flag = True
+# fem_es.ignore_periodicity = True
 # fem_es.gmsh_verbose = 4
 fem_hom = init_hom(fem_es, tmp_dir="./tmp/test0")
+
+#
 fem_hom.pola = "TM"
+# fem_hom.ignore_periodicity = True
+# fem_hom.make_mesh(other_option="-tol 1e-6")
+# fem_hom.initialize()
 
 # fem_hom.open_gmsh_gui()
 
@@ -106,6 +112,7 @@ def compute_hom_pb_y(fem_hom, epsi, verbose=False):
     # fem_hom.path_pos += " ./tmp/test0/source_adj.pos"
     # print(fem_hom.path_pos)
     fem_hom.compute_solution()
+
     fem_hom.postprocessing()
     V = fem_hom.get_vol()
     phi_yy = femio.load_table(fem_hom.tmppath("Phiyy.txt")) / V
@@ -144,7 +151,7 @@ def get_sensitivity(to, p, filt=True, proj=True, interp_method="cubic"):
     epsilon, depsilon_dp = to.make_epsilon(p, filt=filt, proj=proj, grad=True)
     deq_deps = get_deq_deps(to, interp_method=interp_method) * (-1 / epsilon ** 2)
     # deq_deps = to.get_deq_deps(interp_method=interp_method) * (-1 / epsilon ** 2)
-    deq_deps = 1
+    # deq_deps = 1
     sens = to.dg_dp + np.real(adjoint * deq_deps * depsilon_dp)
     # plt_field(depsilon_dp, title="depsilon_dp")
     # plt_field(adjoint, title="adjoint")
[…]

### 2019-06-28 ferromtm/models/optim_para.py

@@ -29,7 +29,7 @@ def init_pattern():
 mat = init_pattern()
 mat.pattern = mat.normalized_pattern
 
-parmesh = 21
+parmesh = 6
 
 fem_es = init_es(0, 0, incl=False, mat=mat, parmesh=parmesh, mesh_refine=False)
 
@@ -60,12 +60,12 @@ to.m = 1  # interpolation order eps=(eps_min-eps_max)*x^m-eps_min
 to.ptol_rel = 1.0e-10
 to.ftol_rel = 1.0e-5
 to.stopval = 1e-6
-to.maxeval = 3  # maximum of function evaluation
+to.maxeval = 22  # maximum of function evaluation
 to.Nitmax = 1  # maximum number of global iterations
 to.N0 = 0  # initial global iterations
 # to.beta = 1  # projection parameter
 lmin = 1
-to.rfilt = 0.0 * lmin  # filter radius
+to.rfilt = 0.05 * lmin  # filter radius
 to.filt_weight = "gaussian"
 to.dg_dp = 0
 to.eps_interp = eps_interp
@@ -254,6 +254,7 @@ def make_plots(to, p, filt=True, proj=True):
 
 
 def get_grad_fd(p0, para=False):
+    print("computing gradient with finite differences")
     f, _ = objectivefunc(p0)
     dp = 1e-6
     nvar = len(p0)
@@ -276,7 +277,7 @@ def get_grad_fd(p0, para=False):
 
 
 if __name__ == "__main__":
-    fd = False
+    fd = True
     partype = "gridmap"
     # partype = "multiprocessing"
     objectivefuncpara = parallel(objectivefunc, partype=partype)
@@ -286,7 +287,7 @@ if __name__ == "__main__":
     p0 = to.random_pattern(mat)
     print(len(p0))
 
-    # out = main_opt(p0, fd=fd)
+    out = main_opt(p0, fd=fd)
 
     # dasda
 

### 2019-09-27 paper/manuscript.tex
theo

--- 2019-06-28 paper/arxiv/submit_final/manuscript.tex
@@
 % \bibliographystyle{RS}
-\bibliography{biblio}
+% \bibliography{biblio}
+
+%merlin.mbs aipnum4-1.bst 2010-07-25 4.21a (PWD, AO, DPC) hacked
+%Control: key (0)
+%Control: author (8) initials jnrlst
+%Control: editor formatted (1) identically to author
+%Control: production of article title (0) allowed
+%Control: page (1) range
+%Control: year (1) truncated
+%Control: production of eprint (0) enabled
+\begin{thebibliography}{36}%
+\makeatletter
+\providecommand \@ifxundefined [1]{%
+ \@ifx{#1\undefined}
+}%
+\providecommand \@ifnum [1]{%
+ \ifnum #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \@ifx [1]{%
+ \ifx #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \natexlab [1]{#1}%
+\providecommand \enquote  [1]{``#1''}%
+\providecommand \bibnamefont  [1]{#1}%
+\providecommand \bibfnamefont [1]{#1}%
+\providecommand \citenamefont [1]{#1}%
+\providecommand \href@noop [0]{\@secondoftwo}%
+\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
+\providecommand \@href[1]{\@@startlink{#1}\@@href}%
+\providecommand \@@href[1]{\endgroup#1\@@endlink}%
+\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
+  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
+\providecommand \@@startlink[1]{}%
+\providecommand \@@endlink[0]{}%
+\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
+\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
+\providecommand \urlprefix  [0]{URL }%
+\providecommand \Eprint [0]{\href }%
+\providecommand \doibase [0]{http://dx.doi.org/}%
+\providecommand \selectlanguage [0]{\@gobble}%
+\providecommand \bibinfo  [0]{\@secondoftwo}%
+\providecommand \bibfield  [0]{\@secondoftwo}%
+\providecommand \translation [1]{[#1]}%
+\providecommand \BibitemOpen [0]{}%
+\providecommand \bibitemStop [0]{}%
+\providecommand \bibitemNoStop [0]{.\EOS\space}%
+\providecommand \EOS [0]{\spacefactor3000\relax}%
+\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
+\let\auto@bib@innerbib\@empty
+%</preamble>
+\bibitem [{\citenamefont {Tagantsev}\ \emph {et~al.}(2018)\citenamefont
+  {Tagantsev}, \citenamefont {Sherman}, \citenamefont {Astafiev}, \citenamefont
+  {Venkatesh},\ and\ \citenamefont {Setter}}]{tagantsev_ferroelectric_2018}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~K.}\ \bibnamefont
+  {Tagantsev}}, \bibinfo {author} {\bibfnamefont {V.~O.}\ \bibnamefont
+  {Sherman}}, \bibinfo {author} {\bibfnamefont {K.~F.}\ \bibnamefont
+  {Astafiev}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Venkatesh}},
+  \ and\ \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Setter}},\
+  }\bibfield  {title} {\enquote {\bibinfo {title} {Ferroelectric {Materials}
+  for {Microwave} {Tunable} {Applications}},}\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {J Electroceram}\ }\textbf {\bibinfo {volume}
+  {11}},\ \bibinfo {pages} {5--66} (\bibinfo {year} {2018})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Vendik}\ \emph {et~al.}(1999)\citenamefont {Vendik},
+  \citenamefont {Hollmann}, \citenamefont {Kozyrev},\ and\ \citenamefont
+  {Prudan}}]{vendik_ferroelectric_1999}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {O.}~\bibnamefont
+  {Vendik}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Hollmann}},
+  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Kozyrev}}, \ and\
+  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Prudan}},\ }\bibfield
+  {title} {\enquote {\bibinfo {title} {Ferroelectric tuning of planar and bulk
+  microwave devices},}\ }\href@noop {} {\bibfield  {journal} {\bibinfo
+  {journal} {J. Supercond.}\ }\textbf {\bibinfo {volume} {12}},\ \bibinfo
+  {pages} {325--338} (\bibinfo {year} {1999})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Lancaster}, \citenamefont {Powell},\ and\
+  \citenamefont {Porch}(1998)}]{lancaster_thin-film_1998}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Lancaster}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Powell}}, \
+  and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Porch}},\ }\bibfield
+   {title} {\enquote {\bibinfo {title} {Thin-film ferroelectric microwave
+  devices},}\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Supercond. Sci. Technol.}\ }\textbf {\bibinfo {volume} {11}},\ \bibinfo
+  {pages} {1323} (\bibinfo {year} {1998})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Xi}\ \emph {et~al.}(2000)\citenamefont {Xi},
+  \citenamefont {Li}, \citenamefont {Si}, \citenamefont {Sirenko},
+  \citenamefont {Akimov}, \citenamefont {Fox}, \citenamefont {Clark},\ and\
+  \citenamefont {Hao}}]{xi_oxide_2000}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {X.}~\bibnamefont
+  {Xi}}, \bibinfo {author} {\bibfnamefont {H.-C.}\ \bibnamefont {Li}}, \bibinfo
+  {author} {\bibfnamefont {W.}~\bibnamefont {Si}}, \bibinfo {author}
+  {\bibfnamefont {A.}~\bibnamefont {Sirenko}}, \bibinfo {author} {\bibfnamefont
+  {I.}~\bibnamefont {Akimov}}, \bibinfo {author} {\bibfnamefont
+  {J.}~\bibnamefont {Fox}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Clark}}, \ and\ \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Hao}},\
+  }\bibfield  {title} {\enquote {\bibinfo {title} {Oxide thin films for tunable
+  microwave devices},}\ }\href@noop {} {\bibfield  {journal} {\bibinfo
+  {journal} {J. Electroceramics}\ }\textbf {\bibinfo {volume} {4}},\ \bibinfo
+  {pages} {393--405} (\bibinfo {year} {2000})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Hand}\ and\ \citenamefont
+  {Cummer}(2008)}]{hand_frequency_2008}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.~H.}\ \bibnamefont
+  {Hand}}\ and\ \bibinfo {author} {\bibfnamefont {S.~A.}\ \bibnamefont
+  {Cummer}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Frequency
+  tunable electromagnetic metamaterial using ferroelectric loaded split
+  rings},}\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {J. Appl.
+  Phys.}\ }\textbf {\bibinfo {volume} {103}},\ \bibinfo {pages} {066105}
+  (\bibinfo {year} {2008})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Zhao}\ \emph {et~al.}(2008)\citenamefont {Zhao},
+  \citenamefont {Kang}, \citenamefont {Zhou}, \citenamefont {Zhao},
+  \citenamefont {Li}, \citenamefont {Peng},\ and\ \citenamefont
+  {Bai}}]{zhao_experimental_2008}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+  {Zhao}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Kang}}, \bibinfo
+  {author} {\bibfnamefont {J.}~\bibnamefont {Zhou}}, \bibinfo {author}
+  {\bibfnamefont {Q.}~\bibnamefont {Zhao}}, \bibinfo {author} {\bibfnamefont
+  {L.}~\bibnamefont {Li}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Peng}}, \ and\ \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Bai}},\
+  }\bibfield  {title} {\enquote {\bibinfo {title} {Experimental demonstration
+  of tunable negative phase velocity and negative refraction in a
+  ferromagnetic/ferroelectric composite metamaterial},}\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {Appl. Phys. Lett.}\ }\textbf
+  {\bibinfo {volume} {93}},\ \bibinfo {pages} {201106} (\bibinfo {year}
+  {2008})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Irvin}\ \emph {et~al.}(2005)\citenamefont {Irvin},
+  \citenamefont {Levy}, \citenamefont {Guo},\ and\ \citenamefont
+  {Bhalla}}]{irvin_three-dimensional_2005}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+  {Irvin}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Levy}},
+  \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Guo}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {A.}~\bibnamefont {Bhalla}},\ }\bibfield  {title}
+  {\enquote {\bibinfo {title} {Three-dimensional polarization imaging of
+  ({Ba},{Sr}){TiO}3:{MgO} composites},}\ }\href {\doibase 10.1063/1.1854722}
+  {\bibfield  {journal} {\bibinfo  {journal} {Appl. Phys. Lett.}\ }\textbf
+  {\bibinfo {volume} {86}},\ \bibinfo {pages} {042903} (\bibinfo {year}
+  {2005})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Chung}\ \emph {et~al.}(2008)\citenamefont {Chung},
+  \citenamefont {Elissalde}, \citenamefont {Maglione}, \citenamefont
+  {Estournès}, \citenamefont {Paté},\ and\ \citenamefont
+  {Ganne}}]{chung_low-losses_2008}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {U.-C.}\ \bibnamefont
+  {Chung}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Elissalde}},
+  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Maglione}}, \bibinfo
+  {author} {\bibfnamefont {C.}~\bibnamefont {Estournès}}, \bibinfo {author}
+  {\bibfnamefont {M.}~\bibnamefont {Paté}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {J.~P.}\ \bibnamefont {Ganne}},\ }\bibfield  {title} {\enquote
+  {\bibinfo {title} {Low-losses, highly tunable {Ba}0.6sr0.4tio3 / {MgO}
+  composite},}\ }\href {\doibase 10.1063/1.2837621} {\bibfield  {journal}
+  {\bibinfo  {journal} {Appl. Phys. Lett.}\ }\textbf {\bibinfo {volume} {92}},\
+  \bibinfo {pages} {042902} (\bibinfo {year} {2008})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Wang}\ \emph {et~al.}(2012)\citenamefont {Wang},
+  \citenamefont {Luo}, \citenamefont {Ni}, \citenamefont {Du}, \citenamefont
+  {Li},\ and\ \citenamefont {Chen}}]{wang_piezoelectric_2012}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
+  {Wang}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Luo}}, \bibinfo
+  {author} {\bibfnamefont {F.}~\bibnamefont {Ni}}, \bibinfo {author}
+  {\bibfnamefont {P.}~\bibnamefont {Du}}, \bibinfo {author} {\bibfnamefont
+  {W.}~\bibnamefont {Li}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {H.}~\bibnamefont {Chen}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {Piezoelectric and ferroelectric properties of ({Bi}1- {xNa}0. 8k0. 2lax) 0.5
+  {TiO}3 lead-free ceramics},}\ }\href {\doibase 10.1016/j.jallcom.2012.02.114}
+  {\bibfield  {journal} {\bibinfo  {journal} {Journal of Alloys and Compounds}\
+  }\textbf {\bibinfo {volume} {526}},\ \bibinfo {pages} {79--84} (\bibinfo
+  {year} {2012})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Li}\ \emph {et~al.}(2013)\citenamefont {Li},
+  \citenamefont {Lim}, \citenamefont {Yao}, \citenamefont {Tay},\ and\
+  \citenamefont {Seah}}]{li_ferroelectric_2013}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {X.}~\bibnamefont
+  {Li}}, \bibinfo {author} {\bibfnamefont {Y.-F.}\ \bibnamefont {Lim}},
+  \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Yao}}, \bibinfo {author}
+  {\bibfnamefont {F.~E.~H.}\ \bibnamefont {Tay}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {K.~H.}\ \bibnamefont {Seah}},\ }\bibfield  {title} {\enquote
+  {\bibinfo {title} {Ferroelectric {Poly}(vinylidene fluoride) {Homopolymer}
+  {Nanotubes} {Derived} from {Solution} in {Anodic} {Alumina} {Membrane}
+  {Template}},}\ }\href {\doibase 10.1021/cm3028466} {\bibfield  {journal}
+  {\bibinfo  {journal} {Chem. Mater.}\ }\textbf {\bibinfo {volume} {25}},\
+  \bibinfo {pages} {524--529} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Hu}\ \emph {et~al.}(2015)\citenamefont {Hu},
+  \citenamefont {Gao}, \citenamefont {Kong}, \citenamefont {Yang},
+  \citenamefont {Zhang}, \citenamefont {Liu}, \citenamefont {Zhang},\ and\
+  \citenamefont {Sun}}]{hu_preparation_2015}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+  {Hu}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Gao}}, \bibinfo
+  {author} {\bibfnamefont {J.}~\bibnamefont {Kong}}, \bibinfo {author}
+  {\bibfnamefont {S.}~\bibnamefont {Yang}}, \bibinfo {author} {\bibfnamefont
+  {Q.}~\bibnamefont {Zhang}}, \bibinfo {author} {\bibfnamefont
+  {Z.}~\bibnamefont {Liu}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
+  {Zhang}}, \ and\ \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Sun}},\
+  }\bibfield  {title} {\enquote {\bibinfo {title} {Preparation and dielectric
+  properties of poly(vinylidene fluoride)/{Ba}0.6sr0.4tio3 composites},}\
+  }\href {\doibase 10.1016/j.jallcom.2014.09.005} {\bibfield  {journal}
+  {\bibinfo  {journal} {Journal of Alloys and Compounds}\ }\textbf {\bibinfo
+  {volume} {619}},\ \bibinfo {pages} {686--692} (\bibinfo {year}
+  {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Sherman}\ \emph {et~al.}(2006)\citenamefont
+  {Sherman}, \citenamefont {Tagantsev}, \citenamefont {Setter}, \citenamefont
+  {Iddles},\ and\ \citenamefont
+  {Price}}]{sherman_ferroelectric-dielectric_2006}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {V.~O.}\ \bibnamefont
+  {Sherman}}, \bibinfo {author} {\bibfnamefont {A.~K.}\ \bibnamefont
+  {Tagantsev}}, \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Setter}},
+  \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Iddles}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {T.}~\bibnamefont {Price}},\ }\bibfield  {title}
+  {\enquote {\bibinfo {title} {Ferroelectric-dielectric tunable composites},}\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {J. Appl. Phys.}\
+  }\textbf {\bibinfo {volume} {99}},\ \bibinfo {pages} {074104} (\bibinfo
+  {year} {2006})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Jylha}\ and\ \citenamefont
+  {Sihvola}(2008)}]{jylha_tunability_2008}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Jylha}}\ and\ \bibinfo {author} {\bibfnamefont {A.~H.}\ \bibnamefont
+  {Sihvola}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Tunability of
+  granular ferroelectric dielectric composites},}\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Prog. Electromagn. Res.}\ }\textbf {\bibinfo
+  {volume} {78}},\ \bibinfo {pages} {189--207} (\bibinfo {year}
+  {2008})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Sherman}, \citenamefont {Tagantsev},\ and\
+  \citenamefont {Setter}(2004)}]{sherman_tunability_2004}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {V.~O.}\ \bibnamefont
+  {Sherman}}, \bibinfo {author} {\bibfnamefont {A.~K.}\ \bibnamefont
+  {Tagantsev}}, \ and\ \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
+  {Setter}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Tunability and
+  loss of the ferroelectric-dielectric composites},}\ }in\ \href@noop {} {\emph
+  {\bibinfo {booktitle} {14th {IEEE} {International} {Symposium} on
+  {Applications} of {Ferroelectrics}, 2004. {ISAF}-04. 2004}}}\ (\bibinfo
+  {year} {2004})\ pp.\ \bibinfo {pages} {33--38}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Astafiev}\ \emph {et~al.}(2003)\citenamefont
+  {Astafiev}, \citenamefont {Sherman}, \citenamefont {Tagantsev},\ and\
+  \citenamefont {Setter}}]{astafiev_can_2003}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.~F.}\ \bibnamefont
+  {Astafiev}}, \bibinfo {author} {\bibfnamefont {V.~O.}\ \bibnamefont
+  {Sherman}}, \bibinfo {author} {\bibfnamefont {A.~K.}\ \bibnamefont
+  {Tagantsev}}, \ and\ \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
+  {Setter}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Can the addition
+  of a dielectric improve the figure of merit of a tunable material?}}\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {J. Eur. Ceram.
+  Soc.}\ }\textbf {\bibinfo {volume} {23}},\ \bibinfo {pages} {2381 -- 2386}
+  (\bibinfo {year} {2003})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Okazaki}\ and\ \citenamefont
+  {Nagata}(1973)}]{okazaki_effects_1973}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
+  {Okazaki}}\ and\ \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
+  {Nagata}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Effects of
+  {Grain} {Size} and {Porosity} on {Electrical} and {Optical} {Properties} of
+  {PLZT} {Ceramics}},}\ }\href {\doibase 10.1111/j.1151-2916.1973.tb12363.x}
+  {\bibfield  {journal} {\bibinfo  {journal} {J. Am. Ceram. Soc.}\ }\textbf
+  {\bibinfo {volume} {56}},\ \bibinfo {pages} {82--86} (\bibinfo {year}
+  {1973})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Stanculescu}\ \emph {et~al.}(2015)\citenamefont
+  {Stanculescu}, \citenamefont {Ciomaga}, \citenamefont {Padurariu},
+  \citenamefont {Galizia}, \citenamefont {Horchidan}, \citenamefont {Capiani},
+  \citenamefont {Galassi},\ and\ \citenamefont
+  {Mitoseriu}}]{stanculescu_study_2015}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
+  {Stanculescu}}, \bibinfo {author} {\bibfnamefont {C.~E.}\ \bibnamefont
+  {Ciomaga}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Padurariu}},
+  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Galizia}}, \bibinfo
+  {author} {\bibfnamefont {N.}~\bibnamefont {Horchidan}}, \bibinfo {author}
+  {\bibfnamefont {C.}~\bibnamefont {Capiani}}, \bibinfo {author} {\bibfnamefont
+  {C.}~\bibnamefont {Galassi}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {L.}~\bibnamefont {Mitoseriu}},\ }\bibfield  {title} {\enquote {\bibinfo
+  {title} {Study of the role of porosity on the functional properties of
+  ({Ba},{Sr}){TiO}3 ceramics},}\ }\href {\doibase
+  10.1016/j.jallcom.2015.03.252} {\bibfield  {journal} {\bibinfo  {journal} {J.
+  Alloys Compd.}\ }\textbf {\bibinfo {volume} {643}},\ \bibinfo {pages}
+  {79--87} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Padurariu}\ \emph
+  {et~al.}(2012{\natexlab{a}})\citenamefont {Padurariu}, \citenamefont
+  {Curecheriu}, \citenamefont {Galassi},\ and\ \citenamefont
+  {Mitoseriu}}]{padurariu_tailoring_2012}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Padurariu}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Curecheriu}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Galassi}},
+  \ and\ \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Mitoseriu}},\
+  }\bibfield  {title} {\enquote {\bibinfo {title} {Tailoring non-linear
+  dielectric properties by local field engineering in anisotropic porous
+  ferroelectric structures},}\ }\href {\doibase 10.1063/1.4729878} {\bibfield
+  {journal} {\bibinfo  {journal} {Appl Phys Lett}\ }\textbf {\bibinfo {volume}
+  {100}},\ \bibinfo {pages} {252905} (\bibinfo {year}
+  {2012}{\natexlab{a}})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Padurariu}\ \emph
+  {et~al.}(2012{\natexlab{b}})\citenamefont {Padurariu}, \citenamefont
+  {Curecheriu}, \citenamefont {Buscaglia},\ and\ \citenamefont
+  {Mitoseriu}}]{padurariu_field-dependent_2012}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Padurariu}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Curecheriu}}, \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont
+  {Buscaglia}}, \ and\ \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Mitoseriu}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {Field-dependent permittivity in nanostructured {BaTiO}\$\{\}\_\{3\}\$
+  ceramics: {Modeling} and experimental verification},}\ }\href {\doibase
+  10.1103/PhysRevB.85.224111} {\bibfield  {journal} {\bibinfo  {journal} {Phys
+  Rev B}\ }\textbf {\bibinfo {volume} {85}},\ \bibinfo {pages} {224111}
+  (\bibinfo {year} {2012}{\natexlab{b}})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Cazacu}\ \emph {et~al.}(2013)\citenamefont {Cazacu},
+  \citenamefont {Curecheriu}, \citenamefont {Neagu}, \citenamefont {Padurariu},
+  \citenamefont {Cernescu}, \citenamefont {Lisiecki},\ and\ \citenamefont
+  {Mitoseriu}}]{cazacu_tunable_2013}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Cazacu}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Curecheriu}},
+  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Neagu}}, \bibinfo
+  {author} {\bibfnamefont {L.}~\bibnamefont {Padurariu}}, \bibinfo {author}
+  {\bibfnamefont {A.}~\bibnamefont {Cernescu}}, \bibinfo {author}
+  {\bibfnamefont {I.}~\bibnamefont {Lisiecki}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {L.}~\bibnamefont {Mitoseriu}},\ }\bibfield  {title} {\enquote
+  {\bibinfo {title} {Tunable gold-chitosan nanocomposites by local field
+  engineering},}\ }\href {\doibase 10.1063/1.4809673} {\bibfield  {journal}
+  {\bibinfo  {journal} {Appl Phys Lett}\ }\textbf {\bibinfo {volume} {102}},\
+  \bibinfo {pages} {222903} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Carignan}\ \emph {et~al.}(2011)\citenamefont
+  {Carignan}, \citenamefont {Yelon}, \citenamefont {Menard},\ and\
+  \citenamefont {Caloz}}]{carignan_ferromagnetic_2011}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Carignan}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Yelon}},
+  \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Menard}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {C.}~\bibnamefont {Caloz}},\ }\bibfield  {title}
+  {\enquote {\bibinfo {title} {Ferromagnetic {Nanowire} {Metamaterials}:
+  {Theory} and {Applications}},}\ }\href {\doibase 10.1109/TMTT.2011.2163202}
+  {\bibfield  {journal} {\bibinfo  {journal} {IEEE Trans. Microw. Theory
+  Tech.}\ }\textbf {\bibinfo {volume} {59}},\ \bibinfo {pages} {2568--2586}
+  (\bibinfo {year} {2011})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Werner}\ \emph {et~al.}(2007)\citenamefont {Werner},
+  \citenamefont {Kwon}, \citenamefont {Khoo}, \citenamefont {Kildishev},\ and\
+  \citenamefont {Shalaev}}]{werner_liquid_2007}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~H.}\ \bibnamefont
+  {Werner}}, \bibinfo {author} {\bibfnamefont {D.-H.}\ \bibnamefont {Kwon}},
+  \bibinfo {author} {\bibfnamefont {I.-C.}\ \bibnamefont {Khoo}}, \bibinfo
+  {author} {\bibfnamefont {A.~V.}\ \bibnamefont {Kildishev}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {V.~M.}\ \bibnamefont {Shalaev}},\ }\bibfield
+  {title} {\enquote {\bibinfo {title} {Liquid crystal clad near-infrared
+  metamaterials with tunable negative-zero-positive refractive indices},}\
+  }\href {\doibase 10.1364/OE.15.003342} {\bibfield  {journal} {\bibinfo
+  {journal} {Opt. Express, OE}\ }\textbf {\bibinfo {volume} {15}},\ \bibinfo
+  {pages} {3342--3347} (\bibinfo {year} {2007})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Keiser}\ and\ \citenamefont
+  {Klarskov}(2019)}]{keiser_terahertz_2019}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.~R.}\ \bibnamefont
+  {Keiser}}\ and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+  {Klarskov}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Terahertz
+  {Field} {Confinement} in {Nonlinear} {Metamaterials} and {Near}-{Field}
+  {Imaging}},}\ }\href {\doibase 10.3390/photonics6010022} {\bibfield
+  {journal} {\bibinfo  {journal} {Photonics}\ }\textbf {\bibinfo {volume}
+  {6}},\ \bibinfo {pages} {22} (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Fan}\ \emph {et~al.}(2013)\citenamefont {Fan},
+  \citenamefont {Hwang}, \citenamefont {Liu}, \citenamefont {Strikwerda},
+  \citenamefont {Sternbach}, \citenamefont {Zhang}, \citenamefont {Zhao},
+  \citenamefont {Zhang}, \citenamefont {Nelson},\ and\ \citenamefont
+  {Averitt}}]{fan_nonlinear_2013}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
+  {Fan}}, \bibinfo {author} {\bibfnamefont {H.~Y.}\ \bibnamefont {Hwang}},
+  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Liu}}, \bibinfo {author}
+  {\bibfnamefont {A.~C.}\ \bibnamefont {Strikwerda}}, \bibinfo {author}
+  {\bibfnamefont {A.}~\bibnamefont {Sternbach}}, \bibinfo {author}
+  {\bibfnamefont {J.}~\bibnamefont {Zhang}}, \bibinfo {author} {\bibfnamefont
+  {X.}~\bibnamefont {Zhao}}, \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont
+  {Zhang}}, \bibinfo {author} {\bibfnamefont {K.~A.}\ \bibnamefont {Nelson}}, \
+  and\ \bibinfo {author} {\bibfnamefont {R.~D.}\ \bibnamefont {Averitt}},\
+  }\bibfield  {title} {\enquote {\bibinfo {title} {Nonlinear {Terahertz}
+  {Metamaterials} via {Field}-{Enhanced} {Carrier} {Dynamics} in {GaAs}},}\
+  }\href {\doibase 10.1103/PhysRevLett.110.217404} {\bibfield  {journal}
+  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {110}},\
+  \bibinfo {pages} {217404} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Allaire}(1992)}]{allaire_homogenization_1992}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+  {Allaire}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Homogenization
+  and {Two}-{Scale} {Convergence}},}\ }\href@noop {} {\bibfield  {journal}
+  {\bibinfo  {journal} {SIAM J. Math. Anal.}\ }\textbf {\bibinfo {volume}
+  {23}},\ \bibinfo {pages} {1482--1518} (\bibinfo {year} {1992})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Guenneau}\ and\ \citenamefont
+  {Zolla}(2000)}]{guenneau_homogenization_2000}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Guenneau}}\ and\ \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
+  {Zolla}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Homogenization of
+  {Three}-{Dimensional} {Finite} {Photonic} {Crystals}},}\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {J. Electromagn. Waves Appl.}\
+  }\textbf {\bibinfo {volume} {14}},\ \bibinfo {pages} {529--530} (\bibinfo
+  {year} {2000})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Agrawal}\ \emph {et~al.}(2004)\citenamefont
+  {Agrawal}, \citenamefont {Guo}, \citenamefont {Agrawal},\ and\ \citenamefont
+  {Bhalla}}]{agrawal_tunable_2004}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Agrawal}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Guo}},
+  \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Agrawal}}, \ and\
+  \bibinfo {author} {\bibfnamefont {A.~S.}\ \bibnamefont {Bhalla}},\ }\bibfield
+   {title} {\enquote {\bibinfo {title} {Tunable {BST}:{MgO} {Dielectric}
+  {Composite} by {Microwave} {Sintering}},}\ }\href {\doibase
+  10.1080/00150190490460803} {\bibfield  {journal} {\bibinfo  {journal}
+  {Ferroelectrics}\ }\textbf {\bibinfo {volume} {306}},\ \bibinfo {pages}
+  {155--163} (\bibinfo {year} {2004})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Ansari}, \citenamefont {Jha},\ and\ \citenamefont
+  {Akhtar}(2015)}]{ansari_design_2015}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~A.~H.}\
+  \bibnamefont {Ansari}}, \bibinfo {author} {\bibfnamefont {A.~K.}\
+  \bibnamefont {Jha}}, \ and\ \bibinfo {author} {\bibfnamefont {M.~J.}\
+  \bibnamefont {Akhtar}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {Design and {Application} of the {CSRR}-{Based} {Planar} {Sensor} for
+  {Noninvasive} {Measurement} of {Complex} {Permittivity}},}\ }\href {\doibase
+  10.1109/JSEN.2015.2469683} {\bibfield  {journal} {\bibinfo  {journal} {IEEE
+  Sens. J.}\ }\textbf {\bibinfo {volume} {15}},\ \bibinfo {pages} {7181--7189}
+  (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Landau}\ \emph {et~al.}(2013)\citenamefont {Landau},
+  \citenamefont {Bell}, \citenamefont {Kearsley}, \citenamefont {Pitaevskii},
+  \citenamefont {Lifshitz},\ and\ \citenamefont
+  {Sykes}}]{landau_electrodynamics_2013}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.~D.}\ \bibnamefont
+  {Landau}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Bell}},
+  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Kearsley}}, \bibinfo
+  {author} {\bibfnamefont {L.}~\bibnamefont {Pitaevskii}}, \bibinfo {author}
+  {\bibfnamefont {E.}~\bibnamefont {Lifshitz}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {J.}~\bibnamefont {Sykes}},\ }\href@noop {} {\emph {\bibinfo
+  {title} {Electrodynamics of continuous media}}},\ Vol.~\bibinfo {volume} {8}\
+  (\bibinfo  {publisher} {elsevier},\ \bibinfo {year} {2013})\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Zhou}\ \emph {et~al.}(2008)\citenamefont {Zhou},
+  \citenamefont {Boggs}, \citenamefont {Ramprasad}, \citenamefont {Aindow},
+  \citenamefont {Erkey},\ and\ \citenamefont {Alpay}}]{zhou_dielectric_2008}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
+  {Zhou}}, \bibinfo {author} {\bibfnamefont {S.~A.}\ \bibnamefont {Boggs}},
+  \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Ramprasad}}, \bibinfo
+  {author} {\bibfnamefont {M.}~\bibnamefont {Aindow}}, \bibinfo {author}
+  {\bibfnamefont {C.}~\bibnamefont {Erkey}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {S.~P.}\ \bibnamefont {Alpay}},\ }\bibfield  {title} {\enquote
+  {\bibinfo {title} {Dielectric response and tunability of a
+  dielectric-paraelectric composite},}\ }\href@noop {} {\bibfield  {journal}
+  {\bibinfo  {journal} {Appl. Phys. Lett.}\ }\textbf {\bibinfo {volume} {93}},\
+  \bibinfo {pages} {102908} (\bibinfo {year} {2008})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Krowne}\ \emph {et~al.}(2002)\citenamefont {Krowne},
+  \citenamefont {Daniel}, \citenamefont {Kirchoefer},\ and\ \citenamefont
+  {Pond}}]{krowne_anisotropic_2002}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~M.}\ \bibnamefont
+  {Krowne}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Daniel}},
+  \bibinfo {author} {\bibfnamefont {S.~W.}\ \bibnamefont {Kirchoefer}}, \ and\
+  \bibinfo {author} {\bibfnamefont {J.~A.}\ \bibnamefont {Pond}},\ }\bibfield
+  {title} {\enquote {\bibinfo {title} {Anisotropic permittivity and attenuation
+  extraction from propagation constant measurements using an anisotropic
+  full-wave {Green}'s function solver for coplanar ferroelectric thin-film
+  devices},}\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {IEEE
+  Trans. Microw. Theory Tech.}\ }\textbf {\bibinfo {volume} {50}},\ \bibinfo
+  {pages} {537--548} (\bibinfo {year} {2002})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Geuzaine}\ and\ \citenamefont
+  {Remacle}(2009)}]{geuzaine_gmsh_2009}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+  {Geuzaine}}\ and\ \bibinfo {author} {\bibfnamefont {J.-F.}\ \bibnamefont
+  {Remacle}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Gmsh: {A} 3-{D}
+  finite element mesh generator with built-in pre- and post-processing
+  facilities},}\ }\href {\doibase 10.1002/nme.2579} {\bibfield  {journal}
+  {\bibinfo  {journal} {Int. J. Numer. Methods Eng.}\ }\textbf {\bibinfo
+  {volume} {79}},\ \bibinfo {pages} {1309--1331} (\bibinfo {year}
+  {2009})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Dular}\ \emph {et~al.}(1998)\citenamefont {Dular},
+  \citenamefont {Geuzaine}, \citenamefont {Henrotte},\ and\ \citenamefont
+  {Legros}}]{dular_general_1998}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+  {Dular}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Geuzaine}},
+  \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Henrotte}}, \ and\
+  \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Legros}},\ }\bibfield
+  {title} {\enquote {\bibinfo {title} {A general environment for the treatment
+  of discrete problems and its application to the finite element method},}\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {IEEE Trans.
+  Magn.}\ }\textbf {\bibinfo {volume} {34}},\ \bibinfo {pages} {3395--3398}
+  (\bibinfo {year} {1998})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Amestoy}\ \emph {et~al.}(2001)\citenamefont
+  {Amestoy}, \citenamefont {Duff}, \citenamefont {Koster},\ and\ \citenamefont
+  {L'Excellent}}]{amestoy_fully_2001}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~R.}\ \bibnamefont
+  {Amestoy}}, \bibinfo {author} {\bibfnamefont {I.~S.}\ \bibnamefont {Duff}},
+  \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Koster}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {J.-Y.}\ \bibnamefont {L'Excellent}},\ }\bibfield
+  {title} {\enquote {\bibinfo {title} {A {Fully} {Asynchronous} {Multifrontal}
+  {Solver} {Using} {Distributed} {Dynamic} {Scheduling}},}\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {SIAM J. Matrix Anal. Appl.}\
+  }\textbf {\bibinfo {volume} {23}},\ \bibinfo {pages} {15--41} (\bibinfo
+  {year} {2001})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bouchitté}\ and\ \citenamefont
+  {Felbacq}(2004)}]{bouchitte_homogenization_2004}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+  {Bouchitté}}\ and\ \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+  {Felbacq}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Homogenization
+  near resonances and artificial magnetism from dielectrics},}\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {Comptes Rendus Mathématique}\
+  }\textbf {\bibinfo {volume} {339}},\ \bibinfo {pages} {377 -- 382} (\bibinfo
+  {year} {2004})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Cherednichenko}\ and\ \citenamefont
+  {Cooper}(2015)}]{cherednichenko_homogenization_2015}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
+  {Cherednichenko}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Cooper}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Homogenization
+  of the system of high-contrast {Maxwell} equations},}\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {Mathematika}\ }\textbf {\bibinfo
+  {volume} {61}},\ \bibinfo {pages} {475--500} (\bibinfo {year}
+  {2015})}\BibitemShut {NoStop}%
+\end{thebibliography}%
 

### 2019-09-27 ferromtm/models/electrostatics/nonper2D/femmodel.py

@@ -99,9 +99,9 @@ class FemModel(BaseFEM):
             argstr=argstr,
         )
 
-    def postpro_fields(self, filetype="txt"):
-        self.print_progress("Postprocessing fields")
-        self.postpro_choice("postop_fields", filetype)
+    # def postpro_fields(self, filetype="txt"):
+    #     self.print_progress("Postprocessing fields")
+    #     self.postpro_choice("postop_fields", filetype)
 
     def postpro_electrostatic_field(self):
         self.print_progress("Postprocessing electrostatic field")
@@ -119,7 +119,3 @@ class FemModel(BaseFEM):
         E = femio.load_table_vect(self.tmp_dir + "/" + "int_Efield.txt")
         P = femio.load_table_vect(self.tmp_dir + "/" + "int_polarization.txt")
         return np.array(E), np.array(P)
-
-
-if __name__ == "__main__":
-    print("This is the femmodel module")

### 2019-09-27 ferromtm/models/nonper.py

@@ -14,6 +14,7 @@ from ferromtm.tools.utils import *
 from ferromtm.models.theo import *
 
 from pytheas.homogenization import *
+from theo import *
 
 if __name__ == "__main__":
 
@@ -27,7 +28,6 @@ if __name__ == "__main__":
 
     fem.parmesh = 11
     fem.parmesh_des = 11
-
     fem.parmesh_incl = 11
 
     fem.E_static = 1
@@ -49,15 +49,16 @@ if __name__ == "__main__":
 
     fem.inclusion_flag = True
 
-    dx, dy = 1.6, 1.6
+    r = 0.5 * 1.3
+    dholes = 0.6
+
+    dx, dy = 2 * r + dholes, 2 * r + dholes
     nb_inclx, nb_incly = 2, 3
 
     fem.hx_des = nb_inclx * dx
     fem.hy_des = nb_incly * dy
     nb_incl = nb_inclx * nb_incly
     fem.nb_incl = nb_incl
-
-    r = 0.5 * 1.1
 
     # Rx = (0.1 + np.random.random(nb_incl) * 0.3) * dx
     # Ry = (0.1 + np.random.random(nb_incl) * 0.3) * dy
@@ -81,6 +82,8 @@ if __name__ == "__main__":
     if fem.inclusion_flag:
         i = 0
         for Rinclx, Rincly, rot_incl, x0, y0 in zip(Rx, Ry, rot_, X0, Y0):
+            # x0 += (1 - 2 * np.random.rand()) * Rinclx / 3
+            # y0 += (1 - 2 * np.random.rand()) * Rincly / 3
             points = ellipse(Rinclx, Rincly, rot_incl, x0, y0)
             fem.inclusion_filename_ = "ellipse{0}.geo".format(i)
             fem.make_inclusion(points, startpoint=1000 * (i + 1))
@@ -104,6 +107,8 @@ if __name__ == "__main__":
             epsiyy = epsilonr_ferroelectric(E[1].real)
             epsizz = epsilonr_ferroelectric(E[2].real)
             epsi = epsixx, epsiyy, epsizz
+            # e = np.ones_like(epsixx) * fem.eps_incl
+            # epsi = e, e, e
 
             make_pos_tensor_eps(fem, epsi, interp=False)
             fem.compute_solution()
@@ -128,21 +133,23 @@ if __name__ == "__main__":
     eps_hom_xx = []
     eps_hom_xx_no_coupling = []
[…]

### 2019-09-27 ferromtm/models/theo.py

@@ -5,104 +5,120 @@ import numpy as np
 from ferromtm import rootdir
 from ferromtm.models.bst import *
 
+epsilon0 = 8.8541878128e-12
+
+# fname = "drilled vs undrilled"
+fname = "/home/ben/Documents/projects/animate/results/theo/drilled bst/drilled vs undrilled simalr feild pe"
+f_ = np.loadtxt(fname)
+
+ind0 = 180
+ind1 = 311
+ind2 = 465
+ind3 = 601
+#
+# ind0 = 0
+# ind1 = 601
+
+# f = np.vstack((f_[ind0:ind1, :], np.flipud(f_[ind2:ind3, :])))
+# f = np.vstack((f_[ind0:ind1],(f_[ind2:ind3])))
+
+# f = f_[ind0:ind1, :]
+# f = np.flipud(f_[ind2:ind3, :])
+f = f_
+
+Eh = f[:, 0]
+Ph = f[:, 1]
+E = f[:, 2]
+P = f[:, 3]
+
+# ind0 = 0
+# ind1 = 311
+# #
+# # ind0 = 0
+# # ind1 = 601
+#
+# Eh = f[ind0:ind1,0]
+# Ph = f[ind0:ind1,1]
+# E = f[ind0:ind1,2]
+# P = f[ind0:ind1,3]
+#
+i0 = 301
+eps = np.gradient(P) / np.gradient(E) * 1e-6 / epsilon0
+eps0 = eps[i0]
+eps = np.hstack((eps[ind0:ind1], np.flipud(eps[ind2:ind3])))
+E_ = np.hstack((E[ind0:ind1], np.flipud(E[ind2:ind3])))
+# eps0 = np.max(eps)
+# eps0 = eps[601-ind0]
+eps /= eps0
+epsh = np.gradient(Ph) / np.gradient(Eh) * 1e-6 / epsilon0
+epsh0 = epsh[i0]
+epsh = np.hstack((epsh[ind0:ind1], np.flipud(epsh[ind2:ind3])))
+Eh_ = np.hstack((Eh[ind0:ind1], np.flipud(Eh[ind2:ind3])))
+epsh /= epsh0
+
+
+E_Theo = E_
+E_Theo_h = Eh_
+eps_Theo = eps
+eps_Theo_h = epsh
+eps_Theo_0 = eps0
+eps_Theo_h_0 = epsh0
+
+
+def fit(filename, fitname, par0=(1, 1)):
[…]

### 2019-09-27 ferromtm/tools/parallelize.py

@@ -1,6 +1,6 @@
 from multiprocessing import Pool
 from functools import partial
-from gridmap import grid_map
+
 import subprocess
 
 
@@ -31,11 +31,12 @@ def parallel(function, partype="gridmap"):
     FUNCTION.
 
     """
-    if partype == "gridmap":
-        if not is_sge():
-            partype = "serial"
+    # if partype == "gridmap":
+    #     if not is_sge():
+    #         partype = "serial"
 
     if partype == "gridmap":
+        from gridmap import grid_map
 
         def par(iterable_values):
             result = grid_map(
